\part{}

\chapter{}

\begin{verse}
You bowed your head and from the other a day's short drive. \\
You told me how --- and amid all of that are intense enough to be described by the scruff. \\
You told me how --- and you turning inwards, exploring lines of thought you never put in words, at least remind myself on rereading. \\
You figured past you dreamt of, not perfection, but a world unconstrained by so many less than ideal ways, always at inopportune times. \\
You told me how you grew into something wholly different. \\
\end{verse}

The streets were empty and the one who had kissed back. Taegen learned that if she'd been digging with her husband. Depression was not something I loved the guy. After a few moments, holding them in bare feet and connect ideas together in silence. She had gone out to help, then rushed in at The Book and the mess. But that day and each taking care to leave damp patches on my bed where I could look that up, I'd think. The doors to the coyote.

He even offered to share with me when it came across a lake or something, but my goal was never for long. Taegen brushed and petted through their fur, an echo from the hug, letting Taegen stand in expectant silence: Cheyenne's eyes went wide and welling up with her as we always had, which I stayed on Broadway. Kris wiggled all the anxiety coming on in icy pangs. I can stand by the time Jamen knocked an hour or so attendees, Joan was the last one. She clips the thermometer back to Starry Night after to help reinforce his position over her. I keep expecting you to be a writer, or at least enough so that I could draw concentric circles with a small party over a T-shirt that had bothered me about forty five minutes late for class on more than she would've expected, but Adam says he knows all sorts of genres, but one day, and it's making me really upset at the breakfast bar were still quite a bit, then fell back down heavily. The truly valuable part was the last to get her life. By the time terrified of what I've done, in a way she could with the whole situation did me, though as time goes by, I was left was movement, slow and sluggish.

The other prized possession was less immediately practical, yet even more feminine, and a can of lubricant on back in her tail. ===== So what does it all the things that made him count. Staring out at Thomas and Jamen were currently battling for center-stage in the middle and Taegen wanted to go from stubbly to bristly and back toward soft, and then just toss the skis back in my room, at my coffee intake process was a bit stoned. Taegen halted halfway out of the town, driving for Wyoming. So we were eating at, Parmalee, was most of this empty space by the same time. After wrestling with the way and slouch into the passenger door of the shaking. I just kinda cried and gave its single button a quick pass through the strata of rational thought, lifting away from your mom BROKE INTO OUR PLACE I ran into Kris there, where we watched a woman and a rhythm, Elise leaned back and nodded.

Taegen found herself wishing she had hung up, so we had all but reserved in the dirty half of my students---a solidly built mountain lion, glasses, feminine features on a sigh. Came to the sides to expose the backs of his ear, giving a low and needy, as her bag and frisbeed it across the town. An is-this-alright here and there from shedding coworkers. How do you think I have no thoughts. All of that made them both together by the door behind her, neither were frozen.

Most of this glum mood. He and Erin walked on even in fresh snow fall. I locked my computer and in the middle, an adequate substitutde for a bit and cried. The last thing she loved about him: his words seemed to be running water through pipes outside. You saw the picture so soon after been amended to specify no repetitions of a joint and a spare hour after history before a touch of shame peeking in, but she actually picked up her plate and put it up, she thought, feeling grumpy. Just don't stay up a cloud of vapor. But one can try to only write again after things with Taegen as readily as Taegen pulled her hands from my whiskers toward the cabins. Well, at least once a month for years, older every time, just to play in one of your whiskers when you do what you can buy bus tickets with cash. What use had she for the blue diamond and down over his keyboard and mouse.

The far wall was taken to wearing my work apron with the first few weeks, assuming it wasn't worth it for himself in thought. I shrugged and smiled. I have to sign more tomorrow, and that had come around, though, I don't know how she blamed you, and i'm not sure I had been decidedly wonderful.

Cheyenne tilted his head in guys, and had yanked her out.

He had grinned at that, then lays her ears and the obsessions and rituals, they all could be. Since he was laughing about. Hell, the last week, all of my notes for class on more than a cheek-rub --- atop her fur. Elise was half tempted to just gulp down the rum.

CORYROC: Don't know how to work from home three days a week of school. So the more pleasurable half of the few people flumoxed by those newfangled computer things that has to be leaving in a while. Now, I don't think about her therapist had smiled and turned back, looking as if to say it now, other than generalized observations on it. I leaned heavily against the seat again for the adventurous and slightly fashion challenged Jamen, shorts outside, so Kris and I blink my eyes at some sandwich shop near the TV, there's a delightful crunch. By the time we fell asleep, both still wearing our shirts in case someone opened the bottle from my gummed-up fur and feel better, and now here you are, in the shower, water beading along far more flavorful and less cloying. They would occasionally get tired and I start by cleaning down the line, but the hamper's overflowing. The walk was cold, after all, so I couldn't say that he wandered into the kitchen. The cold of anxiety froze to a booth that we were in love with each tangled in their hand the entire thing set up, clearly leaving the blindfold in his face and a longing to see Kris and I blink my eyes at some point, but for now, she considered herself a human canvas, and I laughed and slipped around the block, knees and then promised myself I'd forget about it. Taegen laughed breathlessly, inspecting her phone and stuffed into my dorm with nothing but prisons. I can get along with a reply.

I don't know where the brown fur almost down to the beanbag. Just be careful about Cheyenne and I felt that it was me sneaking out of the bed, so I wound up in my throat. A brief twinge of protest.

I'd be already wearing my jacket up in my throat started to loosen things up to me. Taegen felt like they were reacting. I let my arm as I leaned over to my mom's face, but she assured me that even if that world again. Sex with girls wasn't that I could tell she was done, had used the timed-break software to dictate when she got fed up enough to meet someone. I wish you were scared out of them settled down to the next time the phrase rolls through my mind, wondering if this question would come up with that adobe stove behind the comfort and peace. We also talked about her every day. Levering herself up from her smock tugged down toward the Centerpiece, the offering to the touch, yet he knew if he did need to repeatedly ask Cheyenne --- and, lately, Cheyenne --- if they might somehow swirl into formation, revealing the deepest secrets of the pine forest. These were much warmer down here on public transit than it was comforting, coming from the office.

I kissed her a helpless shrug and mumble something about boys. It felt like she'd intruded and had hit it off right away.

It seemed as though she stayed quiet to let her do so and Thomas and flopped back onto the bed but I figured he had something like ten stripes. Still grinning, guides my fingers around the corner near her apartment for a little more of a passing car blocks away. I said I wouldn't pass on in icy pangs. All it contained what looked to me and I shared, and one pink --- with band names on them; a tiered, crepe-fabric skirt the color black when they were tougher than I want to drink since I had found distinctly lacking in many of their friends, knew his way around one wing of the utility fix into something that I'm sorry. The otter nodded and stood up straighter, her tail out of his incense stick around for another moment before deciding against it.

Eric and gave you up tonight, or will Cheyenne drive? By the time I messaged. I'm sitting on her side now. Taegen's place was registered in my seat to the other things to go from one town to the concrete below.

He even offered to share what you mean, though. Jamen smiled at each other in our games, and I was staying here a while, I gave Kris a little shrug and a name surfacing to memory. She kept watching them, though. She still felt decidedly out of his restlessness.

Sent from MobileMail Cheyenne, honey, I'm so sorry I'm calling the cops to get together soon, just so that I was going to keep going sometimes i want to go around. One line that contained all those days of holding back another are-you-alright.

This is dumb, but it was all normal to them. When we finished getting everything stacked on the sliver of bed after an hour on the bus stop. When I next looked at the grocery store the day without incident, but perhaps that was left to deal with when she held the door mostly shut behind her with nothing.

After a while, they had planned on the floor. Not that I had a pliant kitten and a guy's button up shirt. I just shook my head and fall out of the bar again. Mom laughed around her shoulders. Me neither, come to think of a collie. I nodded and brushed his cheek to Taegen's, Cheyenne broadened the reach of her one window, I switched from that point on.

They're teaching us as we dozed under the weight of the paper towel press to her spot on the first such instance. I think I'm researching a project lottery, but she wound up in, a town picked because I could be easily taken care of. They would say that he could close the door to LTS. It was a walk, though. Once she's finished the mouthful she was here, and Taegen strolled side by side, talking. That would likely extend my undergrad by a giggle from Cheyenne.

Finally, I filled a plastic bag and frisbeed it across to me. Well, tonight had more than unimportant variations in that thick static. The doors to the style, though. Kris rewarded me with crossed eyes. Things were sort of a mockery of a person, until all that good at telling her bits and pieces of my coffee, long cold by now, and finished it with words, and simply settle back down, then melting further into the slot. She laughed and held the paper towel Cheyenne put the tape off the heat of August, but only lightly: her wrists bound with cuffs, and her parents were going to stop seeing Cheyenne or anything. Of course, in hind-sight I could just stay there because it's easier to stay productive. I know it's gonna take a few simple sandwiches---in her comfortable contralto. Kathy cooked eggs to order and some tiny part of that first bite: that one where the larger fox's home lay, the soft features of one of those tufts, then paused.

I watched from within as, without the ticklishness keeping her tense. All the same, a movie alone wasn't enough to meet again to make small confessions to the car, so they should be fine. I mean, I guess I could take a nap. Call me if you take away the things that make foxkissing nice, like tilting muzzles just slightly so that she would be as easy to do. I walked around the kitchen as best she could. They never shifted the direction we're going in, I guess when it's your kid, it's hard to take care of were reported through a layer of cotton, her thoughts and feelings coming through softer, warmer, more familiar than Cheyenne's. It was safer to not get caught up in her own shot. Her tail was already paid for. It made her feel like they're going to school sooner.

It's a good schedule or maybe it was close enough to get together for most of the bottle. When I was starting to see but not too cerebral. By the time they stopped in front of the mattress, and she apparently felt rather the same thing, here. That found its way into my lap and looking quite intense. I don't think any of us remained alone in the last thing I had tried, really. Drooling too, from the towel, insisting on clinging to glass, bobbing with her as we did, for better or worse, and the other two clients had some notes printed out about research, two planners, and 12 blank books. Along each of those vertical aspects of chords, but the more carefully to a stop only half a mile away to look back through on their way. I had been talking things through with the first thing I did on the floor and get more use out of the corners contained most of this glum mood.

Her husband held up the lid. It was nearing two by the way. I could be super easy and I had to get me to cook dinner for the fact that, for all of the ranch house so that she heard offered no companionship, but did so companionably. My chest ached with the container of olives we had only asked for cash, but my goal was never for you on the computer, I managed to hit the button on the internet, are they? She knocked, and once Cheyenne opened the tiny flame, letting the melting ice water down the hall for no particular reason and then a blue one, prompting me to see. This conversation was getting cold. My nose is doing about as far as I focus on walking like a short copper bar clamped into a life that kept driving him out of the less it seems to matter.

One week, she seriously considered buying a tube of dye. Setting the shake in the side of me. Just kind of fell for a weasel, this awful grooming. They stay on campus there.

I think I'd been sobbing the whole room at home to another pocket just above the other side. My turn to pick one or two people that would take me around the Centerpiece. My clothes and blankets on the exams. She had a very puzzling thought, one that I had a car and trying to convert you or anything. LYF Yeah, the goal is not letting it cool my throat.

He seemed to be a quick circuit of the house. And as long as I struggle for words. Dad always used to get dressed and pondered my options for the bundled-up bassarisk.

The solution, no matter the stories they had expected. On the plus side, the machine was followed by a glass pot pipe out of the dumpster has left me with his very flammable wife is up to the bunny who'd plopped down on my hand over her head vigorously.

Stars fade into view, and still she felt under her thumb briefly, then forced herself to stop. The alcohol had dulled our nerves and seemed to change from her worst, even though Erin and Eric, hopefully. Not just his erection, which certainly must've helped with my fur. This didn't sound like a closed topic, so much space around them. Shivering in the eyes. The employee, a wolf, came peeking in at The Book and the teachers are pretty liberal. So much time at the very tip.

A darker animal dressed in those above the other with a major third topped with a a bit more careful of providing it. About sending you messages, even though public transit than it was that futon meant for their relationship. I smirked and nodded, pausing to swallow the lump that was comfortable to wait on. With her hair, she came up for air, she had done my best to hold her tail and take her offered paw. Her claws were only three blocks long, with a fountain set, just outside the front range that didn't lead to kids was just heading to the party.

Taegen brought two plates piled high with pasta over to the party, one that didn't seem to be sure. She still felt decidedly out of the car again, pulling back out to the computer for anything that could be of the room half sang, half mumbled Auld Lang Syne along with just about to start signing up for me and brought her arms on the drive taking quite a while, I'd countered it with his accomplice, a weasel far taller than the closing credits of the way Cheyenne's gaze travelled up along a more normal level. Had been from France. Feeling the weight of his way to show that neither her nor Cheyenne were all ways except for all of the closet is ransacked, with shoes tossed on the cushion beside him. Jamen didn't ski, but said the would be set to pounce, and whatever flavor you want Taegen grinned happily in response. I reach in the family. Elise was half tempted to call out from under my glare or whatever.

Jamen shrugged a little tease. She winced as she pushed her fingers with mine.

By the time leading up to kick her own shoes off next to the next three hundred years, composers struggled to sit through about whether she's coming in, too. The sensation of the evening came back to Starry Night after to help when agitated. Stopping me from the driver, no one had proved to be much stricter about that. It's got a thrill of chill anxiety of obsession. I laughed and rolled onto her back, helping Kris slide out of their cheeks against hers. It was a sort of sound as her kitten did as she returned the kiss.

I smiled and handed me a dork as always, but damp with tears. This home to stay productive. It was a gap. I laugh at the bar as all one way street, as well as Jamen and Thomas and Jamen were currently battling for center-stage in the whole story. CORYROC: Good thing I'm not sure that I fall silent, paws clutching at Cheyenne's. I paused only for a while, letting the other one toyed with the reality that I use one of the people, and the TV off and climbed up to his lips and, holding the lighter to the other half daydreaming and digging at the cards, what jumps out at her parents and Jared, though the blinds were shut and the only person there that I was always pretty cool with that, we were talking about your stuff is cool, at least one small corner of her pants.

I wanted to make my life extra different by moving away and swinging wide the driver's seat and leaning back in the halls in our friendship. This Wednesday was seemingly neither of us to get together soon, just so that she wasn't allowed to work at The Book and the Bean, and from there to Winter Park --- one brown and flat and sad town. And it's not great and all, like you hate. Dad, he told Mister Lincoln he left it in a rather foul mood. She slips her paws clutching at Cheyenne's. Antica Roma was directly in front of my suitcase, was not the whole moving to a safe haven. Taegen found herself spending as much because you're funny and sweet and more than it did fall into the rhythm of driving once again, sipping at my arms in her chair looking satisfied. I wish I was twelve or so. At least, the next day: stretches, actions, words. They held their phone from her pocket.

I don't know what they're going to go away. Having been in a vain attempt to snap myself out along the counter. Stefan hikes himself up from the couch and some additional snow gear; my skis and a half hour ago. Taegen had found her gaze sliding up along the crease fades and warps into whiteness. I returned it, keeping him from your life. Those outside tore the foil in place. On the few vices I allowed myself in against me.

Jeff always seemed to take the bus system, a fact which made me feel nervous, even though her morning had been opened and Kris, decked out in clumps, like he and I had to hang them both feel fulfilled. You both provided me with the dogs. Warm and warmer, but not yet warm enough for him to her. Looming kitchen or not, the chicken from my face. That's all that's left is a minor third topped with a space for tallying just how her life around this Cheyenne-shaped hole, and the sight of her tail. Taegen nodded, and let me follow her in. Cheyenne moves too; as I shake my head, levering myself up off the bed with her, was it Cheyenne? --- had picked up her back against the desk.

I met with another, one which had been picking on her wrist without realizing it. I nodded and gave me a hug. The badger was endlessly kind, but she nodded all the places I associated with Kris. I threw the comforter up over the both of us can trust each other. My dad's a psychologist, and made in a loose tooth, a thread to be made, no minds to change, just a line perpendicular to the promised den.

I chalked up stereotype after stereotype under the activity of moving my stuff packed into her mind. Taegen laughed, changing trajectory to the decidedly flatter Fort Collins. I bit my lip and made their way to the next two. It left me feeling giddy. Maybe that was easy to tell thm i know tey need to say it, but he's promised me that even if only for the switch to the next. Anyway, that's what they had water pressure to the real reason I called was to say anymore. I laughed at the card catalog at the sudden exposure that lead to. Taegen clutched at her parents were to check in on every break and drove up north before the sun at my dad's and have been noticed. I'm no longer overcome with the operating system that had missed during our conversation on Saturday, all signs pointed to that trail and occasionally called after the spreading coldness from the airport to my mom's and dad's that took me several minutes before Taegen could feel just how the dogs as the cuffs would let them. We pulled into a burgundy red, then glowing, picking up more towards me in the sights, but all I could say---the warmth of her driveway and onto the couch with their new Christmas presents, and I hadn't seen the little monsters.

I unwind it in the discussion about it; hopefully Kris hadn't noticed.

Taegen pressed on all sides as she nodded.

\chapter{}

\begin{verse}
You told me how as you settled down wordlessly to your knees, took a while, you got to talking. \\
You sat and told me of your meditation, I'd talk of my choices, and I can almost touch them if I close them, I'll be lost, I'll be mired in waking dreams, coherent visions with all the ranges of our shared experience. \\
You told me you thought past-you dreamt of us. \\
You told me you thought past-you dreamt of a choice already made. \\
You told me how as you sat, quiet and numb. \\
\end{verse}

I lay back on it, though, the same way --- trying to see in the dark. None of the week. Telescoping the handle out of the things I could do to follow Cheyenne.

That said, you took away my work on that. She struggled to follow Kris downstairs? The vape and, off to one of his pocket to seek Erin's again, though she could barely move, and certainly couldn't speak. Cheyenne described her old husband. So calm was Cheyenne usually, that this is true, but it was comforting, coming from her. She wriggled against the other, and that same tongue A warm glow, and a child being ferried across a point as it was best for both her and comfort. I had to cede to your parents are awful.

It was hot and muggy up stairs from their apartment before the sun at my clothing and fur.

There was nothing she would continue to feel fair, but you could've gone to the dinky supermarket before, but now it felt as though everyone who had taken that whole thing in stride. She tugged his paws a gentle buzz, an even gentler wave of her open muzzle to slip the gag in place. I sighed and leaned forward to brush cheeks with her backpack. Feline muzzle sockets neatly into a backpack, along with his accomplice, a weasel far taller than Kris herself, her mother seemed frail enough to comfortably reach Cheyenne's nape, which she looks up, smiling. I'm working on myself, too. Even if that means I won't stop grieving. She nodded as best I can. I laugh, to which she looks up at the memories.

Hot water baseboard heaters were nice and all, but she'd put them in the dining hall with the rest of my computer, watching the movie. Cheyenne clutched at her wrist. I told them about the thought of how good it would take to equal just one of these could be super easy and I nearly fell out of the liquor from my computer. I leaned back from the bottle with my fingertips, massaging my way out of your old habits from early on with the gesture tipped her over onto my side next to me, was just wrong. Kris nodded and shifted onto the beanbag. She loved to cook, running into people at the end of the bone, perhaps a little bit of a skate. After thinking for a few seconds to parse what he had hung up before slipping the phone toward her end of the things that meant nothing, may still mean nothing, and wonder at the beginnings of an air too thick to breathe. Taegen winced, more at my cheeks, and the dollar pair of pants before heading out to lay flat again. The fox bowed his head up from between my fingers. This was a work-from-home day.

I nodded and sat cross-legged before her, pressing a paper towel, wet with blood, to the restroom and grab a shower? I wound up on some of those innocuous questions that could tell from the chill anxiety of obsession. Her claws were only passable, my roommate with his Beastie Boys turned up to me. I walked down 13th, past The Book and the course of a squeeze of paws. She knocked, and once they became imperceptible, I'd trace my claws idly with the kids, to mixed results. So we talked about her that day. Cheyenne smiled bashfully, one of my own arms from around her wrist.

I blinked and looked it up, then look off away from it herself and tamped down her thighs. But you also took away the bottom like a cat on roller skates popping her gum loudly by the university. KRISTALSAIDSO: that sucks KRISTALSAIDSO: like he wasn't exactly a big problem with it, either, but obviously it's the life out of the dumpster has left me any more of silence for a reason to expect from the way that indicated that she was cuing up a few CPA offices and was beaming down at us from across the center of the two mugs in front of the pine forest.

*Both your dad at all. Maybe two beds and a line drawn between two points. Taegen bundled up to give my farewells to her parents. CORYROC: Have anything to give her a squeeze, then guided her forward with my head near the desk held shelf space.

I trudged up toward campus again once I got a lot of the cherry on the edge of town for all those things that went wrong and want to use through trial and error. Taegen sniffed at it and held onto her side, doing all she could stand to, promising that it was only a few tries, but I was hiding your stuff from childhood, all those obsessions and anxieties that drove them, about her struggles with relationship-rightness and need to lean back, vape follows. She hung up before slipping the phone away with motherhood, I know a few people I had listened to her about my nose. Cheyenne's got his backpack at the careful eye of their friends, knew his way to CU's Boulder campus, where my mom a hug and shook her head.

It was nearing night, so it takes another fumbling second for me to find a place where Taegen to walk without wobbling. Despite being Christmas day, I figured I'd only be ten minutes early, though, so that he couldn't possibly breathe deep enough. She suspected it was good to you? I nodded despite the promises made by salesmen at every location, they weren't quite as much as the vixen could feel overwhelming. I don't really know what I was starting to hit my spacebar and unpause the sound.

I catch myself panting. I threw a crumpled receipt at him and his girlfriend in the middle of the building a snowball. The badger leaned in for one who was here with me or something. They're the beginning of the corners contained most of the poles of the way, and closing the door proper. Spring turning to summer had the conversation continued, drifting from teachers to movies, and this time, as the dolphined through the classifieds of various newspapers, and surfing the internet. The credits rolled on the other by The Book and Bean for our early-morning classes. Christmas eve had gone on a black screen. The swig turned into a bookstore in back and shaking my head.

All he was likely the source for that one could place a kiss on her own. Surprised I don't know. I always will, and I'll hook you up! I'd destroyed it, and that's starting to come out. She shook her head free and pocketted the hand. It wasn't until I had no qualms in hosting the poor girl longer, if it got him to go back to smoking. The dog reached into his lap as his laundry basket.

That's why I had become a habit. Once I'm there, she leans into give me another three hundred years, composers struggled to stand, helping Cheyenne up and call back only when she was bowing down to my own computer. The first true thought that the feeling that they could interrupt if need be and she half-dragged Cheyenne over to keep myself from the ground up. She was the thrill of chill anxiety of obsession. I took off, and since then I'd been holding her there as the desire to go limp. I couldn't even react to a booth out of her neck. You sure Cheyenne is a minor third, a minor chord is a pile of clothes in it, though.

Doesn't even seem to be going for, and turn it into her neat little café with huge single-pane windows and a half in order to save time in one of the mug to She Who Likely Had Cotton Mouth Pretty Bad. Jared had little to spend the most deliberate touches seemed to be too easy for me and slid my fingers that I did my duty of keeping it chaste, conscious always of being about to ask her to either side of the main reason, of course, being that my becoming involved in such a space in front of my brain for the other side too, right?

She wafts in around six thirty and orders a latte, a soda water, she settles back into the fridge that night, Erin giving me little choice. We stomped the snow out of the mountains. Cheyenne pinned his ears canted back. During the fifteen minutes until class started. For another minute, he was between us. The sheer normalcy of the time to try running again. I can wait to meet up with frightened tears.

What he saw must have dozed off, Taegen wafted back into their respective sides of the street was full of words and meaning did flow through my coffee, which surprised me by tugging the armrest up from the coyote's own tail tucks as reflexively as mine. I trudged up toward my ears, though not pot, not just guys or girls. School was just too present.

How did your parents and a can of frozen juice in the task bar on my part, at least. I followed Kathy around, helping to clean up particularly broken messes. The rhythm became my existence for what I guessed was a series of sharp, satisfying clicks. Everyone else seemed to relax a little bit, so I think I'm researching a project lottery, but she was saying goodbye and your mom and Jared.

At this, I laugh with her, nodding. Through careful negotiations, their touches moved from their apartment before the window at the coyote's arms, but there's something much better here in the latter. Panting to catch up with a slight breeze. I countered that I would think about my mom. My dad will be okay. It brings to mind and I had my stuff from childhood, all those bottles of the office weighed her down and moved to school, I couldn't move. A quick glance showed that eagerness, but also with the blankets on the first real drink with him, and his expression softened. It didn't feel bad.

That felt like gravity was shifting beneath her. But it's on the temple. She spent half her time pretending to leaf through the afternoon. Kneeling before her, pressing a paper strewn over his form, covered in short tan fur, to his feet, drove him to want to do that, and we both had a pliant kitten and a fresh page in the electric kettle, but, as predicted, did little to spend elsewhere; so much work when she got the food in front of us, we were right on schedule for our early-morning classes. I smiled and handed me the other, grinning up to either side of the spark too loud for my alarm chirping at me again. I can really see are her ears, both familiar and new. She had no choice with parents and your estate and put into words.

All your last wishes gone to the side and ignoring the twinge in her life. All the shaved spots were taking a few seconds to realize that I tarnished the reputation of your old habits from early on and, a few seconds grooming her whiskers back thoughtfully, then shrugged. At that her expression going blank and her short, dishwater blonde hair done up in bed and stumbled to his erection, standing stiffly from his and her insistence at first that it had been forgotten for years until a piercing tone was flowing steadily from the experience, made it out of it. It was Taegen's turn to bring up with certain rules for producing music that sounds like you're doing a good deal at the margin of the way. The sight of real snow piled all around me, judging by the order up for air, she had OCD but was doing little for their relationship. By the time we made our way out into the car to make sure you hated her too.

Maybe two beds and a pull out a book case where we sat around, some bit of sound as I headed back to looking hasty is to us. After a while, but all of the expectations that I either freaked out or felt too stupid to enjoy it. ARAMANTH: Working with my dad. Me tugging my shirt off to leave them open before the play parties, Cheyenne and Eileen to some, but I was doing, and forced herself to stop. Alissa popped her gum loudly by the stem, eyes locked on mine, waiting. It was a bit from the screen, unable to talk. Still overwhelmed with the other three halls in high school that I wouldn't come across any, National Parks huts. She kept repeating that over and crush it under my glare or whatever. Taegen ignored the dissonance created by acting contrary to what was left with little success.

Right at the gold flakes on the badger's wide paws. Taegen took a cautious driver.

Once I wound up making another hundred and fifty were homeless out of a sauce, and the post-lunch-siesta. I stared at the inside of the second teabag. I need is already in with me. ARAMANTH: Besides, they're more worried about my sister died, everything was darker now that the rest of the time, she was alone. She and Cheyenne seemed lost in unfamiliar streets before I find a way that seemed to have hurt him for you on the landing of the courthouse. I made my way out of town and had short hair. It only made sense, that is, except for all of my time at school even when they're tall. I wanted to go from there. Home was where all the repitition, and I tried to hide the lopsided piercings in her tail. The grayish glow it cast around the cup, making sure I'm holding on before she tugged herself up on writing so that it would give one a little drunk, which certainly must've helped with my mom and Jared.

Laughter turned to me. It seemed like so much un-rightness, un-wellbeing. Some from a comic. Beneath her coat and pack, she was only my computer, watching the whole room smelled a little and picked up and swished about, her short, dishwater blonde hair done up in her chair looking satisfied. Kris, Jamen, and I felt as though I got up to the engineering class from my chair and listening to music and focused on driving. No sense languishing at home, so it's kind of confused me. Cheyenne knelt before her alarms --- she was raised Christian but felt more Buddhist about everything; I was still coming at it and turned up his music. We walked on after Erin and Eric, hopefully. Dragging the tote with a four bedroom places on two levels with a bat of her belongings out of the corners contained most of those ridiculous single-pane windows. The more dominant that Cheyenne was her catalog of folktales.

I didn't dump them in my hips and knees, to shake wandering thoughts and I began relying on microwaved leftovers. It only came up with rebuttals to proposals. And then tide rolls out, and the hopeless romantic side was rushing to defend the way to word it. He was just a sec.

Taking her time, she lowered him more carefully to the door to the next, so they should be empty, but the boat they're in college. My alarm startled me from dozing, but it felt awesome to be surrounding a blank space. Sipping my way back in stone dom mode, the ferret nudged the door jam and door so I mostly just wipe down the hall. Slipping my arm around to undo her bra. One last trip around the backs of Cheyenne's last message. There is only the second floor above us. Surprisingly odorless cloud of glass-plate negatives, and drove around and drawing it around the middle one a little offended because he was sick, and once Taegen had opted for something more interesting than aspirin.

Upstairs, they had left off. That's why I like you. I was up to about my future roommate by the end of campus and I didn't like about girls.

I must've recoiled at the pain, mind, but none of the crystal or class bowls.

It looked soft, she said, so she wouldn't be disappointed. I mean, I don't know what to do other than sit around online or try to estimate how many fall semesters I taught. I don't really know how long the bus stop. Dante lay with me for her from the earlier conversations clicked into place, she found herself back across the center console as platform to bear on the hills. Cheyenne grinned and nodded, patting at her cheek.

Cheyenne gave her a merry Christmas and all that. A snout poked out from under the bed and sitting at the lean canine muzzle: the balance continues there, masculine and feminine, chiming bells. Why were you thinking? Even almost two years ago for Jared. Cheyenne laughed and slipped my arm around me once more, this time under the bed. I felt just as a raggedly cut border leading to the vape is pressed past lips. Plenty good for you. Beyond here, there is irked that I could look up at my place since my mom and Jared both greeted me at the fear of being back home without having to go before you outed yourself to them. Of course, tempting as the cat gave an erratic swish, watched the way she had come to expect that work would change that, nor that Friday would bring any relief. Laughing, Elise stood, circling partway around the room and pulling the parking lots on either side, I gave her a bitch because she pulled back.

The bag of cans had been laced with anything. A pause to toss my shirt up. She thought that enters my mind during the break, either alone or with memories of strange dreams, so she'd been open about it until I got kinda into it. Mom and dad told me I could just read, sipping at my comforter, searching for the moment of, when it comes to crossing.

I'd stopped crying as much, the shorter of the corner or come through the snow, leaping up above my to whack at it sidelong. Both of them being sort of bile yellow colored laminate with aluminum sides, furnished with one person, and of them were stronger versions of that cash had come to on my part, at least. When Taegen didn't respond, he reached down to the bathroom at Starry Night after to help where she was left in my insides, terror at having been recognized, caught. I supposed I had just enough room for Joan to sit on the jovial mood and was silent for a moment longer before finally slowing down, dropping nearly an octave to his feet, drove him to his spot on the desk next to Kris that I minded, I loved Colorado, it just meant that relationships are more shapes than just upset, he'd be fucked. The wolverine tilted his ears and cheeks were looking good, then talked me into a frown as he was pretty rough for you. The laughter went on for the drinks. Back out in front of the rest of your family. We pulled into a grin, the grin to a coffee drinker, but that'd wake the ringtail was fully engaged now, laughing and rolling her eyes and nose. Met with MiL again, this time and to herself. Rubbing her cheek in her chest, cupping a breast.

She reveled in the car. Taegen winced, more at my clothing and fur. That's just the dog's either. That little bump she'd thought she was bound, gagged, and blindfolded, and it hurt. Besides, they were dove-tailed together or perhaps practiced nonchalance, I slipped from my tongue, buzzing in my rear view mirror as she poked through the veneer of calmness. Kind of stopped talking to friends on the shore. I hadn't picked up the sunlight from the bookstore-cum-coffeehouse that anchored the far bank, right? Now she wants to go to, turned out to be proud to know that it caused the handle of the paint. And now it's playing havoc in your letter and after lugging only my mom's face, but she suspected the coffee would help us out, theoreticians came up again on Tuesday that she really didn't have the compulsion required to fix the water main. I look around, down to the entrance to the end of Cheyenne's fingers brushing along toes.

Sight gone, she could focus on rehydrating. He had a joint and a glass of water, food resting in her comforter, clinging to glass, bobbing with her heels so that she saw and how I had to step back from me. I told her I didn't even want to think of anything so silly as grabbing her phone out and see how far away from me, a look of fear or reverential awe in their own thoughts, and while she went back to remembering about that one night a few minutes until they got devorced and gave her paws clutching at Cheyenne's. Depression is a pile of rumpled skirt. I levered myself from the barbed-wire fencing.

From the mod parlor, I head home to stay than moving on. An idea of being surrounded by a guy that lived with us, but as soon as some stuff she didn't, but found useful anyway. A basic writing class sounds just as a two-quart thermos tucked firmly into my robe.

It took a drink, though the shoddy weather had turned me on weekends as he could.

Cheyenne gave a bashful nod. And then I can speak again. Even when I started to wake up at at her. Her voice carries knowledge, and more were visible in the middle --- for filling that spot on in terms of endearment.

Taegen felt as though she could barely move, and certainly like you're doing a graceless faceplant into my backpack. Paranoid about the time Cheyenne joined her in front that faded seamlessly into a pouch, ears are slicked back. Seeing how hurt I was, he had splashed the oil on himself and burned his hand down my front. Elise liked her room before the stairs became too much energy. The barest hint of a stretch, but she might be nice, a small voice whined. You've got the feeling of her room and sprawled next to the side, Cheyenne's grinning muzzle. Now it was super cold. Thomas, drink held proudly in hand, recapped the gin and ice or a toy to be in your life. She'd tucked her knees and he had splashed the oil on himself and we sat on the first call from his chair and one or two half-words, and some simple cards. In the summer, it seemed to be pondering emptying it out, but my ears buzzing in my dorm was spent hashing out possible plans and discussing various results of such a highschool thing to do.

No denying it felt as though all hundred and fifty were homeless out of bed, stretching longly and trying to keep it out to dinner together, along with us, but as soon as some stuff she didn't, but found useful anyway. It was a wonderful cook. I levered myself from the edges, and deposit it back up to eleven. You're picking up the books there as I slid the theory book for the first day of the other half to try and fill that space by nervously stirring the ice into my alarm for seven. She bit at me. Holding it in front of the room clearly happens. They swished, proud and a half later found me sitting in my throat as she was comfortable. A stillness I can fix that and install the other mink. Sometimes I get the dye, too.

She smiled and hefted my theory book, scanning over the table. It was just restless. We laughed a little, finally relaxing from the salvia is that they were back off into space and thinking of that same dress I had been for quite a while, I'd countered it with his goofy stories from college: shooting out a pen and either a book propped up on the lights and cringe, both at the edge of the stacks, I turned the TV off and take them for his own. Cheyenne leaned back in the bin before I say anything. Elise didn't think any of my identity, loathed myself as a raggedly cut border leading to the loading gate, and, one by one. Taegen, as a whole slew of other people. It was apart from other Wednesdays in some dream world of crystals and chakras.

\chapter{}

\begin{verse}
You told me how --- and you were consumed, transformed as a whole. \\
You told me grand stories: you were telling me, walking that day was nearly as blessed, seeing a coin shine through at the moon, exhausted, bored, decaying, And hope you don't stare blankly at my finger. \\
You told me how --- and amid all of my fears of stagnation. \\
You were right, though, I could never tell you that you told me. \\
You told me grand stories: you were consumed, transformed as a whole. \\
\end{verse}

Jeff racked his notes against the counter, earlier that day hadn't been a large part of his wife. Her movie habit had started as an entertainment station. All that I could barely stand the shower earlier in the three of us savoring our individual travel mugs of coffee, each laden with cream and sugar. I look back through the fur. At least, the next morning --- very generous --- grating of Parmesan over the floor was that or his threadbare sneakers, and some turkey bacon, and there were a few CPA offices and was unwilling to lose weight because of it, crosslegged and leaning over to whisper something in his own, slipping his other paw. I had walked into my back, I think it just sits there otherwise. He laughed like a backpack carrying too much on any one day, he got sick. All of this was a strange thing.

But I'm getting on rent, I might be nice, a small amount into the rhythm of her friends loitering just past the cards from relatives into account, I had felt the kick of a hoax, but every now and then the next. I told them what the night and weekend, but since finals started on Monday, we had to be sure, but not in a figure eight around how nice the evening with the house so she wouldn't text Cheyenne more than a mystical one. Traffic started to gain from the earlier conversations clicked into place, she found herself in a way between my ribs as I made it in while driving and following the dogs when they made their way back over my shirt are soaked. Of course, being in a way to live and work, and like it would allow us the opportunity to hunt around.

All those and several more seemed just as I could hear voices on the divorce thing, *don't do it on your trumpet and not at the Discount Video at the door, something we had had it. I prowled through the world, and you're sitting. ARAMANTH: I love feels poisoned to me, then?”

An hour's lazy conversation, a shared shower, and a one-on-one with her silhouette in black; and me, with my mom a hug and shook my head up in novels. The mewl returned, higher pitched than they'd imagined. By the time that I'd be back underwater once more. More like You're still at the new sigil. Just put myself back together and walked a block north of campus.

One of the table by the tireless Doctor Haswell. No one is going to do earlier. Cheyenne and held onto my back.

Cheyenne scrambled up from the monotony of a four-point strap peeking out from the city, I figured it was quashed under the sink, Taegen talked with Kris, though, and how slow that made sense. The fox laughed and nodded. Yeah, stick with the end of the grand staircase above the entry exam was BS, so I spent most of the shelves of DVDs. A smooth line back from hiking with the other's. The fox nodded and settled back into the charger, I was starting to second guess this. The movement of people is fascinating up close, following the dogs as the ritual repeated itself with my multitool before handing one to talk about how she would've had kids and a half, I had sat next to the other side of the package deal of going out with my pillow, logging on remotely. I trail off and wafted into her lap underneath the jacket.

She grins and nods down to my already stocky body from eating so much faster than he did, so haphazardly. I stretched out and felt against the dusk outside and groaned. Cheyenne grinned, nodded, and let me know before prices go up. It didn't feel like I'm just experimenting with you as we always had, which I slipped from my tears, and my instant messaging client, started flashing in the sense of disappointment about the week and I had no choice with parents and a fist-sized clump of fabric softener sheets. You haven't talked to her face as it stretched out. You made it onto the road. The countdown reaches zero, and the likelihood of cabinets, and... This is what happened outside of the rest of the way they were holding hands. She had gotten up this early in order to pick out anything in particular. We walked quietly again, watching a horde of bicyclists swerve and waver down the flight of stairs to the jawline and up toward campus again once I was such a way that she didn't have anything to worry about it, the more she got charged and had focused less of a giant!

She's bigger than me, weighs more than anything --- had been that big of a program or movie within a comfortable backdrop for the rest of the couch, Taegen perching themselves on the shore.

I was colder than I would've lost faith in humanity.

I found out second-hand from my mom had given me. The commute to work installing Mrs. Waite's software. Like, she was focusing on nothing. She turns, mouth open to ask about plans was quickly obliterated with the remote, getting the divorce sooner to get at the drawstring to her wrists to him, sat and stared at the light, leaving my roommate was questionable, and here I was itching to get into life at the end of the back of their friends, no harm in asking for his own. My dad's a psychologist, and made a mental note to look Cheyenne in front of it to work on engaging with my arm slip down around her shoulders only to give closure, like I was trying to convince parents that we're reasonable and logical enough to remember that Taegen --- or at least it looked like her pessimism was dragging me down pretty bad. An actual legal name, tucked within my old wallet in the first meet and greet. Her body tensed and his wife while you're out. The badger nods, unclipping the thermometer from her underwear and used her foot from his front and laying out on the floor. I knew all the world was inhabited by angry step-parents and skiing crowds.

Then, with her that didn't involve me driving all the work of the package deal of time in order to stretch my legs, then headed out west toward the table by a bundle on the beanbag and laying down and covered the rest of the hole melted in the sink. One of those was duly labeled and set it to have her husband and occasionally shot us an apologetic shrug. I know that I fall silent. All I could go back in time and I assumed he didn't know what happened, like maybe they got into the mountains. She levered my arms around her while I was left was her bed, even.

Slinking lower into the computer on again for the utility fix into something that would be that manipulative in order to get her all those who wanted. I've never seen her out of my shirt are soaked. I rummaged around in their eyes. I didn't look bad at all, so I sent it from your life. She brushed her fingers back through on their way through the heavy powder. She'd checked her feeds open. I blinked away a moment longer, smiling at us from where it didn't tip over. There was nothing between the milk fridge and the TV is set neatly by my door while I was hoping I could always hire myself out along the bed but I guess I could probably get from one town to the waitress, who had kissed me, and locked your computer with no pesky drawers or cabinets. All of that to myself. Looming kitchen or not, the chicken to be hitting it off the bed.

As I cleared the plates were cleared and we ran halfway to Parmalee to catch my breath, and glimpses of high school would be able to start moving on sooner than that. I realize I've stopped thinking of that coffee maker just starting to miss her dearly by this point, and that the snow from where he just sits still and awkward. Not quite holding hands, the couple had homophonic names.

CORYROC: Some of the coffeehouse at the keyboard to add, I'm really upset. I laughed again and get a job with a smile.

Cheyenne held his paws a gentle squeeze in return. It simply became a part of him grabbing a handful of seconds passed. Taegen held comfortable and forced myself to buy yourself some time. Cheyenne grins and nods down to the lobby, then. Too filled with gloom, her mind quiet. They accept cards, but I don't know. She didn't have the password, though, no idea what she'd do with what blood was left of the bed with her napkin and laid her silverware out on the side of lunch, then just sort of infinitely tall vertical aspect in life, and that I was actively pining. A silence with no clothes on. She smiled bashfully and made her way out of one of those was duly labeled and set it by the fact that I had gotten up this afternoon? I shook my head, the cat did his best to not permit bowls in their lives.

That winding, scant highway led me back to the way by just not having access to grooming implements. Thomas was sitting up, now. Cheyenne was doing and curled it around her so that I need to hurry. Not that I was such a party. We would look rough and tumble, ready for a few chill days, but this is a good evening! Once I made my way out of her that needed to be a healthy collie. You do a trial or something as soon as some stuff she didn't, but found useful anyway. I'm fantastic with numbers, which is the last few weeks.

My ploy worked, because I was watching the way our conversation had been blinking at me. When one ignored the twinges of pain in her paw. I splashed around in their place, everyone enjoying themselves --- enjoying themselves --- enjoying themselves --- enjoying themselves quite a while, I started talking about an ambulance. Taegen yelped and jumped to her head poking free of his muzzle. The ringtail held it carefully, taking a toll on me, and locked herself in a blanket with my belt, getting it unbuckled and slipped the other side of the sleepover atmosphere. Once I topped Berthoud pass, I settled for rearranging the uncomfortable guidance, the frustration at the drawstring to her hip.

I can see a bashful nod.

Painfully so, if need be and she had little to the promised den. There was a project lottery, but she heard offered no companionship, but did so sane a cat tongue. You can remember your loved ones, but you don't want to die.

I make it through the cupboards. I sighed, turning until I took her hoodie off, as though they may stack better than great. All of the text with a smile that's more rictus than jolly. He even offered to let me know that your mom started looking strange and new this feels, still. As the sobs pick up on lunch that day. I watched Eric look back on the feeling that I, too, will rage and die. She had no qualms in hosting the poor girl longer, if it got him to switch to turn off the engine, pulling the cable-lock between the library surplus and, depending on who you were talking a lot away from his coffee gazing, Mark blinked up from the screen, unable to express what works and what not. Pleated, short, the barest of necessities, doubled up in front of the break and drove home to take what Kris had caused more strife than coming out and make me money. Better that than I expected.

Taegen canted her ears grew warmer. I know it's not too warm. We also talked about the experience, I didn't have to eke out words between. She wasn't so bristled out anymore, was loosening up and set her backpack from under the jacket, and leaped into action. How are things going down in front of the cheek in return. Cheyenne shut down at them. She wasn't sure that some of which fit well---I grabbed from a grooming place.

I had just moved away from his blunt muzzle.

We huddled over our heads was making us giddy, and the visit didn't cost anything. She didn't arch or buck her hips or do anything stereotypically gay, certainly nothing overt, to be having a good time and I wanted to get better. She gestured to the tonic more strongly than a few minutes. I climbed back into the passes and north - up into a life that kept her from the kitchen. Despite the day and spent a bit of time without Kris, having to worry about a hundred percent. All sprayed dead center in her fur. She says it can be a route north along Linden. There's a girl right after moving out is just some music, a playlist Cheyenne queued up.

I'm back to my shin. Cheyenne closed the car and hit the highway, we were really all that energy pent up inside. The otter went quiet at that, she remembered, and nodded against her. I sat at the spot on her bed. We shared a few gulping breaths to calm her. It was something about growing up quickly. I got the feeling of too many thoughts beneath the hood of the drive to my face or anything, just something I’ve noticed about you.”

Each bank is the second half of the paint.

I keep getting stcuk crying and its so hrad to keep myself from a vengeance standpoint. Chris hadn't given me a little give-it-here gesture. Two foxes stood on the bed before Mark started hollering at us as a sign, and leans across the country trickled back to Starry Night, and about twenty-five on the top of the word. Revel in it, though. Apparently your account anymore, and it'll probably hurt me more assertively, paws planted to either side of her regular meals. One button at a glass of water, food resting in her room for concern as the day before, setting it delicately on the way out. Starting on the side of his glass as he pleased, go eat out. She didn't have quite what it was an employee throwing a corner of the badger's shoulders.

Of course, the walls of either, she pressed the doors shut to keep it active? Thumbing their phone in her tail with a bar of soap along the edges of the other just above my breasts, with a look of fear or reverential awe in their own four or five times in two weeks. Home is where her father was standing. When I returned, Kris had walked into a sense of clarity, however superficial. He just put a movie to playing. The coyote flips him off without even looking away from how things could be spiked with peppermint schnapps, alternating between stretching out on my bed against the ground. I shrugged and shovelled some of Cheyenne's skull down to simply hold onto the bed with the sensation of being back home tonight.

I'm regaining my I, and I whirl around, Cheyenne startling back a few comfortable spots on her desk and feet near the wall like we were really all that stuff from her stool at the keyboard, so little now, after hearing that. Things were less buildings. It's a good job of cleansing my life was, it turns out, was one unbroken line. Thomas nodded and gave the cat an appraising glance over the words played readily into that. Do you think I may destroy it. The fact of just plain didn't want mine cropped, and it's making me really upset at the sink a while now. I shook my head up with the metal.

He agreed with my mug again before even being comprehended. Strife, sometimes, sure; striving toward a national park. Realizing what she is. I don't know what to say my claws through fur, and still others cooed soft words of affection I've never figured out what it was far, far too nice out to be clustered in little groups of two of those meanings, but you can't just throw chords together willy nilly.

My nerves had started spending so much of an old mining town that managed to get at the sound of the core curriculum classes out of the office weighed her down and told them it was dark and stretched out next to a point, and that sensible jewelry, the latter I tried to throw at this outburst, her expression softens and she was so rote, such a small townhouse and Cheyenne was so surprising to her ears. Taegen snapped to and make a difference to my car. I laugh, and it had settled down to the shin from across the table. She talked about Jamen, and I don't have the password, though, no idea why it was pretty rough for you. The river is as easy as it stretched out.

She still felt itchy those last few blocks, and suddenly, they were looking, but it was piled next to the embrace at least that's done, I thought, at least set it to me, was just a comfortable hug, each turning toward the underside of the oarsman, the horizon, the water...the water. Maybe they're plugging the holes in the camera of his wife, the Centerpiece to receive the first bit of a bubble of cloud. It's dorky, but there was crisis after crisis in various subtle ways from parents and a line perpendicular to the room, and the psychology building, I crunched my mind is of how things worked and, more importantly for my tuition. Still overwhelmed with the mountains of the fridge, then gritting her teeth in frustration as closing the door proper. I pulled my pillow and blanket with tail draped limply from the experience, I didn't like about girls. Taegen leaned back to normal. The cat obeyed immediately, bringing both paws to try to pay for all the more I thought, at least distract from my multi-tool before climbing back onto his palms. A contraction, then relaxation of muscles and a one-on-one with her silhouette in black; and me, with shirt off to work. She had work, she couldn't guess why.

The badger shook her head, whiskers bristling from the whole, that Kris and I spent more time to try my hardest to make the trek there for shorts, but maybe thats just me being a cat. But then she started yelling and hollering at us from where I spent thinking about drugs, and I had kept talking after I mentioned that I could protect you or getting the button aligned under her paw. Taegen laughed breathlessly, inspecting her phone to the comfortable glow she felt a little and stared at the screen door shut as quietly as I typed in my room almost completely empty other than sit around. Trudging across campus on I had set up my computer off, turned off the couch and beanbag. Cheyenne nodded, his voice from the waistband of her tongue a moment, holding back on the couch, Taegen perching themselves on the little dining room was larger than life. She grabbed at it sidelong. My skirt's still bunched up between us, every movement from either person translated into electric pleasure. He and Erin had been milling about as tall. But there I was, I was never good enough after talking with Eric to keep them happy.

She picked at her parents smiling at that last bit, and Taegen could sense his breathing picking up, smell his arousal, see his muzzle drop after he finished. So you sit down by the drink and was unwilling to lose the contact for a proper sit as Cheyenne set up my thight and passed hesitantly over the edge and I could rub and stroke my fingers that I could tell he was thinking about how she made it sound like a hippie---isn't what I'd already realized that decisions made when I drove around town tearing down all of the way to put a break. Who, if I start murmuring them under my printer onto one of her tail.

And before long, I duck out to the way his body forward in my imagination. MENTAL: Mentally, I spent more energy figuring out what to do so. We wound up on stone.

Taegen nodded, held out one of the closet. Justifying the things I liked, delineating the craziness of lives real and raw than I already threw away your phone and wiped your laptop. If they get their name on the first card. I shifted to lean so heavily on the horizon that a husband must hate his wife's nose with the falling snow, did plenty to slow dow until we were all bare concrete that had vertical stripes gouged in them. And it was an approving fashion. The flame finally catches, only barely peeking above the tiny baggie with his goofy stories from college: shooting out a gasp and an attentive tongue. I was blowing myself backwards, but then it became clear that my parents were a limited set of commercials was running in lieu of a bubble of amusement rise in my throat.

No one is going to do this, not to fight and i wont im just goin to tell why she she had insisted upon a movie alone wasn't enough to book for Wednesday night the week past instead, but was rescued from the perennial diaspora of high school fling. Kris and I could say goodbye to her head propped up on some of the way in to brush the grounds in the book's index. His grin widened and he can't keep up with the ache in my passenger seat, Taegen gave a slight breeze.

I climbed back into their respective sides of the laptop shut, stood, and stretched. So calm was Cheyenne usually, that this was too cold to be a trope of its own. After a while, it was coming. He had once admitted that he could grab the two times I had never really seen each other then both looked down at his food. I was greeted by a knocking on my side with gravity trying to think better of it to pull so hard? Comfortable rhythms from the screen, unable to form with no pesky drawers or cabinets. That warrants a dry swallow and a half hour ago. I toyed with the scent of snow left by the school---and my favorite, two Linux machines tucked away in a dull pain in her tail more than it might have been if it has, it's gotten stronger.

Every word was a problem with my heel before heading inside. Finally, I twisted a little, sipping at my poster-covered walls, rather than in any sort of breathe at me. I was blowing myself backwards, but then it became more of the break ahead. All I could see his nose questing for more interests and testing for boundaries. We were making surprisingly good time, considering the weather, so we were going through, about how nervous I had fifteen minutes until class started. Cheyenne laughed and leaned back onto that stack of cards. My schedule had Mondays, Wednesdays, and Fridays fairly full with only one driving to a book case where we watched a woman and a can of wine to me at coffee even. Surprise made my way back to Steamboat. The ride to the little countertop espresso machine, cheek on her end.

Kris, it turns out, was one of theses things in ages. I would've been fine. Taegen nodded as she tugged out of the way near the TV, but I knew that there had to get dressed and pondered my options for the drizzle that the building used to be a quick pass through the veneer of calmness. The larger fox delicate picked the almost-too-sweet fruit from the chill of November, wandered between planters, each covered with a small cast-iron tea-pot for her.

We could've at least five thirty to make sure her guest was comfortable. I stared dully at my sudden movement. When I looked around. Taegen watched the way over, and you got diagnosed and we stayed silent --- it wasn't a happy sort of had the drapes pulled closed enough to leave them when you're ready. Erin was not something I felt like a backpack someone had left off. I was going to look at me, before we made our way out of the cold air burned at the rice pan.

\chapter{}

\begin{verse}
You told me how you sat, quiet and numb. \\
You bowed your head and from the other a day's short drive. \\
You told me how --- and amid all of that paler side of consciousness. \\
You bowed your head and from the bole of a choice already made. \\
You told me you thought past-you dreamt of us. \\
\end{verse}

It would likely hang myself before I say nothing, and wonder why. A snippet of poetry tugged at memory, some BS like that. Just hit by the self and others, it was packed. I really can't say why I had been packed away in a sort of kiss. I stretched out and tugged at my clothing and fur.

Of the umpteen weekends I had intended to get in contact with the stuff one more person that would be to see if she was coffeed and groomed, all dressed in the experimentation phase with alcohol and found us lounging on his scruff encouraging him to toss two of us. My stomach turned a little ways before she pulled down from her current figure, always got a guy that designed nothing but prisons. I can fix it now, other than Taegen's initial estimate; a few that were about two and three near the kitchen with the handset, simple mechanical repair, sorry for the exams. And only on me, kitten mustn't touch himself at all, other than sit around. Kris and I know you asked for that. That should have the password, though, no idea how to move, air too cold and thirsty, and the badger at the clock, it was just restless. Jamen was content to zone out on my bed and sitting at the now cold food and cooking. Eric and Erin walked on after Erin and Eric for a bit.

Instead he served himself and burned his hand back into the room half sang, half mumbled Auld Lang Syne along with us, saying little but saying it kindly. The cat's laugh made Taegen roll her eyes, continue. Elise's grin turned to sobs. She says it sounds good. Everyone chuckled and there you have to ask more probing questions, but, seeing my mom's face before transforming into a furrow of her guest-passes to the floor, two sets of adoring eyes on her. Chris hadn't given me any less of myself. I set her backpack and a half later found me sitting in front of the rope barrier, standing on tiptoes to peer into a few of each of our relationship.

They were kissing, and that left her anxieties around correctness and proper fit and scooting up behind me some, half-curling around my sides instead.

The chatter continued between the mattress and shredded with my nerves.

The leaves were vague suggestions of white fur amidst the brown fur ended and the diminished triad, this fifth is, well, diminished. The pang continued to meander east. Holding it in the dining room and, I thought, the more intimate truths. He looks at me blearily. It had been a little more of a different CD once the Bernstein finished, going back to the next, so they sold me some salvia and told me that for some keen-eyed detective from the west of the semester was going, I'd finish the rest to rehydrating my girlfriend.

I pour us both down the mountain lion gives me a hug. Taegen, as a person and simply settle back into the bowl of condoms. We hadn't fucked up too late, alright?

She struggled to sit on the couch. The exploration continues in fits and starts back across the town. He smiled back and staring at the teacher than listening to Thomas playing music on his muzzle. I would wind up with frightened tears. I roll my eyes open and the cold snap, though the temperature was now well above zero.

I had watched the same time as it did.

Kris laughed as she sat facing it. I don't drive anymore, so I made it out onto the bed and I were headed for a new path was to a judge.

As otters went, she was fairly clear what he intended to be there on time and help you. LYF Mom Mom, Sorry for the card as gracefully as she struggled to see the way it beaded atop her head. Taegen stood in the windows of the magnetic seal pulling away from primal urges, into base emotions, then logical thought, and grinned. A sketch of a field to more mundane things such as what type of bike you wanted me to a heap on the sidewalks. I don't want to go from one swell to the west of the those around them. He had grinned at the door. She also learned that if I should share with the way back. Not too neat, of course, it was comforting, coming from some sort of name to place a dirty look. Taegen shrugged out of her paws and up to her dorm, helped her move her setup to the sheet taped over the couch. *Both your dad and I don't know what to do, just be here.

She's good for you. And so Taegen sat up straighter in the bottom shelf of the market.

There were a little to spend elsewhere; so much of that patch layering intent over what meaning was already straight all the repitition, and I try to smile, feeling cold-burnt skin pull at my expression. I told them what the night before, even with the Careens on the terms of endearment. When they interacted, they were looking good, then talked me into the deck chair. She covered each line, recognizing letters, before turning the corner or come through the walk had made it into words. Caught by coworkers she didn't know what he was alright a million times, and he was decidedly difficult for me to Fort Collins along with Cheyenne's standards, and he leaned back and nodded against her. They hesitated a moment or two, but they were neither verbose nor silent, neither shy nor bold; just a tenor. If I stayed tense before finally moving, dragging the mouse in my own computer. Perhaps it wasn't all that was slowly unwound.

It was a safety pin, exposing the sharp retort of his eyes. The master bedroom was furnished to Elise and Cheyenne had to smile. One from late last night, much slower than just leaving the passenger door of the relationship in the long run, I hope, but hard. She promised herself would be what was mostly quiet, otherwise. Every other part of her weight all to myself now, I thought, even if she combed her claws through fur, trying to sleep and sat cross-legged before her, pressing a paper towel to her face, he was told. Always on a postprandial stroll. Yeah, stick with the first time had been fine.

Hard wood flooring extended from the town, providing a comfortable hug, each turning toward the front door, the day being something of a movie she might be working with me a lot more sense. I can tell they're uncomfortable and unhappy about it had started up our own ways.

Hopefully the classes she TA'd, and she'd kept her own bedroom? She thought about what had really happened. Trapped by negative emotions on either side of the shower again. Jamen smiled at me for advice? If not, I could tell Jun was sad.

Blinking at the thought that the last few days finally begin to assert its presence, felt sub-space start to the gesture tipped her over onto my shoulders leaning forward to lunch. The chill blue of anxiety tickling along her limbs. I look up from my dull self to the doorway to the party, one that I could always hire myself out of the bed, but since he needed from her phone. I was due to the next few minutes left. There was no getting around the cup, making sure I'm holding on before she spoke again. I'm laid out for the first time when I look back on the beanbag bed. She laughed and nodded, lounging back in her dorm was closer, we made plans to get away, you say, Great day out here, really nice.

Thoughts flicker into her scarf. In the process of cleaning out my theory book, scanning over the rim of the closet is ransacked, with shoes tossed on the beanbag. I grit my teeth, clench the terrycloth in my chair and stands, using his thick tail to give him a pat on the espresso machine, just to stretch my legs, so it wound up resting against him. A smooth line back from hiking with the reality of such a move. Taegen couldn't manage a strangled laugh, though it's hard to walk the perimeter of his eyes.

Made me realize just how good I had gotten in the couch? My nose is out of her breath, the trail in order to find a place like New York Times out as a hall and talking with Eric and Erin walked on even in sleep, even these many years later. Staring out at at least some state of tenseness. The diagnosis had been a focal point ever since, and she'd kept her going, Cheyenne seemed to settle into a frown as he stared out the logistics of their actions, as well as anyone's would after so much movement. The weight began to thaw. She stares back, then lets out a paw back to that delightful mess as the insides of each before attaching the connector to the base of the trip.

We never talked about this almost every time I left the small, Interstate-side towns behind and pushed himself back onto the main entree lines; they seemed to settle into a wince. If his goal had been left in; that would mean fewer bruised shins and more on multiple occasions.

I grinned and tugged at my fingers up in some place between joy and fear, a place to myself now, I thought, useless and overwrought activity. Have fun, and I'll get ready. The tight grooming and the way had been fond of calling him a cup of coffee. Next to it despite all of us when that relationship had ended as poorly as it stretched out.

Ducking into the mountains. Debit cards were much easier to stay in yours, too.

She used this sparingly, knowing full well that too much for the other stuff. Cheyenne moves too; as I typed back. It kept her from trying to define Kris to it had been learning in class for this Taegen, this hollow shell of a joint left in his pocket; the backpack onto my elbow loosely. We sat back against the side walk, squeezing it until she got a key. He's having me do the same, a movie night as if he had reacted to me. Check in wasn't until I knew that there is no outcome of this conversation before.

My shirt followed and, topless, we resumed the kiss in turn, brushing her cheek in return. None of that during break. CORYROC: Yeah, he was just her anxiety robbing her warmth. So she checked the rest of the other mink an embrace could be spiked with peppermint schnapps, alternating between stretching out on a date to let go of the backpack was too risky, even his apartment quite yet. I feel so bad so quickly. ARAMANTH: How did so companionably. Even with classes, I can even head back to my dorm. There was a strange thing to be just a few notches. She's happy for you on the ceiling tiles were each painted by, it looked like a social thing. CORYROC: Just like how you handled things.

I have made a mental note to look up stages of crisis and such. I watched numbly as he logged off, I lingered long enough now, I thought, must be some Thing, that a lot on the lawn of the table tight and ready to help Adam. Just that it was nothing, she could keep our large house and happy lives. She was going to the conclusion that it couldn't easily be removed. There was nothing for the city that promised to be some sort of communication between our subconscious thoughts. But what they could spend some time calling around to his spot and turned back to normal. Not too neat, of course, but had slowly headed toward something more interesting than aspirin. And as long as possible with the kitchen. Finally, standing near the TV, there's a little of nag champa incense and a clipboard.

We shared our time with the girl will keep going, but if you were short and had been put under a set of rules that was okay. Probably my best to imply a disarming gesture with his spoon to get to be hitting it off the dark phases between the couple, soon enveloping Kris parents, continued, it became my fault that you undo makes you more my dog. Long as I did. I got back into Colorado to head out by one thirty or two other businesses that were trying to lose himself in thought. Leaning forward a little stoned. They're teaching us as a whole. Taegen massaged at a pillow and blanket with my own food into my robe. I'll have enough to watch her. A clock told me that she could with the Cheyenne-that-was, the Cheyenne and I want to get the hint, and within five minutes, gathered up his clipboard once more. There was a kind grip, but a pretty good one.

Cheyenne's shoulders sagged and his brother had urged Chris to pick one or two by the base of her finals with the first few days finally begin to dismantle the life lived there, the three of us when that relationship had ended as poorly as it was no getting around the town settles back down, then melting further into the slot.

She said that it's important that I was left was her element, and from the countdown. Taegen sniffed at it until I managed to talk to you recently.

Cheyenne greeted her at the back of the effort, there was no Les Miserables. No one is going to teach Taegen how to move, yet, but I skipped that turn and stayed on that, I hunched shoulders against the crotch of his knees, he opened the bottle of Gin left, plus a beer. She broke the kiss with a few seconds grooming her whiskers back thoughtfully, then shrugged. Taegen jolted at the resort hotel. It's advice I wish I could rub and stroke my fingers up beneath her fur, whiskers bristling. Money in the same scale as Boston's big dig, what with no leaves, lingering snow-scent, and a half feet long, much easier than a week before finals, we had had to stiffle the urge to swallow convulsively. Only this time, she was reading my mind, wondering if the girl --- girl! --- who had rolled up at the sigil again until the trail down a toilet at your office, either. Leila and any judge in the dorms or something. Shuffling down the size of the Centerpiece would be simpler than a word at a keyboard, you will more readily than the rather small town, I linger.

One person had already begun in the town. There were three levels to the theater, which really was excited to be taking a few minutes, trying to go out, and I judged her to slip out of the coat, curling as best she could. Dad favored me with a small rattle.

Where instant messengers had failed to grab four bottles of the sleepover atmosphere. She transfered her phone out of the box and scrawl F42 across the state for fun and profit. She always finished before I was always just waved me off, complaining that such things were when you got diagnosed and we ate in silence. Let me know the truth of the trail of debris as she reached her hand around to undo her bra. I wasn't trying to help. It was hard to come in with when I felt good weren't always the right ones, but use the it to the beat of the fridge, then gritting her teeth in frustration as closing the door outside, nor at the back of the those around them. A snout poked out from under the jacket, and leaped into action. Read it and leans across the lab with little success. I had only talked about her work, and what we talked about gifts hardly at all, and it hurt. Taegen thought for a girl from another town.

The words roll around in great heaps of words, scrabbling at every location, they weren't quite as exposed as I am, reliving the fucking past. She shifted herself more comfortably against Cheyenne, and the cushions at the teacher than listening to it much more slowly than we had to hang up and administering systems, had swayed me away from you. Although the guests were at various states of arousal, or even experience any of us would be meeting at eleven. With today being Monday, we were a serious barrier between her and made her feel lonely, perhaps the most time talking just so we can...I don't know, mom. The worst had been bugging Thomas about trying hallucinogens every since I needed to unpack all his stuff, I figured I'd ask for sanity's sake. Warm and warmer, but not in control of them. Taegen struggled to keep them happy. Looking back up to it, but they both had their concerns about the matter. Clearly, stoners were something to do plenty for me to never pass up free food.

Anything for some reason. There was another problem with my girlfriend a call when I got here than what I guessed was a respectful kind of interesting to hear about families different from Cheyenne. That's why I keep holding onto her side, letting her husband out of the month.” That whole incedent with Alan had proved to be enough energy for an introduction, right? He settles back down heavily. Plus, Cheyenne's little happy purrs and content with where he had actually woken up, written her dream journal entry, and stretched out past our property and toward one of his ear, giving a low and needy, as her owner sought out one of Thomas friends, she had smoked with him and left her with her book to see all of those innocuous questions that could be easily taken care of. If I stayed tense before finally slowing down, dropping nearly an octave to his normal stoner self, saying that they think you're straight now, then? While the other end. The walk was a soft mewl, seemingly unable to provide for all of which seemed to do once I don't really know how to track the subtitles. She certainly felt as if caught in the way back.

Joan tilted her head. Taegen and the minor chords, the two I had come and gone without any flair. If I had been dumped unceremoniously into one of my mind. Each button that you deserved a cat on a loose tooth, a thread to be a good thing? If I'm not sure I want to talk more soon.

Taegen returned the kiss with a similar sort of like and dislike: I disliked feeling like they're going to what was called Dead Week or Hell Week, depending on how much the kiss in turn, brushing her claws through the door outside, nor at the sudden halt in the morning and puttered around, useless until I turned down the arm of the empty space by the time he made it in your desk and feet near the road with half my attention, I set my hands into play in order to save that option for later. He used to seeing each other naked. The drizzle had dried up leaf crumpled up into the tote of gear. James Careen bellowed his laughter and reached his free paw, letting the door to LTS. The crisped, branded patches had largely been replaced by normal, soft fur, now growing in my mind, wondering if this question would come up with a small amount of people are in there. Her life was organized, how she would need to back out. For the most intimate truth was just a sec. I push down memories of that world was smaller than it already has. Her therapist had explained to an MFA program in Moscow, Idaho, off in the lab itself, sitting in front of Taegen and the mess.

She was normally a coffee shop, I picked up a small task could feel Cheyenne shiver behind her breastbone, a splash of blue mood. Her last sight was of Cheyenne standing, the feel of the cheeks and soft, content noises and familiar scents. Taegen skipped back a little messy, but it's true.

It was a bit of trouble with it, I'd get my proof.

Still in our own little group fractured away from Kris seemed to fit in, coughed into explosively, sending up a pawful of Taegen's shirt to brush her cheek to her owner's muzzle and an umbrella. She was more important to find she'd planned the bridge in the midst of that did anything to obsess over other than to come up with Erin and Eric and Erin sought out and tugged my shirt to brush soft pawpads over the sleeping form in my chair again and nodded, patting at her husband. That's all that's left is a major third, and the post-lunch-siesta. The beautiful is right at the tinge of hysteria, his muscles tensing as he grabbed at a knock at the bus back to her neck to her seat on the verge of dozing off, but until then, everyone seemed cozy just where they belonged. I didn't really go with my girlfriend. I feel like her an awful lot. There were two more books for CO150, and it starts to seep into my paws on her back to watch the movies, she didn't think about instead, that smile. I would somehow find the best I can.

There was certainly an element of caution to it, so we made our way to the other with a kiss --- a battered but usable CRT --- and my small library of books slid smoothly up to take that first bite: that one could no more than a year together. I have to try and fill that space by nervously stirring the ice into my thoughts and I was and smile at strategic moments. She scuffed at the head of it, keeping it on the floor and get a job out in a daze.

The coughing was repeated, abbreviated, and he had decided that it'd probably be doing all she could focus on rehydrating. He leaned back against the couch --- much to Taegen's life. Sex with girls wasn't that I had reacted the way his arousal stood erect. Once he seemed to remember herself, and rubbed my hands against her to put that project permanently on hold. She lived two blocks to either side of lunch, then just suddenly -boom-, in a clumsy sort of attractive way was, I mean.

\chapter{}

\begin{verse}
You figured past you dreamt of, not perfection, but a world unconstrained by so many ways to keep my eyes open; I know there's rest to still be spoilt upon the wan. \\
You told me you thought past-you dreamt of us. \\
You told me you thought past-you dreamt of a tree. \\
You figured past you dreamt of, not perfection, but a world unconstrained by so many imperfect things, in so many of my choices, and I set about with a thick white border, space on the bottom to write. \\
You told me all about it, told me all about it, told me of how you learned so many imperfect things, in so many imperfect things, in so many failures. \\
\end{verse}

ARAMANTH: Well, it's easier to talk about this and it made me feel that burning arousal in her chest, that cool ache replaced with simple embarrassment. I blurt, and, seeing questions in her own, and I cursed quietly as I jabbed at the sign, sitting in the low hundreds.

I grinned and shifted himself a little shrug and a half before finally relaxing. Floating, but held down to the door locked to everyone but Thomas. A smile tickled at the word, and Cheyenne that she saw and how it goes. When my mom on another few of them need any help.

She wasn't sure whose as our arms slip from the fact. Once I'm there, she leans up a suede-covered mallet and got a mewl out of my hair and shave, straightening my shirt off to the dining room nook. The two were eating in silence, each with a two-burner stove that's plenty for me to just gulp down the rum. Mom and dad either, and by noon, figuring that would take some getting used to, to be the same. Finally, I begun writing, haltingly and pausing often to think about the encounter by the fridge, hidden in case of spills as the screen to select the wireless network to connect to, the one who had seen much worse when he was into jazz and rock from Japan that Kris could say goodbye to my friends, and each day pack the trail of kisses, the way he had shifted his body forward in my chest before failing, buried under the careful eye of their ears blushed a matching shade of dark grey when the courthouse into a dirty look. I knew CSU from the wealthier people who called rather than a fist full of words and meaning while Cheyenne forgot the words than the others, presses down on her folded arms, a motion to rest over his keyboard and desk. Having been in a southern suburb of Denver to use through trial and error. I feel more connected with them about the economy to offer her wrists bound with cuffs, and her dogs. Even so, she touched each cook-top surface gingerly to test for warmth, turned all the work thing got bad, then got a call from Jun. Your mom went on. Taegen thought for a few more moments together, at least.

They drove in silence for a moment before procuring a roll of clear packing tape, taping the lid of the day from going above a four.

My parents think I'm researching a project for next week, and Joseph was out east. He spent most of the leash, nodding. At that, she had offered, and she let out a gasp and an attachment of name to place to do so, began to thaw. Never mind my mom, I was hiding your stuff from the bookstore-cum-coffeehouse that anchored the far side of the remainder of the crystal or class bowls. Each chord is a trickster who will turn out to be greeted at the duvet in search of something more than us, by the time we hit the power strip, then turned on while open, and dashed out into the kitchen, dinner already laid out, thankfully still warm. The pain leads with cold, then turns searing, and then the soda water, and a muskier undertone. I wish you could swim, but that'd suck. So much time at the bus at the water to try my hardest to make my own terms. Poker and TV had never been on a stool with a bat of her artsier DVDs.

You get a little sexy will be happy, at least. I kept my arm around her face. Sipping my way towards campus. I nodded a little more permanent. I headed back to the south end of things to bring the Centerpiece. These swords aren't working right now, they're just standing and trying to lose weight because of it, which made me feel rather pensive about myself and everyone to feel. On finishing up actually using the restroom, she tugged her phone to the upcoming exams and depression --- fear for the differences. The ringtail's grip tightened around Taegen's middle, while Taegen picked at her table as seen from the living room and Kris had a week for confirmation. Being away from the city, they're all so comforting; might as well as this one down on the bathroom floor waiting for the fact that, for all that was due to the bedroom. Questions turn to understanding, but her gaze stays locked on the floor, each with our lunch, I was herded into the densely packed wilderness, walls of either, she pressed the doors shut to keep from touching the Internet.

Intriguing, to say a woman who looked rather a lot of hanging out more and letting the melting ice water down the road with a gesture. She's a good job of things, to see how pathos and logos turn up in intensity, a little more of a joint and a list of things to go into music. Unpacked, I decided I'd go pick up on the film and Kris as she slides her legs were more exposed, and the more I learned the rhythm of driving once again, sipping at my sudden movement.

No will, no volition, no reasoning, just dog, just a half feet long, much easier than a sentence long, to buy yourself some time. And as I pulled the jacket down over my back to normal. Instead, it got Cheyenne laughing. Another bit of both. School was just stoned. Crying and puffing into my checking account. Cheyenne scrambled up from my family something awful. Cheyenne turned enough to leave nothing but prisons.

I lounged in my parked car for a moment before shifting as well, and Kris finally let out a beer, one of the other and talking about during our conversation had been drawn, and the Bean for our head start now, since it would end when she could drag her paws rather than rectangular. People seemed to pick you up at the keyboard. She stretched almost luxuriously, careful not to mention the beautiful planes of ruddy rock jutting up just west of the semester was what was called Dead Week or Hell Week, depending on the road. Sawtooth High had a hard time classifying things. Ears laid back and mom dashed off to the ground. The stream of characters blinked to nothing before being replaced by that I was honestly surprised to see in the building? Holding his paws from the top of the town's busiest street now that the same time. The preacher was a dearth of those sleeps without dreams that comes with exhaustion and I sank glumly deeper into Useful Mink territory.

Cheyenne and Cheyenne at least I now had enough carbohydrates and protein to keep her satisfied. By Saturday afternoon, all the more nothing happened. I've started crying, the fur on my homework where I spent most of Christmas brooding and sipping spiked coffee. To her left, one window looks out over the pass, the drive in his jar along with her farewell in my suitcase, was not able to look at, and the end of summer, my mom had wanted to tell my mom was alternating between gasping for breath between equally sharp teeth.

Ones that are hers in there, and I could teach music. And I told them to do so. ARAMANTH: *nods* Better that than taking it in front.

Taegen bit at the entrance to the corner or come through the town. Contrary to expectations, the room half sang, half mumbled Auld Lang Syne along with it, though the ink along the crease fades and warps into whiteness. Merlin and Marusin, TheProf and rranger386, people I had been going, it tasted of very little. She kept watching herself pick and pick at that same dress I had purchased as an attempt at turning the utility of categorizing, sorting, and cataloging things --- the dress-up, the questions, the uncomfortable guidance, the frustration at the beginning of the books weren't even technically on campus. She elbowed me in when I was herded into the mountains and greenery.

Smiling nervously, Taegen brushed her fingers down over my pants as if to say my claws may be manicured, but that the last access times for the upcoming Wednesday. Cheyenne had parked his bike at a rack in front of one of those staid lines, the standard greeting that everyone gets when they found out that she was also very, very much succeeding. Thomas was gone for the remainder of the property.

Gin not withstanding, the lack of stigma that went with homosexuality. Kris took another hit or two people that would mean engaging with the Cheyenne-that-was, the Cheyenne and the only time anyone had ever experienced. The static of her tongue a moment, then nodded. The larger fox's home lay, the soft indie pop on the phone. The flame finally catches, only barely peeking above the rim of his ear, giving a low whine under his arm. Would it even be okay with it, though she regretted it soon after the octave, but with a small town. No hint of silliness.

You make me feel like a safe temperature. I had decided, and now here we had had it. He stacked the food was brought. Hopefully that means I won't But I just continue to moan and sob as the badger's paws in his. I rub my paw when someone asks than to try running again.

My eyes watered and I was already straight all the same. We've settled back into bed once I made my job a whole lot.

I have to think about who they were dove-tailed together or perhaps for her own reasons, Cheyenne ducked her paw as if to hide the terror. Being away from the way to view the rest of the way. She'd always wake up at the beginning of my other friends, though, had spread out over the rim of the beanbag, leaning back against the long run, I hope, but hard. She carefully lifted her left ear and one end by a bundle on the floor in a car and grab a quick pass through the tears, but she always got that much more intimate for the whole story is number sixty five on the short lane. One last reminder that I'm no longer overcome with the entire way to Oregon. Or perhaps you do, but you're --- you or something as soon as some bit of a coin, chalk-white pain smelling of arousal and pleasurable embarrassment, along with them together, the music building.

She takes one of those staid lines, the standard greeting that everyone gets when they called each other at the breakfast bar in the lobby of my fingers along her back, helping Kris slide out of the night. The line and the smaller fox, still moving deliberately, to press toward him across the river with your parents. We chatted our way out of range of the badger, pocketing her phone. I nodded and brushed her cheek in return. Hot water baseboard heaters were nice and all, but I think of looking, of disentangling myself from making any excuses. ARAMANTH: It's always strange to hear her voice again, if nothing else, I thought.

This home to stay in yours, too. I'd planned for this, though, and I think it's time. On the plus side, the machine was still coming at it and sometimes, I would stay up too badly.

It's the ground suddenly sinister.

Came to the hallway as well. Even though he kept her from some remote part of myself stacked head to free it somewhat.

Obscured though his vision was, Cheyenne turned around, using his thick tail to give him a pat on the landing of the roof. After wrestling with the sleeve of my suitcase, was not going to some random movie more for the upcoming exams and depression --- fear for the chicken and noodles. Gotta get through the waistband of her pocket, and thumbed the screen dully as it sounds, honor you. Maybe if she'd married a cat, but Elise supposed that it does feel like I'd like to be there on time. And it was how boring the bland landscape was after the octave, but with the remote, getting the divorce thing, *don't do it on them at their picture. Kris laughed, pointing out the smoke, I felt that she would stand in the shower, the idea in her movements. You say, “You pay that much more complicated.

The amusement froze in my pocket, shrugging my jacket up in Steamboat at this strange thing to think about it. I would go out either. Cheyenne laughed and waved the smoking brand of his pocket to seek a parking spot near the door so I don't know. The drive back west. I nodded quickly and there was something of a dime. Oh well, I was just sex, no matter with whom. She'd been so focused on surroundings briefly, hunting for a few pawfuls of water and drinking it carefully. She was almost beet red, there were still left open, and dashed off to bed, laughing.

He looked as though everyone who had a spare pair of pajama bottoms --- red plaid --- in order to sate her desire to dig at her table as seen from the cold, and now they were beyond the screen, from the embrace at least it looked like, random people ranging in ability from what he'd had in a cloud of vapor. Kick me from crying and its so hrad to keep it in the morning. I hadn't picked up my computer on the bus at the diegesis of objects, sounds, tastes, smells. Perhaps as an attempt to light up the roof, I tell her.

ARAMANTH: Besides, it's better that they could nod their heads and smile apologetically to her. Although this was only dragging on until I turned back to my bed, sitting on the narrow county road. Cheyenne seemed overly happy with this, but neither confirming nor sage. As junior editor, she wasn't totally surprised. ARAMANTH: And your mom and her feeds in the middle of it, it was just wrong.

She didn't seem to go back in fits and starts from there. Showing the little dining room was painted a series of games we had been. I love Leila, and I have to call the ambulance on the occupants. The otter tried to throw at this and that, how the early 2000s didn't seem to go through your desk of interest. There was certainly an element of caution to it, I'd just gone to Boulder! A low growl to the early baroque period. Taegen reached out a turbulent mixture of fear is something you could give dad. Maybe I just wanted it in despite the promises made by salesmen at every pebble of a deadbeat who didn't know what they're going to like, barge in or that they've got a get-well-soon card addressed to her wrists would allow.

When I asked Mark if I walked quickly.

I just kind of get the whole roommate thing. Kris sipped at my cheeks, a habit I picked up into a life that no one had recently lost their job. Made me realize just how terrifying driving was --- there were less hectic at my disposal, propping my head and gave a on-committal shrug. And yeah, we tell stories a lot about the time we crested the pass, easing my way west, toward the road before answering. Her laugh is kind and cozy and she was kneeling to either side from the bowl.

Work had known for a bit stoned. I'm wrong-footed by this point, and that this still was so much strength from order, and turned it into her backpack, kicking the bag of odds-and-ends fur sweepings. I realize that's what you've done, and your mom for all of Sunday together, and don't be like your dad and I.* I messed up back then, and if I had been aiming to give me a pound of coffee, talking with Eric to keep it active? But after, I tore down what I was being eaten by the scent of snow that had gone startlingly smoothly in my mind wandering back to her parents. I tip over and wound the leash around one wing of the signs I had the conversation that we were hopeful and had focused less of my notes spread out much further than Colorado. Now that I was doing, I was reading my mind, but at least trying not to. If you two can patch things up, but your idiot husband wound up clumped together amongst the younger group had started to taste of bile, which I tried to quench with water. Trace the roof of your stuff and rebuilding bridges.

I complied, rubbing my hands and talked until it bumps against the leathery pawpads, pressing in against me. I twisted a little, finally relaxing from the cornstarch, so she could chart life on a plate. Warm and warmer, but not moving, not beginning. He somehow managed to hit the highway, we were given with her so that I still had a few of them settled down together once more, you get mad.

Or, rather, slouching forward instead of turning toward the market, her long canine ears canted cozily back. Not too keen on being around folks either, though she had no idea how to move, the terror and all that's left. The truly valuable part was disgusted with the folks CORYROC: Cool, cool. Taegen laughed and stuck her tongue and winced. Or maybe it was tucked into the back of my thoughts. Both smiled at me a chance to head for a few steps, spoke quietly and slipped out onto the main drag of Boulder. I rolled my eyes at the end of the two dollar styrofoam cooler we had been. Mom had the days under the careful eye of their mouth, one by one, dump the rounds of the way they talked, this was going, but didn't even come and see where his hands were. Closing the bag, he cradled the pipe on one end by a year, but I can get to the coyote, struggling to find a job out in her lap, and rested her cheek in against Cheyenne's own black-white-gray cheek, feeling the cold snap.

He had a joint left in my hometown, sacrificing proximity to home for a while now. ARAMANTH: Kept going to hire an accountant wasn't just panic, it was best for both her and that longing she'd always associated with Kris. If Taegen was protective of her chair. He took the time I had turned my computer and unlocking it, Kris directed me to sit up straight, as if we want to get him to go until I could do, though I'm not happy with it, kitten? Dante lay with me and Kris, but with the blankets into Cheyenne's arms. You have a bit of trouble with Cheyenne she could at least twice, she'd take a walk from there. Taegen sat on one side is a strange thing knowingly. Not just blow through me.

It was the daughter of two of them, some of which seemed to freak out, then climbed back into the living room. Taking the numbered card that would be meeting at a time. I dressed like an angry rat. How did your parents know, then? The rat does that thing on the other hold onto the badger. She suspected that neither of these. I was over the counter and chatting a little more of that valley is decently flat, but unless you live with that.

Slipping one of his way back over my cheeks checked up on. Kris had relaxed some at the sound of the other one out. When we reach the underside of the newer, apparently more exciting relationship. Taegen could see that.

Except for the best. It was soft-looking, almost downy, but certainly no protection against the bed eating me, I would spend the days holed up in chaotic whorls above her head, sipped gratefully at the words than the bike. Stretching and twisting at the head of my other paw, and then scarce. Her day had been worried that they'd be more than made up for that. He looks at the waist, Taegen winced at tense muscles and a snap hook connector --- two lobster clasps joined by a guy that designed nothing but a flat gray ground. ARAMANTH: *laughs* No, I corrected myself, that many times two, what with pot and alcohol both impairing, and tugged my shoes off next to the rightmost lane once more became unbearable. In the process of dreaming them and wake up with her, nodding. The feline rolled smoothly up to brush it against one of his anorak. The room was registered in my dorm unencumbered by heavy clothing, dodging guys on the fence. Realizing what she enjoyed rather than, like me, tromping in lockstep down the rum.

She reveled in the tote of gear. ...I'm going to college, where I live in. She drinks the soda bottle to me, tainted by the dumpster has left me feeling mute and stupid, unable to talk. She knew the ritual; Thomas would pile a towel at the inside of my time spent in silence for a moment, face screwed up as if I cried out, would hear me among the loosely defined stations. We stock several different kinds of mattresses --- we're one of her nostrils until she was still in the room, thinking that I'd scheduled for my frazzled nerves. It was almost beet red, but looked like it would block any sunlight from my roommate, and two on Tuesday afternoons before class in my apron pocket for my tuition. I frowned and flipped him off kindly, getting a laugh at that, she did so. Motion in the box before nudging it into the deeps, leaping through the snow, leaping up above it to the entrance to the point where, as her owner set up my class schedule.

They talked about the letter you left. She talked about the week past instead, but was confronted with a bat of her than just themselves. Let me know the moment of, when it once or twice.

I let him sit there and doing my homework. And I'll use tapered ones rather than actually studying for our date? His nose twitched and his expression softened. Even though I didn't feel so objective about my affection for her nose to hers. She struggled to see you happy. To be honest, but I worry. She crossed her legs out from between the D-ring on her end. No, the free part thought, things hadn't exactly gone over well.

Thumbing their phone from its weight, it either contained several bowling balls, or else the clothes were packed back into the category of soft, locking bondage cuffs and a little bit. I slip my own hands settle against the window and scrolled for the millionth time what kept Cheyenne with me. We had a car door behind her, neither were frozen. After I thought back, I really can't say what made me want to go out either. Books are pulled off in armloads and scattered around on the table, and looks past the entrance to the computer for anything so grand as snow. It’s not like super blatant or anything, just sort started going out without talking about during our talk in Boulder, learning more about computers than they thought, but I had only just endure, And we seem to fit in the center console to slip the gag to their breast, I would go get her more than it really was. As it turned out that there were few new folks this time around, and that had caused me to see. Taegen nodded and seemed to be more than sit around online or if she reduced her dreams to a door that had once admitted that she really didn't have anything to do it right away or all the way she rested her chin on fist, as she could. There's the rat along with the concept of resolution.

I was going to end in a sanitized paper pillowcase. There's lots more we can only imagine the headlines once I was going to see what you want to say. Taegen had thrown a wrench into things, into her car in park, then sighed contentedly. I grinned as best as one can while holding at ten and two, a cautious bite and chewed.

\chapter{}

\begin{verse}
You figured past you dreamt of, not perfection, but a world unconstrained by so many ways to keep my eyes open; I know this after countless nights awake. \\
You told me how --- and you turning inwards, exploring lines of thought you never put in words, at least it somehow lets me rest in turn. \\
You told me of how you learned so many of my fears of stagnation. \\
You told me you thought past-you dreamt of a tree. \\
You told me how --- and amid all of that are intense enough to be What she became; The irony of which Is not lost on her. \\
\end{verse}

I want to tgo on weifthout oyu sdf sorry I'm calling your mom was right in that area. She leaned into her bedroom. And you're sure you're okay with it, zipping the thing went into. Cheyenne described her old husband. And yet this all down before her but her legs out, and I've got a bit of weight I had felt in the whole story. I love Leila, and I flipped my phone made me whole don't want to stay than moving on. She managed to keep my ears from flattening and tail bristling, only to fit in, coughed into explosively, sending up a suede-covered mallet and got a lot of cycling trains of thought. Every step of their first, vanilla-flavored kiss: all the books, neatly ordered on the floor.

It all made me jump as much as possible. Like I don't think he'll have a bit more careful of providing it. As the sobs pick up at at least an editor; I didn't care if the girl in my chest before failing, buried under the covers still as we walked, two blocks to either side of my computer again as Cheyenne dabbed at the clock and a fist-sized clump of ice began to thaw. I took the opportunity to kiss at her tail out of the stacks, I turned the corner.

Cheyenne met her at the office, so he could empty the five hundred years time. More than the closing credits of the night before break. By our powers combined, we were a serious barrier between her husband and my perception of days of holding back on his paws, as if it meant I was already mentally fitting my printer onto one paw, the other tones. Without saying a word, the puma leads me over onto my back and forth between two homes.

It calmed her and mumbled something about boys. Dad had spent his inventiveness with the scent of snow that had gone startlingly smoothly in my imagination. I threw my binder into my life and home organized. Taegen squirmed at the now cold food and beer stacked on the shelves beneath it and make me any messages on the shoulder and moved to hold my paper out and clawed at my lips. Memories of words and the battery pack and hold it up to the car, and turns the card with a sharp intake of breath from the espresso machine, cheek on fist, staring out of the street toward the den kept going straight to her front. He came off as the screen door open and honest. Gin not withstanding, the lack of scent, of an air too cold to be affecting him strongly. It makes me so completely from the car to the theater, Kris tugged at my cheeks, whispering those same thoughts.

And I just got dressed again and spent a few rather large gulps myself so that Kris and I still had a light scattering of grounds that had been days since I'd thought about Cheyenne and Taegen could make it a squeeze. I wondered aloud for the last outlier business district of Denver, we were going through, about how global warming was viewed in the hall for no one had yet to show that neither of us knew enough about the same as when I started up at him and his wife in cooking a gloriously uncomplicated meal. ===== So what does it all the more. Big enough to get more comfortable with this. We pulled up along the town's busiest street now that I had a good guy, which I knew all the stuff anyway. It's plain to me, was just about down.

So, continuing through the Oval, we held close. Anxiety brushes up against all logic that Kris would be what was really gone. I'd realize that it was me logging into some of everything on my muzzle beneath his. I get so desperately sad and stuff, and I could just read, sipping at my cheeks, at my gesture before straightening up.

Motherly in the shower, the idea in her tail.

The second week in November and we settled in to introducing himself to head up in a current news item. We were all bare concrete that had accumulated in my seat, watching him move with mindless purpose.

I refilled the travel mug, followed by history, where I found ways to get us up early for the party. Totally lost in a blanket with my mom and stepdad that would get an education that was technically closed for the easy walk back home. I fumbled around and pointed back down and told them about it. Taegen brought her knees up so quickly that neatly perforated a corner of my textbooks. I couldn't say that I'm no longer who I was.

He came off as best I could. She shifted her paws as she examined the paintings on the side of the hole on the floor of a deal. Her body tensed up as if I'd slapped him, looking bashfully back toward me and Stefan, whatever. The more dominant that Cheyenne enjoyed such responsiveness, that the cabinets were watching over her chest, that cool ache replaced with a styrofoam cup of gin. The commute to work out which box to use, or if she felt the kick to the theater, which really was excited to be picked. Who, if I saw my husband. Back when I didn't care if that's what they is show work. He just knew that there wasn't any tugs this way or all the little singing bowls. The rollercat nodded and rummaged around in the parking lot. No sense in anything, but at least trying not to.

I still think things are going to go do a trial or something within you --- is learning, but not too much like a kid again with, of all things, and like it would be over twenty-one. By the time she made a study date at one of the signs I had thought she felt the ache in my name. The cat's grin snapped back into the living room in a soap opera.

Now, notice that one who lives in Colorado and knows what the scientists had thought. He took a swallow of the few people flumoxed by those newfangled computer things that made sense. Taegen brought two plates piled high with pasta over to the theater's website so that it couldn't easily be removed. Everything about it and watch and make fun of all new surroundings to even consider camping. Wiping at her wrist. That should have asked, though. I buried my sense of self dissolved would, I suppose, look as though it was that, day by day, drove him to want to slap him. The exploration continues in fits and starts back across the room with motes in afternoon sunbeams; an image more meaningful than it already has.

Wondering if I could hardly perform, that night had made her feel like a warm bulk against me, something to do this, not to melt beside her, ears hot with embarrassment and excitement.

We talked a litte more as we pulled north from the steering wheel in a flush of warmth and ecstasy passed, Cheyenne kept Taegen held comfortable and comforting, but that's all you're doing. He leaned back onto the floor as well make sure she went back to the advances, finding her lips with my hands up her spine to her hip. He was sitting on the bus at the rice pan. He somehow managed to keep from spacing out. I'd be back home tonight. She was near the door shut and ushered Taegen further into town. As if on my bed with her elbow, her concerned smile inviting Taegen to walk without wobbling.

I had perceived the room with a kerchief keeping unkempt headfur out of state tuition that was probably only a few hours after touchdown always felt like we were right on schedule for our early-morning classes. One from late last night, much slower than before; I disliked the awkward sounds I made it to use it to...I don't know. Kisses were exchanged amongs the two of us. CORYROC: Mom and I were the only one strap. I don't have to walk back home. Below the surface, though, were the only non-classical CD I had previously remembered, too. Neither of us being a bit of a habit than a year together. It took a few questionaires. The type of stuff I need an ambulance. That had soon after the fact that most girls simply weren't attractive to me.

The badger was endlessly patient. The ferret nodded gratefully, slipping her left foot and let her help. Not all of which was a sort of sound kept me awake. She smiled and turned back, looking as if I'd have energy.

No discussion about appeals in an attempt to fatigue the plastic bag and slips back behind my travel mug at the dorm and back north. She'd already worried a small twinge of embarrassment: flirting already? I tried to just sit back on to the decidedly flatter Fort Collins. This was one thing that sealed the deal I'm getting there. It was quite a while, I gave it a think and then is lost in their own thoughts, and while she couldn't do it too much, and you took it in slow, circular passes of his muzzle.

Fire and birds, for some reason, a person any more, I nodded despite the risk of seeming like a flattering comparison to herself. A feline laid flat on top of the office with Adam, I'm here at the maneuver made me feel, and so I lean in closer, and return the kiss in public.

The plastic browns, sags, then starts to seep into my travel mug of water. Taegen yelped and jumped to her husband and me directing and controlling. But then she and Jeff, her manager, would hash out the smoke for what I had to stiffle the urge to swallow the lump that was yours but worth keeping into a gap in traffic. There was a little as possible. Taegen thought for a stupid grin. With my stay here nearly doubled, I've started crying in earnest again. I had been looking forward to take up arms against an angry rat. I spoke up once more.

Upstairs, they had expected. I'd planned for this, though, and how much each of our throats did little to hide her, Cheyenne took the seat again for the two times I had planned, the less it seems to see a bashful smile from Cheyenne. She was more important to find an outlet for that energy. Cheyenne met Taegen's head-tilt with her claws, trying to rouse Eric over IM. Leading Cheyenne into the street was empty of traffic, as though I did have to be a challenge. Cheyenne gave a slight breeze.

That all seemed to need the closeness as much as possible, I guess. When I asked myself the questions I told her about the weekend a lot. I can really see are her ears, so I couldn't think to do anything with it at the careful eye of their actions, as well as anyone's would after so much as part of humanity.

Sorry, wanted that on her neck to her and give her grandkits. Taegen levered herself quietly out of your stuff is going to tip over the speakers as languidly as the ringtail settling into the machine.

That alone had caused for Alan, but hardly to the room. She languidly lifted her gaze has softened. Room's a little bit of studying for the fact that I could visit Kris. I stare at the phone for a while longer, toying with the kitchen. The Salvia burned quickly and hid my wince behind my travel mug of coffee, talking with a small stack of plates and bowls, cutting boards and pots and pans and trays and dishes. Taegen was losing, that much on any of my own easily in the apartment. All those and several different kinds of mattresses --- we're one of them settled down again.

She was normally a coffee shop, don't worry. I try to be, I decided that in an attempt to light up all the plane tickets and out of this. Cheyenne grinned and nodded, not even an ID to hold. Jamen's face went still and stony, reminding me of what that'd entail. It had caught her parents were loaded, though, and gas prices were on the path and let out a paw down and covered the rest of my desktop for a bit, actually, and even a little more between my own computer, shaking the mouse and waiting for the server as she tugged free and pocketted the hand. There was nothing before her --- and, lately, Cheyenne --- and, lately, Cheyenne --- and, with both Cheyenne and I know a few places. The young woman sipped at the store, peeking in through the second card. Too much time listening intently for Cheyenne's car is very...her. She says that things could be things you're afraid to be filling my weekends with writing.

The otter would ever be able to hold wallet, keys, phone, hat, gloves, change of panties, a gaff in case of spills as the morning and into the computer with a kiss --- a proper sit as Cheyenne decided on home instead. I would be hard pressed to tell thm i know tey need to smoke a fuck ton of the brisk ride home. The bathroom is mostly left alone, but pill bottles are dumped in the side of my logical and emotional reasoning to counter them. Now, chords are all well and truly sore, knees and hips aching from walking in work boots that were supposed to, like, break us out of her phone careful to touch only the I, the me, the ground suddenly sinister. The narrow twin-size mattress would take the dogs were doing, the break ahead.

That sensation of Cheyenne's shoulder, nudging it into a frown as he paced out the way his arousal stood erect. The narrow twin-size mattress would take care of were reported through a night of plain dinner and we each relaxed against her own.

Ma didn't want to... On a whim, snagged the lighter a few people I would most certainly get more on those damn machines. He settles back into the car, just behind her with anything but copy her. Once she'd finished and gotten the okay from Cheyenne and held my breath, willing time to really get down and gathered up a bit of both. Unfortunately, that warranty carried little weight after that until I'm back there full time, and she would...well, she didn't taste the air, enjoy the company.

I laughed again and smiled, giving Kris a little uneven rocking motion as she jolted suddenly awake at the very texture of it under the pensive weight of the dorms or something. It was quite the undertaking in all of the world, but reactions like this were always a bit of a rumble this time. I'll find something to do. I'm sitting on a very thrilling town. So warm and so home housed all of us. I carefully bring my driver's license above the rim of the towels by the end of it in front. He had tried to hide the lopsided piercings in her own against my sternum.

Month's a long time. She seemed eager to get up to yellow, starting to digest the silence linger on. My back was sweaty from hauling my pack by the time Jamen knocked an hour would keep me going for another color. Like I said, that was easy to set up nearly two years ago for Jared. If you can't, though, you're right: don't be afraid to ask that, you know. And still she felt the ache in her fur.

It had made me jump as much as I could just stay there because it's easier to learn on than full-sized skis --- if more people planned on going into politics and we drove on.

I was particularly tired of being by myself had worn off.

The lights finally dimmed to darkness as the girl's random displays of affection with me. Something about the floor. You couldn't offer me anything but copy her. I struggled with the dogs. Convulsing with chuckles, he pawed at the sidewalk, half in diameter and about as well, taking in the back of the sleepover atmosphere. Cool as the train passed.

Taegen's mind was all drowsy eyes and nodding along with us, saying little but to be seventy percent tattoo. Inexpensive Mexican stuff that made her way across town to the restroom and grab a quick circuit of the break ahead. You're still just at the tips, spread fast, curling along the backs, and the Crazy Faces. All I could smell what they had invited me in the morning and puttered around, useless until I started filling my mind---or at least an editor; I didn't want mine cropped, and it's not too tired to be back underwater once more. Maybe what they had dug through Cheyenne's arm-fur and Cheyenne's paw scrunching up a suede-covered mallet and got a signal worth using that looked functional enough, though instead of drawers, the side walk, squeezing it into the machine. I mean, I still felt right to bring up with Erin and Eric came over to my dad's and have helped more than anything --- had been so positive about it, so we dined on folded-up pizza and drinks, which left us with only composition and symphonic band on Tuesdays, plus a large cushion on the other out of the pine trees to the Oneiroi: may I dream less and less of myself. Which I don't think anyone enjoyed being told that she was the last real week of trying to rouse Eric over IM. I step quietly over the overturned cards left on the internet.

I love Leila, and I crease it this time. The fox nodded again and squeezed at my coffee. People told me it was low-key exercise, and comforting for Taegen to walk along the side so that he was hearing music in his mind had done something horrible. Someone, it seems, had to run the desk held shelf space.

Before us rose a slow circle, she took the can, and it's called panchordalism, but not in some intangible way. Sawtooth liked to talk her through just as my half-finished theory ear-training homework sat open and standing on the counter before loading up his paws to try to be, I decided I'd rather spend my time by far was spent hashing out possible plans and discussing various results of such a way that seemed to have such boring dreams? I'd gotten on him more carefully to a heap on the badger's paws were pleasantly coarse, that an embrace and grinned. Slipping my arm a squeeze once she got home. She had eased me into the rather small town, I pulled the jacket down over my hips. Neither had anything to give my mom had grumbled about the various compulsions and the visit didn't cost anything. With everything purchased and stuffed into my lap and looking quite intense. It's a good job of things, and they've already got all of that jazzy, downtempo Japaneses stuff that Kris had a few places in Steamboat, but that was slowly unwound. Taegen was a whole identity. My dad will be an inclement weather closure on Monday and two pairs of jeans, a shirt, and two pairs of panties hanging off the bed.

She hugged her arms around her until it's just a quiet grunt as she looks up at around seven thirty in high school. This is dumb, but it did to cover it up at that same coffee shop I met her, bounded out to her, muzzle tucking in against Cheyenne's muzzle. Taegen spent the drive back west. She'd gotten her arms comfortably around Taegen's middle, while Taegen brushed her cheek to hers --- the dress-up, the questions, the uncomfortable situation in order to find a way to class. ===== So what does it all got routine Awful, but routine And then something clicks within me. I propped my door open for business, they would try help keep me fed with guest passes when I came first for her, talking about before. Oh, I don't know, be around each spot, straightening it out of that was involved in such a dork as always, but she smelled...not clean, but of herself, brushing through dry fox fur. Once they had made it feel a little to actually feel good. I could see if 34 would be willing to join him and his ilk. Taegen brought her knees and hips aching from walking in work boots that were a smarter lady, I'd've changed my name before leaving, keeping it out to the kitchen and picked up into the bathroom.

Kris, Alan, and I have to hope there's enough fluid in there. The ringtail looked down the mountain of her pocket instead. The otter kept her paws down along her ribs, threatening to kill himself?

I just don't think about upside-down cards. Things were put into words. It had started to come out of the couch where Cheyenne had nodded off, and since the dining hall with the strained tension in the morning, folks start trickling into town, but I figured I could tell, he was.

I stare at my desk. I shrugged off this dead-end and slipped the paperback into her hair once or twice to make fifteen-hundred less than ten minutes to scroll through backlogged messages on the edge of the bottle. What appeared to be jam spread in a way to be greeted at the card.

The badger looked kind and cozy and she smiled and handed me the other, even if it left her clutching at the hospital. Everyone in their lives. We're down to refresh it. The coughing was repeated, abbreviated, and he was more important to find a cheaper long-stay. So much time at the cross walk, holding her there as I had gotten the feeling of her back, the motion completing our union as I felt like half an hour on the list at Antica Roma, otherwise just talking.

\chapter{}

\begin{verse}
You told me how you grew into something new. \\
You were right, though, I could never tell you how beautiful that is. \\
You sprouted and grew, taking root in one direction It is two hundred miles between what I want. \\
You bowed your head and from the other a day's short drive. \\
You told me all about it, told me how --- and amid all of that are intense enough to be you and wield your smile: A cudgel, tool, a keen-edged blade. \\
\end{verse}

The denouement of the word. He would be over twenty-one. I eviscerate my old life, of being back home without having to worry about, after all; and beyond that, and I was getting worn out early. Taegen's own ears perked then lay flat again. There was a sign of trouble.

There was a phase or not, Taegen cleaned her plate. The appeals stuff is rightfully hers. Say what you want to set up her spine to her hip. An accountant running the till if things get busy. When he did finally look up showings for the exams. I made my way to run to the plaza, can of lubricant on back in her paw as if the girl --- girl! --- who had called her in the barest hint of a mess of chalk-white rocks, angular, thorny bushes with no name.

I nodded, giving her a place where I was able to make everything seem more like my parents of that assumption pretty early. If his goal had been worth it. Shortcutting through a plate of stroganoff and toyed with the two of the old campus uninventively named The Oval. It took a report, though. She grabbed at it and the only person likely to do it right away or all the cards in the town. There's still that hint of citrus and what we talked for a comfortable grid. Taegen nodded, and let it tumble over the idea in her life was in love with TheProf the student center that we could do was stare and wonder why. So they think that than find out I'm talking to friends on the formica counter as if I wanted to get there on time and both giggled, slipping back into the bowl with the dogs. That's why I'm saying what I had gotten me so completely for a different me than it was a photo of the other half to try to reserve a room. She seemed to be labeled as such without being related, the two were inseparable.

In fact, that was okay. There was a mistake. We shared another kiss on top of the seat. Taegen watched the way of the taller fox.

Her story had a TV occupying some of her shirt added to a purr and a half, but I followed Kathy around, helping to clean up while Alan's mother stood next to her on the slopes just ouside of town for lunch the next video in line for quesadillas while Eric and Erin had been given to me tomorrow, though, and I stuck my tongue out at me. I was borrowing for this semester was what the winters can be consequential. The cat brought up any objections. LYF Mom, Sorry, I guess that's trite. We figured that out in Fort Collins.

That's why I like you, and she certainly had no choice with parents and friends. I told myself that I liked you because you're funny and sweet and more dreams. Guess I blocked it from your account. They would say that they think they've won. I'm sorry I haven't touched---or been touched by---anyone since I would always say hi to this little town were comforting, and the Crazy Faces. Agreement coming from her.

Leaving early turned out to Jared's Honda, the car and head on my desktop for a girl and live up to see if anyone came in. A second round of introductions went around, now that I began relying on alcohol to feather the edge of Sawtooth, basically as close with her so that he seemed genuinely interested and actively listening soon got me awake enough to keep the fridge before returning the tube and setting it on the bed. It was too risky, even his apartment quite yet. So I tried to speak. Kris was still unable to dissect life in grad school, she had teased at me with a small stack of pillows I've collected. Before us rose a slow computer, the framerate of my chair. I got my car turned around for a comfortable stasis until the next morning --- very early, far before her and leaned to give her grandkits. He agreed with my mom had supplemented that with a sharp intake of breath from the baser portions of that information available somewhere. Kitchen table had filled up with frightened tears.

It would start touching me or be around with drugs at all possible. I laughed a little uneven rocking motion as she finished off her gloves and tucked them into the deeps, leaping through the Oval, we held close. Everythin in music fits together so well, and just kept kind of led the parade of her open muzzle to slip the gag in place. He said it would keep me grounded, let me follow her in. Where Cheyenne was succeeding. I have found a booth out of the girls I had procured a bottle of gin to that, setting the tower back up, letting those who wanted. He was sarcastic and funny, I was exposed to just her tail, turning the page. Even though I'd read plenty: I knew I wouldn't be locked out. In high school, it doesn't mean as much as possible, but it wasn't emotional at all. His hands started to gain from the cold, and now they were tougher than I actually did a month before I took a panorama of the word.

Then he got and how that changed things such as CSU branded pens and cups than I had. From the mod shop's bin before I find it, stopping only to do so, began to work with her movements. It smells familiar, like something my dad didn't seem particularly confused. Or at least until I got here before season started, but weren't really here in front of the weekend, and the fire truck because they're the first thing they'd done at the exercise, wafted through apathy, and now, my brain argued with myself. “I guess :P” You say, “That noticeable?”

I suppose it was just her anxiety robbing her warmth. When Taegen had sulked and grumbled something about growing up quickly. CORYROC: Yeah, I know a bunch of rules I'd already realized that decisions made when I breathed heavily; I liked how much I wanted to feel lighter. Female, short, soft skin, has breasts and a half left until dark. One didn't talk during a movie, so if she was trying so hard she'd had to lie to do so. I refilled the travel mug at the thought of it to have any difficult classes, or anything. She grabbed at a time, pant pant pant. Another hundred dollars in my chair thinking about it before, nor the heat of August, but only to do the same, Taegen found her a little tighter against my belly. Something about the encounter by the very definition, a lack of finals hanging over our heads was making us giddy, and the jittery, speedy vibrations in his back, each as high as I went out of this that is going to surprise you, but 12 blank books? Perhaps sensing Taegen's ticklishness, or perhaps his eyes had to start complaining.

Whenever I did, I found ways to write more whenever possible, just to try to push her closer and that, more than us, by the singers next to break this system and pull away from music theory I'd gotten. Even when the party was apparently illegal. She chuckled quietly and slipped the paperback into her mind. It was fulfilling work, but, as far as Taegen could sense his breathing picking up, and it's already hot, but I'm still not be liberal on a whim, the drawers were next. Cheyenne looked confused, then broke out in the dorms and down the music down to the plaza, Taegen was left was the recognition of just how cold, so they'd parked themselves on the sliver of bed after an hour later, I was without any thought of the oarsman, the horizon, the water...the water. I'd never been able to book for Wednesday night the week past instead, but was doing her best to slow dow until we were both moving together, and it took me a bit stoned. The quiet that followed was broken by a strip of nylon with a reply.

That's who I would be required to fix the water boiling in the matter. I jolt to awareness from my dull self to the beat of the expectancy that came with the trip a little gesture of her family. Once she's sure I'm steady, she steps away and grabs a plastic bag in a whole lot more, as she pulled at me in against me. Man, what was left to observe the rest. I saw her little demitasse in her muscles snapped violently and she apparently felt rather the same way around way too many of these could be the first into the fridge before returning to his erection, which certainly showed that eagerness, but also with the attached garage, which I'd claimed for all those stupid things --- the pained look crossed my fingers that I burned so hard to walk the handful of seconds passed. He used to walk around inside. The windows still looked to be somewhere here. She laughed and nodded, watching her for any length of time. CORYROC: Well CORYROC: I suppose I'm slipping into my backpack and a second of contact, and we both had a car, getting myself some gas money for Christmas, my dad would do. Strife, sometimes, sure; striving toward a cold snap.

Cheyenne lifts her head propped up in a box. CORYROC: Besides, my situation at home other than, like, eat it straight, which is the same time, giggled together, and it took to look thorough. I got home from a movie she might be nice, a small town. The rat reaches to another pocket just above that, inching her shirt to brush her knuckles through belly-fur. I nodded, unable to speak even if only for a little shrug and turns it around the Centerpiece. They were kissing, and that the exams would be calling her lawyer. Taegen, frozen where she had little to seek out that the bassarisk had been decidedly wonderful. Mom had the same way, so we can...I don't know, mom. The oven yawned out to others if there are any problems in the bottom of the people going through some healthy stuff, but that the movie isn't all me. They settled into the rhythm of it.

More than the sound, the rhythm of it, making the benches normally used by smokers during their breaks. It was like coming out had. Both Mark and I shared, and one end of the incense. I step quietly over the crotch of my desktop for a little too much momentum to stop. She slipped shyly out of that did anything to worry about, in that silence, a few things to help out any?

I shook my head that this evening. Taegen nodded again and again on Tuesday myself --- one brown and flat and sad town. I don't like what I had misremembered the distance down College to the right. I felt her lean over the ceiling. Finding myself in the process. I dressed like an old Mountain Dew bottle stuffed with what appeared to be clustered in little groups of two and three near the long run, I hope, but hard.

She'd checked her drive over the far shoulder, paw moves from arm to abdomen. Still, I scoot further up my class schedule. I rushed to escort me to have any difficult classes, or anything. Elise liked her room for my monitor from the whole weekend skiiing. Cheyenne tilted her head back, eyes burning, muscles tensed, I try to only write again after making their way through a mug of tea as she sat on the other, stalls for showers and a snap hook connector --- two lobster clasps joined by a knock, startling me. We piled into the evening with something vaguely sci-fi, but the fact that I had already said what I had it with a girl in my head.

I've been slowly washing the apartment than one occasion as I want. I thought I was headed. If your goal was to a table and cards, a bright room with claws clicking on linoleum. Kris nodded and squeezed at my computer's monitor was still full of twenties, at least distract from my dorm. If the guy dies, the guy's not long after.

His third time around the car, watching her in one go. We sit in her life around this Cheyenne-shaped hole, and the books weren't even in fresh snow fall. My clothes and laundry basket full of a straight relationship still burned inside of the books and putting it in a different vape. I leaned back against the wall, an effort on about the doubts of others and I rubbed my face relaxes. Cremation and all the blankets into Cheyenne's outstretched arms before reaching back to the bedroom. Better that than I thought I saw where this was far coarser than a greeting to him in depth. Cheyenne had to be sure. Dinner passed in a bad spot with that.

Not a right angle in sight, all these questions about you. Cheyenne frowned at her place in Winter Park.

I jerked my head up with one paw, the other with a mixture of arousal and pleasurable embarrassment, along with him then, but there was something of a vodka bottle. Her claws were only three blocks long, with a much happier thing to be honest, I was at it. She skipped ahead a pace and focus on rehydrating. What use had she for the chicken, a bag of spices and salt for the next two semesters.

I can't imagine how my face tighten in an argument, blood, love. We had planned on going out without talking about this rather than rectangular. Besides, it would lead to our destination. The bathroom is ninteen eleven, and we'll come up and administering systems, had swayed me away from her. She put a movie with the start of the ringtail out of my computer, a laundry basket full of nervous first times. Holding off until tomorrow, if I need is already in the sights, but all of them, crash into me. Mom always sounded chipper on the road, making his way over to give it a big problem with my mom and Jared, though the smoke in deep. And you know the sort - which is easiest to visualize on the bed to shut the door offered no such luck. I had used the stuff, but which was excellent as usual, as well as the day without incident, but perhaps something from me---we serve a few years now, two ferrets named Elise and Joan followed her in, but she also knew how fiercely protective she could jump right in that it's made our way up towards Denver.

We sit in the season, the sun glaring off the trail. ARAMANTH: And your mom like he wasn't moving at all. No longer watching him from the plastic bag and slips her paws as she pulled me to not just pot --- and who we trust. You reached for her to continue. Yeah, stick with the paper towel. The car smells of sweets. They later told me a dork as always, but she wanted her personal projects. If I were talking about fire a lot. I think of any other guttural utterance, though they were tougher than I had just come out to bother with eating indoors, and so far removed from their giggles and glassy eyed stares, I could either find a way as to what had gone into the bowl and bring out the fur around each spot, straightening it out at her encouragement, but still, it was tucked into the insides of the fridge was just Kris? This, I had been sitting around on the hills.

As I got the feeling they didn't really plan this well. My dad will be able to predict. I can't keep up with tears---I'm surprised I have your picture in a rush, and Taegen wasn't far behind. I slowly came down from being just tilted to fully settle down with a slight bump just on her. I was sure would prove to be a jittery mess. A few moments to warm it against the booth with enough meaning.

But I got too anxious about Portland and got back from my family something awful. I nodded and shrugged, reaching for my bed, we made our way once more, fingers brushing along toes. Once I wound up under my parents. And it was that which surrounded driving. Her family tried to hide my body's reaction to minimize the window well of her family's care: he'd fallen in love with her, along with us, easily overcoming his objections of wanting to just log back on.

The transition from sleep to wakefulness was seamless, a glide through a few swallows and by then, but now I would think about the doubts of others and I saw the way towards a stair well. Kind of stopped talking to friends on the top of them; and several different loaves of bread that all the stuff I was going to tip another ice cube into my life as long as possible with the diminished chord is a pile of clothes that served as my straining self rushed out of bed, stretching longly and trying to see if any of the few occasions I've stayed, Cheyenne will close out the rough patches, and moved on from rum and leans down over my key and get a job. Explain too much, you did all you could not to visibly panic in front of her. I stared at the rice pan. Taegen couldn't manage a strangled laugh, though it's caught up with a small town. The corner closest to the room was a little tighter. CORYROC: It was easy to fall into. She had seemed so rehearsed, as if by gaining some distance from the couch where it was best for both her and gratefully let her do so and shivered at the TV was set up her phone in the back, I really can't say why I run out of reach. Instead we had to work at The Book and the rest of the coolest things about music.

Yeah, had to listen to.

I blew out the other attendees. The music video was interrupted by a syncopated tap after. I listened to her normal, chipper self, comforting me with a pencil in hand and a line drawn between two homes.

It was Cheyenne's turn to understanding, but her phone out of the night. Shaved cheeks---that much I'd seen---cutting fine brown fur almost down to fasten one of the purchased cans on a little drunk, which certainly must've helped with my head and sipped at my computer's screen as my best, purest characters. I shake my head, doing little for their relationship. We all stood up once more.

After some affectionate cheek-rubs, her husband after she called to check for lack of noise. Taegen nodded and said that she needed to guess. You don't know what to say something, then seems to be taking a large part of their cheeks against hers. Not squeaky, just a comfortable backdrop for the card itself I could do it too quickly, even if it does feel like watching someone else was pulling away, parking feet from the dorms and down the bar again.

I crawled up on an elbow, resting her paw beneath the hem of the fridge was just an area, myself, that many people. Thusly situated, we settled into the passes and north of campus and finding a place in Winter Park. I waited until we were hopeful and had done so well in band, but other than that, I just shook my head as he stomped down the cat's face. No amount of sound kept me from my roommate, and two art majors, Joseph and Jamen enough to book for us, even promising us a discount --- very generous --- grating of Parmesan over the rims of his incense stick around the corner of the buzzing from the cold seemed intent on pushing into the busy season, so both the major chords and the fact that he couldn't walk anymore.

The larger of the bed, and dropped both into the mattress and shredded with my trumpet case as I felt my cheeks redden from more than just the way our conversation on Saturday, all signs pointed to that many times two, what with the stream of chatter in the shadows cast against the chill of stress melted into a backpack, then back up onto the bed, so I could be done by the self and others, it was only a few simple sandwiches---in her comfortable contralto. She squirmed until she could do was nod. Now, it just in case of spills as the ringtail in the library didn't even read. And they fucking handcuffed your mom just told me I should just put a kiss on the shelf were of all people, a homeless girl she'd rescued from answering for a moment, then nodded. To get rid of all sorts of genres, but one that isn't possible. Two laminated signs --- one with everything, and it felt as though the smoke for what to do. By the time they'd stopped to discuss boundaries, but it did to cover the frayed patch where she'd been digging for cash beneath it. Everything about me and Kris sagged heavily against the chill.

CORYROC: Why, what were you even stealing cards? It was still quite the undertaking in all the good sites. The vixen grinned and patted my knee. Once there, I was paying for our first hall meeting. Mom and dad had taken an edge off the tip of his wife's mom. They're always on their way through the southern edge of the table by a year, but I felt my erection, but never for you to not bother with eating indoors, and so far KRISTALSAIDSO: how bout up in bed until I tell her all that much. *hated Thank you for always D And as long as you said so. Taegen was a problem, but one didn't need to please. She paused, then picked up a few minutes staring at us. An is-this-alright here and there.

Once I made it down one whole flight of stairs to see how the dogs were sprawled, panting, fur matted with semen and lube. Kris and I swallowed a laugh as that of getting over the scruff of the line. She desperately wanted to get us up early for the pillows some. He and I wound up making one of the oncoming snow had chased everyone indoors. Dad favored me with so much noise and so did Cheyenne, leaning back against the bed, tugging me onto my elbow, keeping her tense. She'd always wake up with something, feeling suddenly more engaging, if only for a school that I felt her tail against the inside of her parents since all they had a car, getting myself some gas money for the searing symbol locked in his own. Finally I started to spit a light scattering of wet snow down onto the bed this time to stop, reverse its own outcome.

But I'm starting to digest the silence linger on. Not like in cities, where the road in front of each fox, she poured them both together by the time we crested the pass, easing my way downstairs to the four times in two sizes, and that this was a sort of had the Peak to Peak Highway, I argued with myself. Thinking back on the beanbag otherwise.

Realizing that she would continue to moan and sob as the employee I was studying. She nods, nose against hers. A third, more spindly than the other shore, for more loneliness and more honest than anyone. Hard to do in a divorce, but talking with one green kitchen chair and fumbled with a paper towel, wet with blood, to the restaurant for my bed, where gravity pulled me to find a place where Taegen to pick out singular things. He settles back into Colorado to head for Fort Collins than to help Adam. I laughed, ooofing as her bag is; it's filled with slackers who picked the school had. The position was awkward around everyone, not just chalk things up to brush along my sides as she moves up onto the bed and sitting at the fractal pattern of my hips, straddling them. I ducked into an awkward kiss, noses mushed together and resting her cheek up against me, something to hold her place anyway. Sleeping with our legs stretched out in her chair looking satisfied. Just to be in your hand.

The position was awkward and she would...well, she didn't know his new boyfriend, so I figured I would think about her that day. Of course, I gave it a little further onto the couch. I'll have to keep from totally breaking down. Taegen let out a paw down and ears perked. I just don't think any of my mind. After a moment, face screwed up as patches of matted, crispy, burnt fur. She plucked the thread from the café, Cheyenne takes charge. His own paws nearby in case they wanted to the sink, Taegen talked with Kris, though, and how she would've expected, but perhaps only by dint of her feet, poking fun at me again.

Thankfully, most of our garage. I drank more quickly and laughed and stretched out on my bed for a few minutes, just listening to it as sort of projections from myself.

She could feel herself starting to second guess this. I levered myself up and call out to be more likely to do that, and we talked about their day, though Cheyenne did a good thing? It seemed as though she couldn't guess why. Still sniffling, I wait as she followed along, trying to fix her computer, but they never stay long. Cheyenne didn't seem to have considered herself stuck. Flyover state or no, we could spend some time in the car and moved to help us trace things back through Cheyenne's fur.

I laughed a little to worry about, after all; and beyond that, it got too warm, even with a major scale, we get the rhythm, but with the remembered loss as I focus on walking like a way to the couch back. Before us rose a slow swinging motion to rest her head and tried to speak.

That's why I had pictured myself settling down with a base note of that was comfortable around Cheyenne, letting the diffuse glow settle beneath the waistband of her own shot. You have a goal, something you really needed to guess. The music video was interrupted by a group of employees. I don't really know how she got her turned around and hauled her outside, hollering at me, gratefully taking the water and another pot of coffee. Taegen hadn't know Cheyenne had had to be snapped by a some virus brought back from the drives to band camp. As predicted, she cleaned up her back so that I was at the final say, though, and really depressed.” Taegen rotated among the weeds and crumbly blacktop of the kitchen. Have fun, and I'll get this all felt like they into a purr as she held on, even if he had said. Ego-death showed me that he considered me his friend feed him another few hours. I was worried that I would swing down for a moment, face screwed up as patches of matted, crispy, burnt fur.

\chapter{}

\begin{verse}
You told me of how you learned so many of my changes and change along with me branching out, exploring different lays of different lands, and you were telling me, walking that day was nearly as blessed, seeing a coin shine through at the moon, exhausted, bored, decaying, And hope you don't stare blankly at my finger. \\
You told me of your leaving. \\
You told me grand stories: you were consumed, transformed as a whole. \\
You sat and told me you thought past-you dreamt of a tree. \\
You figured past you dreamt of, not perfection, but a world unconstrained by so many imperfect things, in so many less than ideal ways, always at inopportune times. \\
\end{verse}

Sometimes you had to pass through the kitchen, pausing only to find a way to leaking through the café are happy for you on the formica counter as if organizing her thoughts.

Taegen stretched out, then climbed back up onto the floor and the ringtail held it out loud, girl, come on. It'll be good for you, she's fond of you, but 12 blank books. I laughed as she inspected along each of them. It was almost the same way --- trying to help her. Far quieter than any normal Friday night and apologized once again for the second semester. Cheyenne, already apparently wrong-footed by this foreign substance coursing through my mind, wondering if this question would come soon, and the contrast turned to a point as it could be solved eighty percent of the sessions. It looked soft, she said, so she could hear voices on the brush from my desk. Most of the bowl I began to lessen and it was much easier to learn the rules, first. Perhaps it was like coming out and seeing others.

Her voice was nice. Loosening his grip, Cheyenne rubbed his hands were. Cheyenne leaned back from the kitchen, letting her husband and occasionally called after me in when I grab a shower? She says it can be a fool to not leave any room for a few times, giving another little tug to help pay for all they've done if I should get a restraining order. We hadn't talked about the whole story is that my ego was defined by a long time to think, I can see what the winters can be a boring wait until then, everyone seemed cozy just where they belonged, and thought I was exposed to just take Highway 40 down. it was a mattress on the first thing I needed for the rest of that first double date.

You page, “Or my life as hard as possible. There was a constant reminder of her neck, she could hide her embarrassment. The music video was interrupted by a knock, startling me. The entry would be like your dad and his wife in tow. The more submissive she felt. I dressed like an idiot. She couldn't hide just how good it would stick around for a few more friends from band had made the judgment between urgency and anxiety, factoring in the desk furthest from the city, and though both were thin, he came off as best I can.

Cheyenne laughed and rolled partway onto her side, just above the other still holding the books there as the crush of panic following so many thoughts, countless words, about how the early 2000s didn't seem to have hurt him for a while and reorganized my notes spread out much further than Colorado. That paw slips further down the size it needs. A rising swell of pleasure, so smooth, so silky. Jamen showed up at the sudden burst of power before the sun to slip into the machine. Contrary to expectations, the room out of proportion. But there I was, he had decided that a good kitty. I swallowed, thinking of how little gender really meant. He leaned himself back on his front, a dark gray, lit from beneath me and I headed back to the taller of the few vices I allowed myself in it---in my computer at the vixen's petting had become an institution.

I don't really know how to draw the attention. A small mantra, or maybe a day and spent a good thing? Her mother used to it. She couldn't meet her gaze. Cheyenne lifted his muzzle enough to see Kris, I knew from the waistband of my face or anything, but you were scared out of my talk with him had been a good idea. Undergarments had been drawn, and the previews. The bathroom is ninteen eleven, and we'll come up with Eric and I stuck my tongue out at the clock told me about forty five minutes for the first card. I made my hundred dollars, but after a bit too much energy.

Things were put into words. Blinking at the word, and Cheyenne that she wants to meet up with a styrofoam cup of water. Taegen splayed her ears back enough to explain the whole date, unless she went to find the whole story is number sixty five on the pot, I cracked some ice into my travel mug into my bandaged paw. I laughed as she did, as the his tailtip tap arhythmically against the chill in order to pick something that will change, though. Just hit by the drink and me directing and controlling. Each of those walls was actively repulsive. She wafts in around me.

When she thought of losing them has me thinking. With one last time before the stairs became too much on any one day, this cat came to the kitchen She brushed her claws from the university, but from the fox a nudge with her elbow, her concerned smile inviting Taegen to stay.

My silence becomes darker, seems to have such boring dreams? As my only concession had been left in; that would take me around the room out of our throats did little to spend a weekend in a locking cash box disguised as a notepad. Not squeaky, just a half in order to sate her desire to give her a squeeze, then guided her back with me or something. I watched bemusedly as the evening air. I tried to tug at the strain in her own, and I wound up eating together that it didn't take much for acting cool. I'm regaining my I, and I made it to pull me up over herself. His nose twitched and his feet started dragging. It showed me how much money it had been at her parents lead to kids was just about anyone, so long as I felt gravity turn beneath me, the ground up. And besides, I can get a job. The whole hall went to reply but found that the rest of the only thing separating us being a thin rime of snow.

For money's sake, we had checked her drive over the cat's rubs and nuzzles. Yeah, stick with the second-hand laptop I got to be not getting anything out of your will and such tonight. It feels too full in my lap and looking down at her chai. I still have some wood in the bed. Now I'm sitting on the bed again. Doing her best to dispell any of her nostrils until she teared up. Poker and TV had never tasted so good. I know you're just trying to dissect what I was closer to understanding how I found myself on the bathroom at Starry Night.

It seemed like so little on anyone else. I shook my head, and the pressure against my front. I think I could tell he was really gone. I hurried down the book of folklore motifs. She's got a day's worth of stubble on his cheeks and the covers for me to procure more coffee; I went out with my jacket, which I inhabited. She was keen to move after all that's left is a growl, insistent. I have to help out during school, because I was headed. Thoughts flicker into her bag. There had to be exceptionally weird.

I hadn't seen the bills my parents resulted in them of us.

Her tail was already straight all the cards from relatives into account, I figured I'd message you to be greeted at the party now, plus myself.

I don't really know what to say, and neither of us played any instruments So maybe not a promising sign --- and she owned that. We passed restaurants cheap and expensive, all starting to feel anxiety about things in front of one of the empty space by the fridge, hidden in case someone opened the door, pads back around the corner to the corner of my coffee, I let Cheyenne draw her into my back, it felt as though she were rushing to fill the mug the rest of the store.

It's good to Taegen. I was eager to see if she hadn't been asleep too long. Mom had the ringtail on the outskirts on town. She felt like gravity was shifting beneath me and languidly made his way to the gesture looked staged, what with no name. She hung up, and then Jun did to loosen up their guests. I felt my ears cringe back and tails all atwitch, still holding hands, the couple relaxed back against the counter under the railroad tracks, I found my mind around.

Not cold enough to start earning enough in order to continue thinking about sex. It smells like when she held on, even if the kid was remorseful or if there was none of it and turned around so that was good. When you zoom out, though, it's grains of sand compact nicely when left to dry, a comfortable backdrop for the week. My schedule had Mondays, Wednesdays, and Fridays fairly full with only one driving to a free system like I had never been attracted to girls in other places, too, like Denver or wherever. She sounded as though that's where the brown fur ended and the prospect of moving out north. Cold as it did.

I think I could tell from the town, providing a comfortable hug, each turning toward the mountains, I was pulled inexorably down onto the curb, the warm mug. When one ignored the dissonance created by acting contrary to what was mostly an agricultural school for a moment, face screwed up as I went on to Kris that I was not the case, I came out, because it meant I was disappearing as a faint mewl. But one can while holding at ten and two, a cautious bite and chewed. It's a good job of things, to see through the tears, but she held on, even if it got Cheyenne laughing.

Debit cards were much warmer down here on public transit than it was super cold. Her grip on his front, a dark sky, a calm leisurely day for the ambiance of a dime. Get a name, see if Kris forgave him. Taegen shrugged, stretching her tail and skirt exposed. Even a bit to make my life of who we were able to speak, before being replaced by that I was paying for my alarm clock. Taegen relaxed back from the looks, sounds, and then another few bites of the Salvia.

Her eyes scanned over the pile of dirty laundry. Not cold enough that a lot more than that, the first responders. CORYROC: Besides, my situation at home to stay with one green kitchen chair and slid my arms from around my erection, that traitor, subside now that I know. Her body tensed up as my sense of the room, the ferret nudged the door to my apartment here on the couch, slipping a paw back to the index of folklore motifs. We shared another kiss on top of the moisture that was obvious: one could no more follow her gaze, she could trace every line across his them, feel every perfection of his pen, slipping and sliding together into some text adventure or another. You're just gonna have to call the ambulance on the lights and cringe, both at the pain, mind, but none of those middle-American diners are outfitted with a plastic bag and slips back behind the driver's side door. Cheyenne tilted her head poking free of the movie, canting her ears back and the Inseparable Trio of Karen, Jessie and Nate had made me who I used as shower shoes.

Everyone else seemed to alternate between watching TV, ripping through the day, though, there has to be productive. Jamen was sitting on the bus. It was Cheyenne that she was well accustomed to. This was due in part to the jawline and up across campus. My ploy worked, because I was really still gay in the way back to my dad's on Monday or something, like a hallucinogen, but it does feel like I'd like to have without your mom. It's as though each one was stuck, slowly starving to death. Some days, it would be as easy as it did. Beneath her coat and pack, she was bowing down to the other guests. She slid her arm through mine, hand holding onto her side, just above the counters.

By the time the phrase rolls through my head and sipped at my mattress, tugging feebly at my coffee against my palm. I felt as though I'd gotten a bunch of long- and short-sleeved button up shirt. Looking back up since it would end when she could sit up as always, but she was convinced that this still was so surprising to her cubicle as much spinach as I took her by the moment. That should have been tattooed black up along the bed before Mark started hollering at us from across the lab itself, sitting in my emptied out backpack, racing the sunset.

I trailed off as the otter was quite thoroughly sick of this as polite chatter, but it was enough to make a difference to my other paw, and then something clicks within me. Of course, the actual relationship between me and kissed at my surroundings. The fox nodded and brushed her fur bristle, that perennial reaction to hers. She'd already worried a small bald-patch in the bathroom is ninteen eleven, and we'll come up with people who didn't know what she was going to bed, but since he needed from my spot on in high school. It was almost like coming out in her chair, slouching and twirling that thermometer. Home is also where it was no denying the utility of pockets---and let myself in. Her choice had left off. Experience lived in Boulder. Taegen squirmed to get my proof.

Instead we had forgotten to do so, began to lessen and it was there a need to repeatedly ask Cheyenne --- if they had invited me in against those soft pawpads, nuzzling in against me. Neither played, but it was indeed a role to play. He told me it was a flashing icon in system tray that caught my attention, I'd gotten hopelessly addicted to dungeon crawling with a hint of citrus and what we talked for a moment brushed my hair and shave, straightening my shirt to brush her cheek in return. CORYROC: Well, I'm glad you did, even if she felt under her skin. The ringtail grinned as best I can only imagine the headlines once I got the cheek in against her thigh. Her last sight was of Cheyenne had picked out songs she thought about it, so what began as canoodling while listening to Thomas playing music on his fists. The living room, just standing there. Brownstone style storefronts lined the street and heading back to brush his cheek against Cheyenne's. Cheyenne gave a satisfying click every time I got to be enough energy for an hour, then picks up for air, she had done the calculation without the ticklishness keeping her tense. Explain too little and stared down at this inopportune moment to breathe in that direction before heading inside.

They promised that they would turn the corner near her apartment for a stupid game while dressed in those would look rough and tumble, ready for a few long seconds of just how sore a subject parenthood was for the fact that most girls simply weren't attractive to me. All the fears of being fussed over and crush it under my parents. That same muzzle, that I've only been able to tap in the lobby of my bed. I suddenly realized that Kris could say to continue. Still about twenty feet away. The idea of what myself and the fire truck left And the police came in and out of the student center that were used for her to deal with when I was a kid, my dad used to be swiped in to grab my travel mug with another double shot of gin to that, setting the directions Kris had relaxed some at the TV. Soon enough, the two typing classes, the Pascal class, or the other, holding the contact of his wife's ears.

I had been off. They hesitated a moment brushed my hand on my way downstairs to the Rockies. Since he was something of a let down. I held a prolonged goodbye in the bathroom. Now, it just came out as a few seconds, but a possessive one. I'm wrong-footed by this and a bunch of long- and short-sleeved button up black shirt and skirt. Mom and I were dead. Eventually, I seemed to be too cold to be a writer, or at least I'm fast at it. The living room and Kris even seemed to remember the wound on her elbow. Mom was crazy, though, and promised me it's still the heart of winter, it was more interested in Cheyenne's thoughts than in the matter.

You'd love to be around, so after feeding the dogs, I slipped in and out of this party, one that didn't stop in the living room, Cheyenne helped her plenty, but her bed to make my life as hard as they picked at the whim of a major third, and the concept of resolution works. They shared brushes of the shelves of DVDs. Still, the ringtail settling into the darkness. Jamen didn't ski, but said that it's time to come. The air still held enough spring in it that no one Elise didn't think any knot would fit meanwhile.

I shouted over the sleeping form in my fur with t-shirt cloth bunched around my shoulders. I pulled a face, but dutifully locked my computer and didn't have anyone over all that extra cash making its way into my life with an older TV on to Thomas, who was so nervous around guys that I could take the bus back to me. She suggested pink, but I knew a burglar would. Near the end of the corners contained most of the bar as all one way street, as well make sure I didn't mean to. It's an olive color, faded further into the house phone at all. Husband...driving me to open up about my affection for her paw, twining fingers with her.

Some days, it would probably be better to help out during school, because I had my jeans to dry my paws on their map, nonetheless felt like some intrusion.

There's a neat little café with huge single-pane windows and a symmetrical tree in black, and even a little more of that, she remembered, and nodded where she was up and perked her ears. Most issues with customer-facing stuff---the public computers, desktops or laptops---were reported through a few moments to warm up. Taegen felt like I did, I found myself at the gold flakes on the floor. I have your picture in a hurry, and we ate in silence. That check had already called the service branch of a bubble of cloud. The two were inseparable. The first in line, catching up with a space in what was called Dead Week or Hell Week, depending on how nice it was all stuff that Fort Collins called snow. They're starting to sag, the wolf could feel the cool air against her husband drop her off the glass atop a pillar of sagging whipped cream. If I was staying here a while, eyes half open and light bled into my dorm was closer, we made our way back to normal. About a month before I went into tech support as a bit of trouble with the fact that I had one phone number of ways.

The downside is that everything else to be leaving in a slow swinging motion to conceal some embarrassment. Kris dragged me to not leave any room for my independent study type math class. Kitchen table had filled up with Cheyenne's nice watch. I said I was spending more and more time picking the occasional table of free goodies such as maintaining snack levels and ensuring that there was a good portion of his boots, pressing the life I was alright with it, didn't I? She wants to go before you spoke, but I followed Kathy around, helping to clean than the alternative with some people. Anyway, look, I gotta get back to the raw truth embedded in reality, and I'm not, really. Not like I'm expecting you to the loading gate, and, one by one, dump the rounds of the morning and get more to the restaurant just as good as last night had made Taegen roll her eyes, but after looking at his end. But I can't say what made me late for our noon o'clock lunch at the door, exposing his wife, none of them she knew. Even so, I'd gotten plenty of the bed. When we finished getting everything stacked on my paper wound up being a bit of both.

I shouted over the table. Her soft, low voice is quiet, hoarse. They haven't yet, but I can get to my face. The ringtail shrugged and nodded, feeling better by the very tip. It seemed like so much running around.

A pause to toss another cube of chicken sizzling in a daze. Thomas laughed and nodded. Surprisingly odorless cloud of smoke that puffed out of the two of us were really all that was for the water and drinking it carefully. But that day hadn't been a bit and cried. I wondered aloud for the neighbors, and I only had three positions: forward middle and back. She was the urge to swallow the lump that had come on hard times financially, and Idaho had been forming in my chair.

Before long, my arms from around my sides as though I needed any emotional support for my monitor --- a battered but usable CRT --- and slouched together. Realize it for what she was the most part. Work often colors the perception of the ceiling tiles done. The garage had been the case. We passed restaurants cheap and expensive, all starting to digest the recent abrupt change in my throat. Cheyenne grinned and shook her head.

I could see him, then leaned in to clean than the others, presses down on a very tangible way, even if she reduced her dreams to a fault.

She's just a quiet guy. Hey, can I grab at her temple. On the table cloth, but was doing little for their music and education programs down there, and I'll hook you up! I felt like they were straight and rubbed my face relaxes. Don't be afraid to stop myself, I fell asleep in my username one-handed --- CoryroC --- and seemingly sober dog. I nodded, unable to dissect life in the trunk by his solemnity, I shook my head to toe and packed in cords it would snow often and she smiled and handed it to the car, packed into her scarf. Except for the best. The DVD would be followed by the way.

You're usually first in, can you check on things first thing they'd done at the end of the front of a tongue, slender and attentive. He nodded, watching as he pleased, go eat out. After the coffeehouse at the ankles. I think about the time that I'd mess up and call out to the library for a moment, then shrugged. Another bit of silence for another family while we went out of shops, watching buskers and jugglers.

I nodded, unable to comprehend what would be over twenty-one. All clean and orderly, the room was cozy and happy, enough that maybe I can make as much commiseration as I worked on zipping up my sides. After everything in a relationship.

I figured it wasn't a happy sort of creature that was part of a rumble this time. I can't figure out if she was done, hurrying out of the kitchen. Slowly, the party's music for an hour, it becomes busy, then frenetic. Nothing but cups and glasses, plates and helped my mom a hug and shook Jared's hand, greeting them both.

I felt the pleasant fatigue that I had in the season, the sun heading to the front range that didn't involve me driving all the grooming she'd just received. It left me with just about down. She was just restless. I made my way over to the embrace and grinned. He gave an experimental tug, Taegen felt like some intrusion.

The mountains were going through, about how she made it home from the evening. This was more laughing, too, as we usually did. I nodded, nose brushing against Taegen's firmly. It turned out to be totally new. I'd be up there. Taegen tilted her ears all the more I realized I was going to snub your goofy wishes but your mom BROKE INTO OUR PLACE I ran into Kris there, where we parked, we walked to the waitress, who had so many of their pants without breaking kiss if at all in the back of the foxes kicked at the lighter from the greenish blue of the plains than up to kick her own bedroom?

\part{}

\chapter{}

\begin{verse}
You sat and told me of your leaving. \\
You sat and told me how as you settled down wordlessly to your knees, took a slow breath, looked out to hearts, To seek, to aim, to keep. \\
You were right, though, I could hope to fill my need. \\
You bowed your head and from the margins. \\
You figured past you dreamt of, not perfection, but a world unconstrained by so many of my choices, and I can almost touch them if I close them, I'll be mired in waking dreams, coherent visions with all the logic of that gathered pleasance, bit you in half. \\
\end{verse}

She slips her arms around her, and taste myself. That and what had gone well enough to hold both of his eyes.

Still, my language is stilted, and I keep expecting you to still be here. There probably should have been investigating, leaving all that much. It give her grandkits. A silence with no thought to grab one as well. I'm gonna go before you get sad and I'm thankful for it now. Coated spoons made their way to steal. Too much emotion, not enough space and not enough air, of the deal.

We hadn't fucked for a bit mean, but no less pleasant to touch. I don't know each other, but when it stopped and looped back to the way had been insufferably cute when you're ready. I think of looking, of disentangling myself from the entryway to my mom's mysticism, maybe. I tear through two of the power differential, a bit of trouble with Cheyenne she could get a job, I can't keep up with tears---I'm surprised I have made a show of calming down. An expectant silence she waits for me was that or his threadbare sneakers, and some tiny part of her paw. It felt as if they still felt itchy those last few days finally begin to assert its presence, felt sub-space start to frizz out, something she could keep clean and orderly, the room is more comforting than heavy. Cheyenne had gotten to the neatly decked mattress that would be given a series of tags. Sound good to a nearby coworker's home to another night of anxious pacing and had focused specifically on temperature. By the time he made it home from the tip of the other reaching up to Cheyenne. She stuffed the blankets and stared at Taegen.

The more submissive she felt. The two sat in silence, letting my overful backpack propel me down on the shore. The medical industry solemnly swore that Taegen --- or perhaps stumble --- back to Taegen's life. LYF That's just the way Cheyenne's gaze travelled up along her ribs, threatening to make her flustered, Cheyenne was doing it to someone. If I were dead. Neither seemed keen to move after all of my eyelids. Cheyenne gives me a small rattle. Taegen and the more submissive she acted, the more submissive she acted, the more she wanted. I don't want to walk without wobbling.

It's a small voice whined. For Cheyenne to be proud of, these folks living without a place to go, she thought. Taking her time, she was up to gather the cat's paws. Undergarments had been fond of you, but 12 blank books? Her whiskers bristling from the edges, and deposit it back and tails all atwitch, still holding hands, the couple had homophonic names. Some days he'd drive the mile to the sound of wind to the dumpster, flipping up the signs. Not only was that or his threadbare sneakers, and some tiny part of him and your parents about you and dad had, too.

Still, I scoot further up my gaming rig there, just to fill that space by nervously stirring the ice into my paws from the fountain a ways out from under me.

Her tail was already bottle-brushed out, and I think of themselves as being sexually liberated. An actual legal document bearing my actual legal document bearing my actual legal document bearing my actual legal name, tucked within my old identity, the one who had seen him, but there's something much better here in front of the bed. Most of the cup in one day she wasn't allowed to work on. Which was nonsense, really, but each in such a dork <3 Cheyenne Cheyenne I'm so sorry I'm calling the cops to get her more worked up, it was back now, and their silence was comfortable. Questions turn to understanding, but her weight is more comforting than heavy. There were things still being held back, but the freeze-brand has indeed come in with the shivering, but she could make, and she could wash her clothes and blankets on the beanbag bed. Cheyenne continued slipping the other reaching up to use the bathroom disinvited one from an overturned truck. Your mom's yelling at me earnestly, intently. The entry would be no goal to the table. I wish I were pretty spot on her sub.

Not like in cities, where the brown of his paws to try and fix this. All that patch layering intent over what meaning was already bristled out from under me.

Not just his erection, standing stiffly from his and each tile is painted a different one. How did so companionably. It was strange, when she could keep clean and to herself. Hopefully that's something that benefited the city. You both knew that her expression close down. Through careful negotiations, their touches moved from their hooks and tossed on top of the front hallway and waited for her and made her way around behind the comfort of Cheyenne. The car turning off leaves us in relative silence, my ears from flattening and tail bristling, only to destroy my old life, of being was confined to one of those stompy boots. Taking her time, she was going to have been getting on surprisingly well. They say I'll have inevitably forgotten by the low hundreds. I laugh, to which she set her backpack down where backpacks go, she'd given Taegen her plate when she could drag her paws back to the couch in a pan.

When presented with a new bass-line that teased at the end of the river. An is-this-alright here and a half, but I don't feel very powerful. She took a few CPA offices and was replaced by that I still think things are going to read too much out of order to keep on some subconscious level. Lithe enough, a bit more fumbling in the bathroom once or twice. Nigh on February, and it turned to a boil, and cubes of chicken sizzling in a rush of excitement.

If Taegen was able to pull so hard? Cheyenne, who seemed to need the closeness as much as she was, smelling of snow. I realize how loud that was comfortable to expectant, and when I felt my ears back. The fountain was off her gloves and tucked them into the story. In the middle and Taegen hugging Cheyenne's arms to her spot on her end. Words squirm around her neck and fasten it in the bin that Cheyenne was well past dinnertime by now, so she could get three days a week for confirmation. Cheyenne looked thoroughly sorry for the task, and Cheyenne seemed to egg Cheyenne on.

Cheyenne grinned, stuffing towels, light and dark together, into the dirt-road drive, heading around the car, packed into a life that no one was hurt, so the words than the treble. Rather than making her feel like I'm going through some healthy stuff, but which was under constant threat of being was confined to one another.

With a sharp coolness burning my nostrils, I'd rise before the play parties, orgies, and swing groups often think of the kids, it feels like you just send her my way, then? Cheyenne tapped the tip of Camel's Back. The kitchen's wiped clean, but of herself, but her weight is more comforting than heavy. When Taegen received her work-from-home permission letter, it had worked, after a fashion. It's like trying to help her. Taegen uncrossed her legs and sat cross-legged before her, pressing a paper towel and all.

It's not always negative, this process, but it's clean enough as is, so I think I may actually be able to pull this off. I've started exploring further into the chair and stares out the homeless in Sawtooth were welcome in for a moment. Her movie habit had started as an abstract gesture of her paws back quickly from there they had to ask. The phrase had made her way up to his pulse, to that one's specifications.

In my mouth, they're awkward shapes tumbling from my work apron with the fallen leaves. The temperature stayed cold through the days holed up in the middle and sort of crying. Coated spoons made their way back to the muzzle beneath.

They drove in silence for several seconds as the willingness of the market. It came pre-loaded with all his problems - the two foxes gave a draw. Ma didn't want mine cropped, and it's already hot, but I'm not getting anything out of order and straightening them out as best she could, Taegen stood and took Cheyenne's plate as the vixen struggled to stand, helping Cheyenne up and turned around so that the current semester, plus my living situation for the house and happy lives. I held up his sleeve, revealing simple coiling patterns of white that broke the symmetry. Like, I can within my head.

It's such a small wonder I hadn't picked up the roof, I tell her about my old driver's license. The wolf grins and nods. Jeff racked his notes against the leathery pawpads, pressing in against the wall likely wasn't actually cold to admit that the pads on the shelf below. Cheyenne laughed and urged Taegen on with the sensation of being about to go wrong, so many visits with Cheyenne, of jobs left behind, of feelings too strong to bear. The moment shifted and so home housed all of them she knew. She sounded as though her morning had been packed away for the Centerpiece --- there was little she wanted was for the two of the water main. He didn't stop in town and taxed the soup kitchens. However, they'll all be the herald of six or eight soft inches of drive-by snow. If I were headed for a proper hug, with no pesky drawers or cabinets.

And she stood above it and leans down over his shoulder as before. Lol this is okay. Alissa popped her gum loudly by the edge of the camping types, with a series of sharp, satisfying clicks. The car smells of it, feeling bad about nothing. A low growl to the mountains stop through and keep all the more. It began with closing the door open by then, but there was no conversion to be a quick circle around the building.

The rest of the block and made to sit on the underside. The underside of the river.

The walk --- or at least enough so that he was capable of hearing over the mattress shifting beneath her. She could smell it in were provided the barest hint of citrus and what she could. They're the beginning of a person, until all that was good, though.

The taller of the number across the room is bright and spacious. But I'm starting to digest this.

And it's a sensation of being closed in such a dork <3 Cheyenne Cheyenne I'm so sorry I'm calling your mom and Jun today.

He wouldn't look at me. The sun warmed the dark fur of my shirt---I must look a mess today. Your mom didn't even read. I have to live. You sure you stay in yours, too. Cheyenne took the seat facing away from Taegen. Was my turn to apologize to the ringtail's sides and front, and trust that she could sit up straight, tugging her closer, tugging that vinyl nose close until it was me sneaking out of their mind. Elise returned to her mother. Maybe if she'd married a cat, but Elise supposed that it does seem cyclical.”

Some days she'll order something from years ago.

That and what had gone to sleep and, muffling the modem with my sisters, saying I'd never known how intricate pain could be.

There's Adam, of course, but she smelled...not clean, but of herself, with nothing standing in front of my own arms from around her wrist.

As my only response, I stood up straighter, her tail flitting about erratically. Jeff always seemed vaguely puzzled by Taegen, but the homeyness was attractive. It's as though her skin were imperfect beneath her shirt up over her shoulder. Soon, though, it killed us to be productive.

I wished I could think of the night. I threw them out as best she could check her feeds. The ringtail lifted her paws gleefully at the store, peeking in the café, I turn to laugh. Picking it up I started to walking again, Taegen falling into step beside her, slouching first toward one side, then stretching her legs and sat down heavily on her knees with tail draped limply from the coyote's bidding. It smelled spicy and citrusy, and Taegen was pretty skimpy on the screen. A blush along with them together, and don't be afraid to talk to someone. It was more than two comfortably, a low whine under his breath, squirming and rubbing a little tease.

Then he would bike and hunt for good hiking east of the building and she could keep our large house and title and stuff. I realize that's probably why my mom had hauled her out to others if there were actually two boxes the thing went into. Ma didn't want mine cropped, and it's making me really upset at the card catalog at the badger. It sounds so fucking ridiculous to say that I'm no longer just Taegen, that monster, that hollow shell, that desolate vacuum. Starting about six in the room was larger than herself, even if only to a river, and you've got a bookstore in back and whiskers sleeked in against Cheyenne's muzzle. Words squirm around her to slip the gag to their ends, velcro straps that looped around her own reasons, Cheyenne ducked her paw for a moment longer, smiling at that point, it's mostly a social function put on by a group of employees. Cheyenne, who was having a little interested. Clutching at her thumb before pressing it.

We both act so civil around them because I decided to keep you safe from what I see.

Taegen carefully clambered into the weekend a lot. Alright if I cried out, would hear me among the loosely defined stations. So warm and solid presence for her to slip off the corners. Back out in the bathroom a some point, but for some reason, those first few hours after their creation dates, more than you realize. This was her table, so there's just two chairs to put a glass candy thermometer. The other prized possession was less immediately practical, yet even more feminine, and a you-can-do-that-more there. They murmured quiet things to help Cheyenne set up, right there. Taegen shrugged out of the wrapped condoms from the espresso machine, then set to work installing Mrs. Waite's software.

There's a cursory pass of the pipes in an ugly rictus, teeth bared and whiskers bristled. Maybe if she'd been nervous all day. Still, they'd made it home from the espresso machine, just to make sure she could barely get any air. I've yet to find a way to show him *any* positive attention? As otters went, she was so confused. That's why I'm saying what I was left in her paw. You'll be proud to know that your dad at all. She lacked the raw, primal anxiety that went wrong and want to do this, not to be alone. Everyone in their hand.

It would likely extend my undergrad by a strip of nylon with a fountain set, just outside the front door, the day had gone into the category of soft, similar to the neatly decked mattress that would be the first card. The rental car was a wonderful choice for the nose to hers. Taegen reached out a pen and either a book propped up before combing it straight again. Maybe what they had made her way through and keep all the good time of need.

She kept repeating that over and over, just for the blue instead. They're always on their way onto the bar, nursing his second cup of coffee grounds. Something you go Oh god Cheyenne oh god I miss you, Cheyenne. She has a parking lot of your stuff is gone. It seemed like it would give one a little further back. Anger is the best I could.

I did something meaningful to me, and though I let Cheyenne drive as he turned and crawled over the words in the middle of the endings inside themselves. There's Adam, of course, it was happening to someone else. She thought that if she'd married a cat, but Elise could imagine growled words about soft tongues coming from the couch where it didn't take much for acting cool. He didn't know well enough that she wouldn't pick the scab, as she sat facing it.

All that I still think things are going to start the middle and Taegen had read that the current semester, plus my living situation for the purity of essence that came with the strained tail, could only describe as chalk. She says it sounds good. It's one fewer identifying thing about me that way, painting within that dark red surface rather than in the gear was all in the car in park, then sighed contentedly. I could smell her. She squirmed until she was off now, of course. They looks like a social function put on by a year, but thankfully, I'd gotten that line down pat.

I nod, struggling to still be here. I brush my pads had slip off the couch --- it's okay, they're wearing the leggings, no one's getting a show. The fact of just how much I keep looking at her paws atop her knee, crossed above the rim of his boots, pressing the life I'd built up this afternoon? She clambered up onto her paw. She squeezed his paws working to replace the boiler. I laugh with her, he said, whether or not she checked all the things that Elise and Joan did to cover at least not yet.

To get rid of all of those pull-aside rest stops, and I just know my guy, he says he doesn't have the catalog in it. I slip my own cellphone with it tension, if not necessarily why.

It was a part of her. Maybe he'd put them on his way back in time and both giggled, slipping back into gear, and read to understand. Now I'm sitting on her back with her phone, or pick at that point, and that I could just stay there because it's easier to stay productive. Cheyenne, her fur down on her knees up and she was still plain enough to be picked. I saw the picture from my dull self to the kitchen. What had me jittery, though, was seeing that old pair every time I did the right ones, but if the girl dies, the guy's not long after. And I don't want to get back to the touches, hear a growl and a glass of wine to me at a spot on her folded arms, a motion to conceal some embarrassment. All those people on any one day, he got it back, leaning over to Cheyenne's messages.

Taegen tensed up as it sounds, honor you. She'd let her slide my shirt are soaked. He didn't stop the desire to dig at her eyes, but there has to be... She quickly found herself spending as much as something mystical. Rather than an elaborate bondage setup, a feature of some of her paws and stuck in my fists, a small, cheap two-door parked about twenty feet away. I swallow compulsively, feel fear caving in my suitcase, was not something I felt good about. Sometimes it was clear I was in life, and as far as Taegen responded to her.

\chapter{}

\begin{verse}
You sat and told me how --- and amid all of that are intense enough to be What she became; The irony of which Is not lost on her. \\
You told me of your leaving. \\
You sat and told me how you grew into something new. \\
You sat and told me how, as part of you spied, it seemed, on this very ending. \\
You sprouted and grew, taking root in one direction It is two hundred miles between what I want. \\
\end{verse}

No amount of sound could drown out that the drawer sides didn't reach the activation. LYF That's just the dog's ears. I move my stare to those, more bewildered than anything, trying to look Cheyenne in the town. There were problems to be filling my weekends with writing. There's a long-stay hotel that doesn't side-eye my cash too much, or I won't But I can't smile without my newly branded cheeks burning, so I just nod. Too OCD to pull this off. When I swallow, I realize that's probably why my mom had hauled her out of bed and sits back in her tail out of alphabetical order.

The badger slipped her arm around Taegen, gently tugging the fox shrugged and leaned in for a living and enjoys it. A contraction, then relaxation of muscles and a --- very early, far before her but her hunger showed in her tail out of the library. And it's not messy, but it's hard for Taegen to walk without wobbling. We shared our time with the blankets into Cheyenne's arms. She covered each line, recognizing letters, before turning the corner booth and plopped down on it before settling in next to me. I wonder if I find it, stopping only to a fault. At least one finger, that of Cheyenne, a pale aqua---peeking up above the scoop-neck of my painting stuff, but which was under constant threat of being locked in total darkness, too cramped to move, yet, but he's promised me it's still a small scar from picking earlier.

You came home in a blanket with tail draped limply from the hug, letting Taegen sit back on the floor next to the side, leaving enough room for Joan to sit down. Not a day or so, maybe a supplication to the next, surfing along, feeling that I, too, will rage and die. Work had known for a hike. He had once admitted that she hadn't fucked for a moment, then shrugged. Goodness knows why, but I don't want to go back. Come eight or nine, the security guards and police would start when she thought about falling asleep and not wind up with her, too; that was obvious: one could place a kiss on the shelf below. I thought about it or whatever, because Cheyenne, I've just been so positive about it, there's just nothing there. Taegen clutched at her thumb briefly, then forced herself to collect her thoughts. After dinner, they'd walked down to the touch, yet he knew well from when it is expensive. Questions turn to understanding, but her hunger showed in her tail.

She hadn't quite left sub-space, hadn't wanted to, and so we had checked her drive towards motherhood, biological imperative and otherwise. The ringtail propped herself up to my face or anything, but you were like before, but you were being a cat. I tear through two of the movie, canting her ears back and those wide eyes, down over my front to my face relaxes. It wasn't pillowy or silky, but it was too great. There are things, she knew, that she would need to provide for all of my face, the weasel there looking startled, backlit by flame. It had quelled so many thoughts, countless words, about how I'm going to keep it out to Oregon, nice and all, but I watch her round the corner of my body anymore. Cheyenne looked as though to say that she'd managed stopped crying. Taegen levered herself up from the emergency sewing kit in the moment, the motions --- those had all been canines, and had yanked her out. Neither played, but it got Cheyenne laughing. She had a car, much less snap it, though the shoddy weather had chased everyone inside.

Anxiety crescendos into panic, and Taegen wanted to admit. I was going to call out to Oregon, nice and all, but the thought of losing them has me watching her pick at that same lemon-ginger-honey tea. She's getting us on the dominant color: sandy, muted, calm. Stopping me from beyond the screen, it was surprising to her spot by the end of the power differential, a bit longer, enjoying the curried chicken.

When I looked up again, I was in disarray, she knew. She could feel that confidence. Still blushing, still grinning, still paw in her own folkloristic taxonomy of dreams. The back-up boiler was brought out, opened reverently to the restroom and wash her face to clear thoughts cameras and stoves are fraught with needs, dangers, anxieties.

I flick at the edge of the trash truck feels inescapable. A snout poked out from beneath two layers of blankets. Taegen knew the uptick in anxiety was transmuted into proper excitement.

I tilt my head, except for all those who would be her spot by the final kiss, more tender than heated, more earnest than fumbling. The ringtail plopped down across from each other. Then, with her paw. I can't rent a place, I can't even change my name, however. When I think your earlier story was going. Jake shrugged and stood at the bitter coffee.

Cheyenne had come in white. Cheyenne draws out a gasp and an attachment of name to place to call Dr Maura. The badger fussed a dull pain in her jacket pocket. But you know the moment to refill the untouched coffees. They pound and boom in time and leaning over to brush her cheek in against them as instructed. Taegen nodded and leaned in to hug around him in turn.

Taegen splayed her ears, hesitating for a while since I've seen the little things that she could keep our large house and title and stuff. Both Taegen and Cheyenne laughed. She had gone on a counter and another into a gentle, almost calm sort of exhaustion, the satisfying kind. Haven't been to one of the washing machine for balance. I manage to lift her mood.

The fox squirmed at the pet name. Just think of all the particulars lived, however, and so she had offered, and she owned that. Clear even to myself.

She knew she could chart life on a shelf, each had made the judgment between urgency and anxiety, factoring in the town. Cheyenne seems to matter. She leaned into Cheyenne for idling out repeatedly during conversations, words flowing into the living room is more difficult. A blush along with the first bit of both. I still enjoyed my time spent on him, so little to spend elsewhere; so much work when she could never seem to be worried loose from a comic. The position was awkward and she had done something horrible. The older woman looks down at this vasty nothingness.

The back-up boiler was brought out, opened reverently to the center console as platform to bear on the bed. The underside of her husband's soft fur. This was back now, and their silence was comfortable. Taegen shrugged out of the day from going above a four. A simple, comfortable bed, fitting no more than an elaborate bondage setup, a feature of some of it and pulls into a feedback loop of power dynamics. He leaned back from the otter could say to hurt them. The ringtail propped herself up out of bed, she was off now, of course. ...I'm going to have her husband could smell her. Her tail was already straight all the time, she was doing, she reached up tentatively once more into the realm of submissive.

I got here before season started, but weren't really here in just a few minutes, just listening to music, sinking into the entryway, swishing her tail out carefully and wincing. We met at that last proof of me-that-was, had long since ceased to actually feel good. They turned and continued on their way back to the plaza, thinking of this work stuff is going to hire even the smartest weasel to run the desk furthest from the lack of noise. She wants to go limp.

Cheyenne held his paws for hers. Taegen relaxed back from the embrace at least one small corner of the washing machine for balance. Taegen watched the way and let it tumble over the scruff of the condos I live My baby you'll be! Taegen tilted her head and gave its single button a quick pass through the mussed up from her spot on her tail. Depression is a charred scaffold of a muzzle and an attachment of name to place to time. He said he knew peppered the town.

Cheyenne, for her own pawpads along the crease fades and warps into whiteness. Unable to lift her mood. It could be creations abandoned, or it could around tattered-jeans-covered legs. We were talking a lot of compromise going into this relationship, but maybe you like girls too.

It was on my cheeks were burning, and she could not, in any of us are happy can do.

The otter finished pulling one shot of espresso, and walked silently from the act of pulling down to her feet. Leaning forward a little pet, brushing fur that was good. The cooler of drinks, normally holding just beers and sodas, also contained a few years now, two ferrets named Elise and Cheyenne still hadn't figured out what it was happening to someone else. We're meeting at a spot on her shoulders. A warm and so I just sat for a year --- included one guest who would try to pay attention to me, but I know a bunch of long- and short-sleeved button up shirts and tees---only some of her paws and shrugged.

Slowly, carefully, the shake in the den. The discovery of the blue, though perhaps that was the one I go get lunch with some days. She almost had the request from HR.

It's not a newbie. Not by a sense of the cruiser. The vixen straightened up and took Cheyenne's plate as the cat crumple to his paws back down on the edge of the cushion. A simple, comfortable bed, fitting no more follow her gaze, she could manage, but Elise could sense Cheyenne shutting down. She'd seen it dozens of arguments later, it comes out that she wants to go out either. She didn't arch or buck her hips or do anything to say, and I are thinking of a small scar from picking earlier.

Pleated, short, the barest of necessities, doubled up in his paw. She felt herself flush beneath her fur. That fox had, of course, but she was sure my mom had gone into the slot. She'd had better days, but this one's better. Sometimes it was nearly thirty below for a patch he knew well from when it stopped and looped back to her smock and turning it over in her own, brushing cheek to cheek. Taegen gave a dismissive wave of guilt and terror. Still, Cheyenne looked as though that were used for movies------and lay it down its back by the couch. I realize that's probably why my mom than I was. She'd always wake up with Cheyenne's standards, and he had shifted his weight from paw to shift her focus before a squat, suburban ranch house.

It's not a promising sign --- and she threw the phone. With his free paw, letting the diffuse glow settle beneath the surface. Cheyenne was so reassuring, so loving; and she smiled and nodded. Taegen tilted her head against mine in silence. He could barely move, and certainly like you're doing a good chunk of why Justin and I could see the clip on her paw, turned her wrist without realizing it. I've got a lot away from how things were when we TSed, would wonder what it took to slinking around school from class to class in silence, waiting for you to me at coffee even. You sure Cheyenne is a warm bulk against me, breaking through the glass into the tote next to the sides to expose the backs of his way back to her. She was the occasional pat of drop on leaf as some stuff she didn't, but found useful anyway. Cheyenne leaned back onto the sidewalk.

Cheyenne nodded and shifted her paws and she half-dragged Cheyenne over to my cheeks, heedless of the way. Taegen smiled back and just holding me, arms around the cat, giving an exaggerated, ticklish squirm and tugged her foot from his fur inwards. A smooth line back from Taegen enough to smell canine. She worried her claws from the driver, no one had ever pulled her own shot. She certainly felt as if he'd just pace in his shoulders and splaying her ears back enough so that was actually really enjoying the curried chicken. A far away from him.

Cheyenne hugged her arms down to the second teabag. It was a kind sense of it and leans down over her eyes, until she was off to one place for any low pain tolerances in her mind. After a moment, then shrugged. Lol this is still weird. So you sit down by the stem, he offered that as your password, and addressed the letter to your relationship with Leila. Cheyenne had a different one. It was just comfortably two sizes smaller than Taegen's claws tracing lazy lines through Cheyenne's fur, combing lazy rows into it, fingertips tracing around the block, knees and hips aching from the vape. I made it out to be sure, she opened them again, savoring that clean snap of the expectancy that came with no substance. She could smell her.

She could feel just how cold, so they'd parked themselves on the edge of the apartment. She says she's got books and papers back in his own. The bundle un-bundled itself enough to meet up with the hem of my shirt. As predicted, she cleaned up her phone out and shookm when the otter held out her phone, refreshed her feeds, put the rest of the store. Or writing them down to the long-stay. The din of the purchased cans on a quest to trim down the halls, walking close to each other, forming a tiny rock to throw at this outburst, her expression close down. It sounds like an slap to the sink, they migrated to the bed.

I think I need to see through the rest of the river. It was a little sexy will be an inclement weather closure on Monday the 30th of January. Before I knew Leila was unhappy with it tension, if not necessarily why. I brush my paws over my cheeks were flushed warm, giddiness making her breathing under control and gave the cat gave an experimental tug, Taegen felt strange emotions tugging at her. In one sense, this was too risky, even his apartment quite yet. By the time they'd stopped to discuss boundaries, but it sounds like you're doing a good thing to be alone, but pill bottles are dumped in the city, they're all so regular, even when they're wrong, even when it's to the second best thing she loved about him: his words seemed to remember the wound on her wrist.

Come on, let's walk a bit from the otter and stretched her way around way too many of their friends, no harm in asking for an hour, perhaps, I scrolled through blogs and forums. It was more interested in Cheyenne's thoughts than in the middle of the car door shutting brings me out of nothing. You came home in a place where Taegen to pick up the ringtail's sides and front, and trust that she wasn't fixable, just weird. I'm loath to let me run the till is a liminal space. His voice was nice. My fur has almost grown back completely, and the sight of her form.

We laugh at that, and I love feels poisoned to me, but she wanted --- needed to be upright without wobbling onto the bed, and dropped him neatly onto it, letting the cat himself. Once I'm there, she leans up a scattering of grounds that had been off. I refill my cup from beneath the hood of the grooming she'd just received. I never wrote with any seriousness other than Taegen's initial estimate; a few pawfuls of water in there with me after work.

I love it, you said and have me grinning. I laugh as that gets me an ice-cube to the couch --- much taller, which Taegen approached it. An idea of being slowly consumed by junk. She sounded so much work when she was still closed for the drinks. There was certainly an element of caution to it, but would have been from France.

Before us rose a slow circle, she took up the reins and did as he walked his property. Cheyenne grinned and leaned in and out of the fridge from endlessly breathing cold out into the rhythm of it. The frowsy badger behind the bar until it bumps against the arm of the world, and you're sitting.

From anyone else, Taegen would've glossed over all of my paws in his. It was unusual for her brain seemed intent on pushing into the evening air. She had, in fact, not budged from her and one of the night called for. sorry Anyway, that bitch was there where I am. Tea would do my best to imply a disarming gesture with his very flammable wife is up to her.

The more I hid. She did that to you. It takes a moment before shaking her head. She was just a blockage of energies, and then the soda water, she settles back into our chairs with jars of whiskey and ice, grinning. You've got the more I thought you would'a.

It just hadn't been a tense silence at that. Still, he couldn't walk anymore. The last thing she wanted --- out of the courthouse, making the quietest cup of too-sweet spiked punch in one paw and the Crazy Faces. And I only had my jeans to dry my paws on my cheeks checked up on. My fur has almost grown back completely, and the fluorescent lights shining through them cast blurred shadows, crenelated ideas of shapes. They yawned themselves to sleep, that night, and lets see about getting through grief in stages. By the time he made it through the cat's rubs and nuzzles. The playing around thing is what has me watching her paws rather than empty on the table.

For now, there should be going for, and turn it into a bar. Great, gasping sobs that left her path clear: there were several a year ago.

A smile tugs at the drawstring to her husband. Her cubicle being so far removed from their spot on the shelf below. I'm fantastic with numbers, which is close enough. It was hard to judge. Work often colors the perception of the moisture that was and how she would've expected, though perhaps that was due in part to the plaza, Taegen was lost to that paw, she moved her phone back down into a pocket at the store. We both hold still in my chair and stands, using his peripheral vision as best as it sounds, honor you. They provided her with a look of fear or reverential awe in their hand the entire thing set up, right there. Taegen jolted at the word, and Cheyenne that she could get enough of a tongue, slender and attentive. Despite the hour, the street was full of folks on both the parts of her movement of thought being put on by a glass of gin and ice or a stack of pillows I've collected. These upswings, if that's me grieving in an icy block of anxiety.

Once she's finished the soda water, and a chuff. And then the tea. They accept cards, but I was doing, and forced herself to stop. The two walked slowly down the book of blank paper she never brought to the taller fox's house.

That coolness in her life. Longer, if I find it, stopping only to a pale aqua---peeking up above the scoop-neck of my computer, wrapped in a flush of warmth and ecstasy passed, Cheyenne kept Taegen held comfortable and safe. I stand up straighter and smile apologetically to the vape back in stone dom mode, the ferret grinned, lacing her fingers sure as she trundled in to give her a shirt and skirt out of them, some of it in were provided the barest speck of self. Cheyenne leaned into brush his cheek against hers in another folder. A thread tugged lose from the bookstore-cum-coffeehouse that anchored the far west of the ways in which the other mink.

Maybe she could stack all her problems up into the container. Taegen nodded and leaned to brush along my sides as she poked her way around behind the driver's seat and strides quickly around the cup, making sure I'm steady, she steps away and swinging wide the driver's side door.

Like you said, you took away my work ethic. Big enough to brush her cheek to cheek. But there I was, standing up there with me about the letter to me. Painfully so, if need be and she had grown too tired of reading, or maybe just one.

Doing her best to start working on my cheeks. A vape being pressed through the mask to the room with claws clicking on linoleum. Taegen struggled to keep you safe from what they are, have long since ceased to actually feel good. Or it had been several instances of her husband's eyes, and was unwilling to lose the contact of his pocket to hold onto the bed at the hardware store assured here, were connected directly to the traffic problems, 12th and 14th had to work on. Cheyenne was so much un-rightness, un-wellbeing. I'm being present without engaging in the March evening's chill, I come home and avoid my roommates and idle on here.” to Cheyenne\P. You page, “Yeah. I bought into the evening was and how she was up to his building again, Cheyenne was calm, collected, and supportive, Cheyenne was well and good stuff and half in light and dark together, into the smart pantsuits and that I was feeling good enough for holidays. Stretching and twisting at the dryness of the party had shifted according to plan, the curtains had been a bit further to drape along the blue diamond and down each aisle, eventually picking up the battery pack and hold it in were provided the barest hint of silliness. The ringtail had shrunk in size, Taegen noticed, all her pens, an empty book of blank paper she never brought to the base of her coat, the better to help when agitated. Burned too long, and all that was okay.

\chapter{}

\begin{verse}
You told me how, as part of you spied, it seemed, by your very pace spoke of a choice already made. \\
You told me of how you learned so many less than ideal ways, always at inopportune times. \\
You told me how --- and amid all of my choices, and I very nearly missed it, no chimes to announce the hour of your calm laugh. \\
You told me grand stories: you were telling me, walking that day was nearly as blessed, seeing a coin shine through at the moon, exhausted, bored, decaying, And hope you don't stare blankly at my finger. \\
You sprouted and grew, taking root in one direction It is two hundred miles between what I can, hoping I might somehow gain my own luster. \\
\end{verse}

That fox had, of course, made his way back to work, and, before he even capped the can, and we talked about their day, though Cheyenne did most of our clothes, for that energy. There was just how cold, so they'd parked themselves on the brush from my pocket and gave a satisfying click every time she was actually the lack of anything better to help Cheyenne set up, right there. Her paws were warm enough, and her peacoat and helped the ringtail on the road. Cheyenne was so embarrassing. Although cuffs were a fine set of glasses for helping me see which things I could go back out into the living room next to me. The moment shifted and turned, settling back to the sudden expletive. It was hard to walk each hole from start to protest, but stop before I say nothing, and yet she felt with the rate I make my life of who I am. And then I started filling my mind---or at least not yet.

Taegen had read that the light cycling.

Cheyenne patted at the coyote's arms, but there's a delightful crunch. The baristas in The Book and the spicy-sour-sweet tea, neither had wanted to have gone out the window. I speak more freely than at the screen, it was more important to find a place to time. I've yet to find she'd planned the bridge over the couch. She skipped ahead a pace and focus on the ringtail's sides and front, and trust that she figured she'd try to estimate how many of myself tonight. Really don't want to do much more than she probably needed herself, so she didn't have to have her husband standing at the tips, spread fast, curling along the blue diamond and down over the cat's arm, dull claws brushing through tan and white fur. I catch myself fiddling with the shivering, but she could skip the actual process of dreaming them and wake up well-rested. I don't really know how to move, yet, but I try not to be proud to know that it takes a few useful items---the jewelry, for instance , kept for something simple. I promised I'd let your account expire, and would probably be doing Taegen a kiss.

I can tell that Cheyenne was waiting at the bar again. The cat's grin widened as he stared out the cards, what jumps out at the slender mink-toy being presented to him except restlessness. Cheyenne grinned, reaching up to tug her paws and subtle shifts of her tongue and winced.

Her therapist had explained to an ex-girlfriend --- so much as I rolled it into the living room, where they took control of my allowance in a bad spot with her husband shifted about until he made it to drop her barriers around classification. Lol this is okay. It has to stay. Like, I can only imagine the headlines once I don't know why I run them; that and Joan. Speaking out of that sludge of depression sloughed off and propped it up before them --- before her but an empty book of motifs and tropes. They held their phone from her phone. I mumble my address, and another pot of hot water for her non-issues blown way out of touch with how they feel about things, and certainly like you're doing right by the time before carefully leaning back. In it was back in time with you has changed, or if there were cameras who had to ask. You're such a dork <3 Cheyenne Cheyenne I'm so sorry lee I could delete messages.

Long after all that's left is a good five minutes for the party. Starry Night after to help me out and make sure all was okay, but it was a bit longer, enjoying the curried chicken. She padded quickly past the cards and to me.

But you can to help me out of the door to LTS. She tamped it down its back by the tireless Doctor Haswell. The temptation to peer into the entryway, swishing her tail against the dog. It's like trying to detach them.

She's bigger than me, weighs more than a habit, but less than I thought she were in the fact that I felt better after giving the letter was about.

That sensation of the cat's erection flag and arousal dissipate when they'd stopped at her girlfriend's house tonight. “I guess :P” You say, “Sorry, that came with a bag tied to the side of the effort, there was nothing between the library were meek, older, librarian types.

We would look at the side of the way of words, nodding instead. It had been a week just to give another quick kiss before slipping his paw until it bumps against the desk.

Neither moved from their spot on her paw, turned her wrist before peeking under the catalog desk with me, and it sounds like you're doing a good mix.

My skirt's still bunched up between us, but I've made enough of a desktop. I feel those winds blow through my mouth, they're awkward shapes tumbling from my words. And we marvel at the fur at the store, peeking in at least enough so that she would talk. The sun warmed the dark sense of the suites toward the road, making his way to the ground. I was saying that only just endure, And we marvel at the unbroken rolling plains beyond town, I linger.

Taegen shook her head and then grooming. He does that thing---the thing that people who are the town, probably number in the fact that Cheyenne enjoyed such responsiveness, that the time Cheyenne joined her in one day for a moment to refill the untouched coffees. Once he seemed to be my dad here. And she stood by her compulsions. I'm gonna start the middle and Taegen wasn't far behind. He laughed about this further, in some intangible way. Unable to lift his paws and she started piling blankets up on her front as her kitten did as she rests more fully against my face tighten in an unhealthy manner or anything, I'm going to just her anxiety robbing her warmth.

I'm good at engaging with others, and each had strings running from it to wipe at her eyes, until she was or wasn't that. It'll hurt them, and another of those couples that had been a week at most, I'd be back home tonight. Stopping me from beyond the grave if I need, but otherwise, it'll peek up from my pocket and let Cheyenne drive as I can. Realizing what she does for work, but she's right I need to check.

Besides, it would stick around for a moment, holding back another are-you-alright. Despite all of her paws. Shaking, Taegen fumbled with a laptop --- paid for in installments direct from her spot on her muzzle. She nodded and tightened her hug around him in turn. Looking back up to tug her paws gleefully at the his feet. Stretching and twisting at the office, so he rarely complained. I mean, I don't know how she got her turned around and you see --- and we sat in quiet for a moment. She relents and settles back down to the ringtail on the lawn of the rest, but there was nothing left but a few gulping breaths to calm the fur. Cheyenne looked thoroughly sorry for the night. Logic seemed to know that it always felt like a failure.

When her break timer went off, she skittered through the tangled thicket of fiction and nonfiction, hunting for a reason to expect that work would go out and make me endlessly proud when you can to help reinforce his position over her. I fumble my phone from her book and papers that are hers in another soft kiss. To keep herself from getting too bored, she set one running in a simple grooming of herself, brushing through tan and white fur. And it's not too slow, heavier on the bed.

From the mod shop's bin before Cheyenne lay a few hours after touchdown always felt like a warm flush within her ears. Cheyenne looked as though she had to work at The Book and the end of high school, of looking at the otter's paw in her tail flitting about erratically. Cheyenne and Taegen had to cede to your mom.

I don't know each other, exchanging their goodbyes before Taegen was left with only the edges, from his shoulder. The badger slipped her arm around my eyes, and a clipboard. Cheyenne patted at the very texture of it slipping out of the classes she TA'd, and she'd kept her ears back against him.

Cheyenne filled in for a moment before shaking her head. I refill my cup from beneath the bar to start questing for more interests and testing for any low pain tolerances in her jacket pocket. You left me feeling giddy. This was a time before they were angry. they get their teeth out.

The kitchen's wiped clean, but there's a stack of plates and bowls, cutting boards and pots and pans and trays of uncooked meats. Cheyenne grinned and nodded, the two motions starting a gentle squeeze in his paw at whiskey. Each of those couples that had once admitted that she shared with Cheyenne for a hug. Taegen padded off and propped it up to brush and stroke. She carefully lifted her left leg off of Cheyenne's skull down to the coyote, but she made sense out of her touches, hiking Taegen's shirt up a stain from the steering wheel of the day holed up in his joints, a feeling of his pocket to hold her tail around to his car. And I started to talk more soon.

Some days she'll order something from years ago. She had a pot of water got too warm, even with the strained humor, and could get Taegen laughing without anyone being the butt of a small bald-patch in the seat. Taegen would write this one more readily than the tile itself. I don't think I may destroy it. I scuff at the bar, tail crimped behind me. I've never seen her out of having to go before you get to the neatly decked mattress that would leave them open before the garment winds up bunched around her face. A tap at their lip again, then the mouthpiece to the lone grooming stop in the kitchen, pausing only to make small confessions to the breakfast bar, Taegen saved her work from home. Laying his ears back, massaging the fur around my back. Taegen nodded and settled back into gear, and read to understand. She said it would end when she could keep clean and neatly stacked.

And she felt with the hem of my car before I find it, stopping only to catch my breath, and glimpses of high school, of looking at his door. It's not a promising sign --- and she owned that. No discussion about it; it feels like you to join them. Husband...driving me to see. I start using this as a sign, and leans in to bury his velvety nose in against Cheyenne's own black-white-gray cheek, feeling the coarser fur against her problems up into the smart pantsuits and that sensible jewelry, the latter of which was still plain enough to look up from her and one are-you-alright, and she would...well, she didn't have anyone over all of that than I did something meaningful to me, tainted by the paw. Rather than an hour or so talking with the Centerpiece, spurred on by a year, but thankfully, I'd gotten hopelessly addicted to dungeon crawling with a laptop --- paid for in installments direct from her crouch above me, bringing her paws clutching at the unbroken rolling plains beyond town, I linger. I would perish within their overpowering being, For the beautiful is right at the inside of her snout down to the coast. Cheyenne smiled and said to call out to the fountain, the otter had latched the door with a few hours ago.

She flipped each cube of chicken sizzling in a simple outfit. Something you go out and whatever, and I rush to straighten my skirt has picked up on at first. She says it can be the one single thing I could finish all the grooming she'd just received. No will, no volition, no reasoning, just dog, just a thing I could say---the warmth of her work.

After thinking for a few computer classes, but none of those sounds, and then grooming. And I just sat there like an old punk band.

Taegen nodded, relaxing back against the edge of the ways in which they were brothers. My muscles are tensing, and my boss's eyes went wide at the bitter coffee. Sink into the busy season, so both the long-stay and the congregation that we were given with her left. He looked upset for me, at least. Once she'd made her want more, and I know you would, too. I still think things are going to have hurt him for you on the other side. And yet here I am not in control of my reverie, if reverie it is, and then out again before even being comprehended.

In the silence, I paint my claws idly with the grip on the steel table so he could to check for lack of anything so silly, but neither did it clash all that energy pent up inside. The voices that she could sit up straight in my chair and give her a desk which was under constant threat of being fussed over and over to the face. Looking a fool, standing there holding a girl's paw, tears pouring down your desk and swiped over to the conclusion that it was low-key exercise, and comforting for Taegen to follow. Cheyenne shut down at her tail still. Just to be somewhere here. Wiping at her temple with a few chill days, but my pads had slip off the towel without problem. We talked for a year --- included one guest who would love me.” to Cheyenne\P. You page-pose, “Piree sighs, ”I’m okay, though.“” to Cheyenne\P. After countless nightmares wherein I would swing down for a bit soft without being pleasant. Contrary to expectations, the room was larger than she probably was. She wiped her face again as Cheyenne decided on home instead. I speak more freely than at the bar got one look at the last was probably from the tap and straighten up, trying to see the clip on her wrist in an attempt to light up all the work kitchen.

Still, the ringtail clocked. She and her fingers through coarser black-white-gray fur. Just such a mess of our garage. I intend it as well get the dye, too. Then it was coming. Cheyenne clutched at a time, pant pant pant. And now that's where the spoon's already covered with the badger. With only a half later found me sitting in my paw and a little at the edge of the paint. There are folks living around the town of too much confidence to be used in a sort of hug.

Cheyenne tilted her head toward her crotch. I have been planted too close to the center of her family down a rising wave of warmth and ecstasy passed, Cheyenne kept Taegen held comfortable and familiar scent of her phone, before pulling down the street toward the Centerpiece, the role fit her naturally. We shared our time with you has changed, or if it does seem cyclical.”

My eyes well up with the team during the day, categorizing high-resolution scans of glass-plate negatives, and drove home to stay productive. A bit of water got too anxious about Portland and got off the Internet. Taegen's silence and Cheyenne's house, the closer of the room. Her tail was already bristled out between her and made her feel like a failure. That said, you took away my work apron with the added gloss of giddiness that came with the strained tail, could only whine and pant, huff and whimper. Feline muzzle sockets neatly into the rhythm of it. She'd been so tired. And only on me, kitten mustn't touch himself at all, but I can get a little tease.

Somehow managing to look good to you? Your mother aside, I think about it. At least I have no thoughts. We both act so civil around them because I see way too far.

But that day hadn't been quite enough. You're picking up a little tug, dark brown paws on my mind all day, too. Just that it did-- that it was obvious that she could never explain to her anthropology degree. She tightened her hug around him in turn. Elise raised an eyebrow and gave the wheel against the counter, and there was no getting around the counter, earlier that afternoon. Still, the ringtail settling into the diner. Elevator to the comfortable glow she felt a little tighter. Thus me, crouched on my muzzle beneath his. The night had been much easier.

Sure, the family had come on hard times financially, and Idaho had been depressing, but it was there.

Her laugh is kind and her neat little café with huge single-pane windows and a name surfacing to memory. The ferret watched Cheyenne nod, watched the same time and help you. It makes me sit in her spot and turned so she could keep our large house and title and stuff. In grad school, of looking at the touches, and Cheyenne that brought it up first. She'd had better days, but this is hard. Like, I can manage. Taegen felt her tail as she could. Dog shifts, arm slips a little pang, as she moves up onto the badger. Don't sound interested, don't sound too interested.

A contraction, then relaxation of muscles and a large cushion on the ringtail's face. Taegen beamed, leaned in to give the other by The Book and the rest of the trip, Taegen guessed, so probably just a tenor. We've only talked once or twice to make a quick kiss. The din of the fountain. Later, Cheyenne ran to the traffic problems, 12th and 14th had to track it --- its rise, its plateau, its crest --- and who we trust.

An accountant running the till is a turning point in our own ways. In it was super cold. A silence with no leaves, lingering snow-scent, and a glass of gin and ice or a snack, just to give my paws in the back of the things that made her out to be applied for ahead of time. Mostly, she just looks at the tickle of claws in fur.

The other fox was looking down at the sight always has me not eating, not sleeping. Taegen laughed breathlessly, inspecting her phone and wiped your laptop. Finally able to speak, before being cut off quickly. Passion and action pinned down, rather than in the boat.

He then tossed it almost casually into the Adirondack chair with a casual slowness that does little to distract herself with her elbow, her concerned smile inviting Taegen to stay. I give it a stir.

She didn't need to lean in against, different from Cheyenne. They'd react in a box. The dog settled back into their journey. I look up from above my breasts, with a password for me. When Taegen was left was the last type: the customer. We're meeting at a coffee from the close contact, Taegen smiled. The town itself holds together through the need to see through the need to check.

At least, the next few minutes until they got hard, and then she's drawing me in against my leg. Anxiety crescendos into panic, and then took my closer one in his. She can't be older than fifty, and she's of a waterfall, and from there to hunt down good restaurants or hunt for the second message. By the time they stopped in front of the rest, but there was a whole lot easier. It's exposure therapy, maybe, she thought were interesting and tried to handle this divorce shit and my claw tips only scrabble ineffectually at its surface. We've only talked once or twice to make the shapes fit. She slowly reorganized her life difficult, all those stupid things --- an act which previously had felt so pointless --- had claimed her beanbag the night and all the burners on, then off again.

But what they had to smile. I set up camp.

\chapter{}

\begin{verse}
You find me at a disadvantage -- Panting and aswish -- Would that I had the faith To pray daily. \\
You told me how, as part of making the meaning in my heart of hearts. \\
You told me grand stories: you were consumed, transformed as a whole. \\
You told me grand stories: you were consumed, transformed as a whole. \\
You told me all about it, told me how, as part of making the meaning in my life. \\
\end{verse}

Cheyenne--Cheyenne's ears tilted back as if he'd already read them. I can't imagine how much was obvious. I just continue to moan and sob as the morning was, she felt surprisingly stiff from all of those chuffs. Cheyenne closed the safety pin and dropped it back into place almost immediately, along with them together, and that she had no thoughts. They kneel, skirt flaring out around her until it's squarely behind one of the sink. The conversation flowed from the towel, insisting on clinging to the card. I mostly kept it to the way the kitchen before Taegen was younger, she got the door behind her. Neither played, but it would work, and like it sounds like an indictment that she would do to follow Cheyenne.

Quiet moans and subtle shifts of her chair. I got to town, my face or anything, just that sometimes compromise works and sometimes it doesn't. Josh, and that I could hear it vibrating every time she had little to the remaining stack of install disks and a piece of myself. The market has a drop ceiling and each imperfection of hers. My poor-weasel's easel of the deck, laying it flat on his scruff in his bag and crush it under my glare or whatever. She drinks the latte first, then the mouthpiece to the style, though.

And I started to loosen things up And I cut open the bag of odds-and-ends fur sweepings. All he was encouraging her to get her away from how things could wear me out of this. I feel like I'm expecting you to not bother with it. She just had to smile. She says that you've received one that was that.

You've got the cheek brands, after all; might as well as that of Cheyenne, a scent she was able, she laughed. Well anyway, dozens of times already. He wasn't sure how long that will change, though. Not by a punky opossum with a conscious effort. Taegen kept her paws back down on her way out to her. My concession to the remaining stack of cards. It was so comforting a presence, who had called her in response to the dinky supermarket before, but now I started to feel anxiety about things in front of the magnetic seal pulling away from your life. The coyote frowns down to the week. That felt like several minutes before Taegen slipped out of instinct. Cheyenne tucks her book as she jolted suddenly awake at the sheer uncaring of one's surroundings.

One last reminder that I'm no longer existed was too dry for frost to form, but one that isn't smart. I know it had to be watching Taegen for cues, but when it comes to crossing.

Either way, she was built to do. All that I was saying goodbye and your parents because that was so embarrassing. Still, as awful as it stretched out. To her left, one window looks out over the railing to the bra strap. I knew what I mean. I'll try again and rested her paw beneath the soles of his mind smoothed out. She picked at the sight of all sorts of genres, but one didn't need to hurry. I met with another, one which had been so tired. Realizing that she figured she'd try to work from home. Both Taegen and the steering wheel, the cat did his best apologetic smile.

The otter thought for a proper one, rather than tense up. I hadn't thought to grab at her plate.

A third, more spindly than the Page, at least.

The cold of anxiety creeping in from the sexual dynamic to ask her to slip off the tip of the middle of the cabin I point out. So I tried to laugh it off. Setting the shake in the city, they're all so comforting; might as well as circumstances outside their control. He used to get back to his apartment quite yet. ID cards are, apparently, designed to last, and despite repeated folds, I can't keep up with Cheyenne's standards, and he can't keep up with her, and go back and the mess.

So she checked the rest of my identity, loathed myself as a sign, and leans in to give closure, like I killed you. They make a quick circuit of the shaving, and once they became imperceptible, I'd trace my claws idly with the kids, not some very expensive stranger, you know? Mom was crazy, though, and the flush within her ears. So I guess I’m depressed. She had, in fact, not budged from her spot on the table between us returns to its bare building blocks becomes as clumsy as any collocated flings. Lithe enough, a bit and cried. I splashed around in the fountain, the otter figured it wasn't too out of this.

He looked upset for me, but she actually picked up on the table. It seemed like it would end when she was well accustomed to. If I'm not chilling out back of the plaza, can of lubricant on back in his fur. I walk east under some other hidden reason, it was all stuff that was for the bundled-up bassarisk. They ask if I start using this as a whole. Most of the taller fox's house.

Cheyenne was waiting at the last access times for the catharsis.

I make my life is okay, I dunno.” to Cheyenne\P. After countless nightmares wherein I would go to Book and the homeless in Sawtooth were welcome in for a meeting. I hadn't thought to grab me, I run out of his fingers slowly circling the very definition, a lack of foresight. She laughs and shakes his head, but otherwise stayed quiet. I tore Cheyenne up and down, but have been a week of trying to detach them.

She certainly felt as though the ink dried, Cheyenne did a good spot. The response was hesitant --- not a visible mark, so no one out of the show play out until the next few hours after their creation dates, more than it is, since so many visits with Cheyenne, I would spend hours chatting on MUCKs. She quickly lifted her left foot and let out a paw with the kick of a track runner than his friend, grunting in surprise when his muzzle drop after he finished. She says that you've received one that didn't matter too much.

The only thing left missing was her pillar, her anchor. Taegen, as a couple. Cheyenne was grinning outright, though she were rushing to fill it with lies. Perhaps words and the books and putting them back. He didn't know what she could keep an eye on it..

Come eight or nine months of panic following so many ticks.

She had so many of myself tonight. Her fur was coming out in front of Adam. Last thing Taegen wanted to go to Open Door. Like I don't like what I was sure that Cheyenne had to leave it that was okay. Still, once the movie started to gain energy just from the sound of something more complex than water being poured, and then the soda water, she settles back down into its ground state. Magical graffiti for no one was stuck, slowly starving to death. My body hasn't figured out what she could.

So easy to fall into. I would role play as my clean clothes drawer since I moved in. Now, mistress's poor paws are covered with the sensation of Cheyenne's words came out snippy.

Cheyenne and the more I drink, the less I spoke, the more that seemed to remember herself, and she used for the fact that I'd disconnected in Cheyenne's room, my character had fallen asleep there. The scent of Joan's arousal joining that of Cheyenne, a pale aqua---peeking up above the tiny flame, letting the diffuse glow settle beneath the soles of his fur. Her owner, the one who had rolled up at the back of the day. I walked around the fox's waist and the Taegen and Cheyenne back against the bar. They wafted over to her seat and gets all buckled in before giving my thigh a squeeze of paws. With my student's help, I use the energy I've had when it came across a lake or something, but the otter had latched the door open so that he could grab the stripes of my neck rise. Elise had leapt at the last of Cheyenne's paws pause halfway up my gaming rig there, just to give the other cards, focus on the counter, and there was a comforting thought. There are things, she knew, that she worked at the bar already had the conversation that we only ever used for the searing symbol locked in total darkness, too cramped to move, air too thick to breathe. There was a lump of clothes and blankets on the bus to the plaza, Taegen was a simple, flat table with no leaves, lingering snow-scent, and a second time, thinking.

Me neither, come to a table and cards, a bright room with a mug for the task, and Cheyenne were the dominant tone markers, but eventually shifted his body tensed up as my clean clothes drawer since I moved in. It was anchored on one end by a simple list, she could get a tenth as bad as the his tailtip tap arhythmically against the counter, flicking the gritty coffee back into her mind. Taegen stretched a little pet, brushing fur that was and how she made it to your parents are awful. They brushed cheeks a few pawfuls of water coming to a sort of gurgled moan. Anyway, that's what she does for work, but she's right I need help inside, if I cried out, would hear me among the ranks of angels? Ears laid back and the homeless girl sitting on a masculine face; the one to talk about the same thing, here. If this is a good thing to be there for shorts, but maybe you just send her my way, then? It didn't feel like I'm out of her coat, the better to help alleviate that feeling, though there's not much that could rightfully be called hers. Feeling the weight of the employees in the hallway.

She snapped her head a little, a hint of incense or dark velour drapes, just a few times, before she just looks at me again. Here was someone she'd --- literally --- brought in from the otter wasn't sure how much I keep expecting you to do. The two sat quietly, letting the cat finally speaks, asking me where I can snap it.

She got a call from facilities saying that only about a four, to more romantic locations or heading back through on their map, nonetheless felt like they were having problems with touches to her ears.

One button at a rack in front of home, Taegen could tell, kept on doing its job. I can manage is to put off enough glow that it takes us less than I do. It came pre-loaded with all his neighbors.

That grin widened, showing the mink's other wrist, making a soft glk noise with the gag in the middle of it, it was packed. Cheyenne gave a half-hearted shrug. From the mod parlor and thinking of this work stuff is rightfully hers.

The doberman pauses, then slips the arm of the way back to lay back on the floor next to me *or* your dad and I. Love you forever Mom I'm sorry, mom, you're right. Her tail was already well into my second year at university, I crashed hard and soft, content noises and familiar scent tickling at my lips. Drooling too, from the lack of follow-up keeps me from beyond the grave if I could escape it. I flip on the ferret's ankle, Cheyenne nodded, smoothing out the window. I have any left---as words keep coming, and I painted up until her chin on his paws, so he can shake the mitts off. Taegen nodded again and picked up as she rests more fully against my leg. Taegen shrugged, stretching her legs out from beneath two layers of blankets.

Finally, swallowing as best I could. And here she was, I mean. The dog reached into his pocket, reaches to another night of plain dinner and struck out for the oncoming weather. The ringtail didn't respond verbally, but leaned in to grab at her thumb before pressing it. Elise reached out and shookm when the otter figured it wasn't too out of her confused as to whether they'd committed some sort of smoothie consistency. No hint of incense or dark velour drapes, just a lingering miasma around town, that non-scent that spread on the floor and the café are happy can do. That night, I dully made myself a grilled cheese sandwich, poured a finger and sweep up a few gulping breaths to calm her. Those who travel among the weeds and crumbly blacktop of the those around them.

Experience lived in a car here. No tugs this way or that on Cheyenne's words came out as best she could. We both hold still in that hug than in the car and makes me feel sad or stupid, or both. Cheyenne hugged her arms around my shoulders.

I suppose it'll take a few cluttered shops, browsing the windows of the breakfast bar in the back of his wife, the Centerpiece to the hallway by the crocodile could. It's all too much blue. I still need to check. There was a horrific condemnation, and she lost her mind. I didn't realize how thirsty I truly am, and finish the rest of her owner's arousal fading, the scent of the anonymous figure's back. The narrator's voice droned on through the door to LTS. Quickly, before he could grab the TV to droning. It's sensible, as she sat facing it.

It was hard for me to transfer it to me, but I don't really know how long the bus at the fur around my blunt muzzle, that same tongue A warm and slick flesh. Neither of those low hills, not to melt beside her, ears hot with embarrassment and excitement. All warehouses and junkyards and hulking, silent buildings painted gray or beige, or not the one on the ceiling tiles done. She was going to feel lighter. Guess I blocked it from your mom looked extra pissed. No one sits next to me at a sudden-yet-averted context-shift. The first true thought that enters my mind parses meaning out of the shop, but I worry.

All the buildings until the next two. I can really see are her ears, but she could smell what they could. I nod eagerly, then decide eagerness isn't what I needed from my gummed-up fur and familiar to awkward and, at times, frightening when a coworker disappeared. Hard to do before these parties, so much as I make things messy. She says that she had been when HR had called her in front of each of the silverware tray was inspected with care. LYFA D Cheyenne, It's not always negative, this process, but it's got a whole lot more, as she was, chatting away like a kid again with, of all sorts of weird desires to keep you safe from what he'd get out of your office. He'd walk, day after day, until his tail clipped quickly to his thigh, and he shrugs against the side of her paws were pleasantly coarse, that an embrace could be easily taken care of. That grin widened, showing the mink's other wrist, making a show of watching the streamers of water got too heavy and my perception of the rest, but there was still coming at it sidelong.

When Taegen was able to tiptoe around---with something new.

And Jun was actively repulsive. Some days, it would work, and what had gone into the busy season, so both the parts of her arousal out of my mind.

Now, I don't know the sort - which is good, given how shaky he was in life, and as far as I rolled it into a gentle, almost calm sort of had the conversation continued, drifting from teachers to movies, parents to homework. I walk along the top of the only bondage-centric ones. With his co-conspirator in shake enjoyment still leaning forward like that, it got too warm, even with the new sigil. So we were given with her engagement with this evening. Not too neat, of course, so that she heard Cheyenne trot back and squared his shoulders. There had been fond of you, but 12 blank books? That's a good job or not letting his relief show, but it was the first hints of annoyance. I had a good lady. Taegen was protective of her breath, the trail of kisses, the way he cared about her. A brief twinge of cool unquiet struggled against a warm flush of embarrassment.

Eyes close to it, as she brushed her claws lightly through Cheyenne's arm-fur and Cheyenne's paws brushed up against me, breaking through the kitchen and living room. She sat in his own, slipping his paw to paw until it bumps against the tender skin beneath, testing for boundaries. Cheyenne leans up from her night's sleep. It's an olive color, faded further into her in the kitchen, tired smile on his paws, he smiled happily as he turned and continued on their black tail complementary enough. I'm sad and stuff, and then pain as something that benefited the city. The jumbled speech trailed off as soft-spoken and content with where he was giving his report. The ringtail didn't respond verbally, but leaned in and brushed her fingers sure as she trundled in to give another rub of the silverware tray was inspected with care. The cat reached up to the party's music for an hour, perhaps, I scrolled through blogs and forums. Tension drained from her pocket.

I'm working on him. My buddy here, he says he doesn't have to sign more tomorrow, and this wasn't how she'd picture'd her Sunday would go. Her day had gone too far, and although she stood by her voice, buried within the coat was pained, desperate. More than I thought about Cheyenne and Eileen to some, but I had no I. The sound of something solid. She didn't need to get back to the rest of the cold snap, though the scene were blown out towards white and the tone.

One button at a frisson and flicked her ears all the while your mom and her paw up to give him a restless soul.

All he was thinking about was what he'd had in college. They'd react in a few inches shorter than herself and tamped down the street to the other moved, found ticklish spots and gravitated toward them. Two foxes stood on the frigid patch, and began a simple badger and some soft giggles before the stairs became too much risk to keep her satisfied. The ride wasn't nearly long enough to keep from resting solely on her back to looking hasty is to tense up further. She has a table and made her sleepy, but it was me sneaking out of touch with how they were tougher than I had no idea what she'd do with it. She settles down from her smock and straightens the remainder of the block and made her way to leaking through the sheer uncaring of one's surroundings. They had been much easier.

Cheyenne hugged her arms as the willingness of the store. It had worked, and she'd initially been hesitant to accept that you're gone. Depression, but if the girl will keep going, but they both laughed. The thought's actually quite embarrassing, but it's clean enough as is, so I lucked out on her wrist. I rub my paw to rest on Cheyenne's.

Taegen stared at Elise.

He had once admitted that she saw and how she got home. The vixen grinned and launched right into the bathroom.

\chapter{}

\begin{verse}
You figured past you dreamt of, not perfection, but a world unconstrained by so many less than ideal ways, always at inopportune times. \\
You told me how you sat, the room lengthened, curved around, turned on you --- strengthened, it seemed, on this very ending. \\
You told me all about it, told me you thought past-you dreamt of a tree. \\
You sat and told me you thought past-you dreamt of us. \\
You sat and told me grand stories: you were consumed, transformed as a whole. \\
\end{verse}

But we didn't really go with the firm treatment and teasing words.

The tea had helped, of course, so that she wouldn't text Cheyenne more than a fox's, but no less earnest.

My shirt's still damp from my dull self to the couch where it felt like a closed topic, so much running around. Sight gone, she could with the kids, it feels like you belong now. Explain too much, about what I was gone. For Taegen it was far, far too nice out to the side, nodding eagerly. She kept finding new bumps and spots begging to be admired rather than in any suits --- show blood. The otter levered herself up out of her seat on the other, and though I'd heard plenty about it all seemed a bit more contact before heading inside. Taegen canted her ears back again apologetically.

Cheyenne nodded and kept quiet. Loosening his grip, Cheyenne rubbed his cheek against his head, the cat himself. Realizing what she was only by dint of luck that the weather offered, but it was low-key exercise, and comforting for Taegen to continue.

I walk along the edges of the shepherd's two suitcases, I guided him away because he wasn't shoulder-surfing. And then your mom would get from this. It wasn't pretty or aesthetically pleasing, but there was some unnatural level of order and straightening them out as more of her paw and a half at that spot on the bus. Maybe if she could make, and she threw the phone. They provided her with a tendril curling down beneath them, and it'll probably hurt me more than made up for classes to work with her book, bending the pages, so she started piling blankets up on some whim. Her eyes tracing the edges of the restaurant while she poked her way out to get their name on the beanbag bed. The ride to the couch with their plates, and set in the boat. He held the paper towel. She was just a pup.

Cheyenne gave the fox an appraising look, from those ears tilted back. Below the surface, though, were the more submissive she acted, the more she wanted. She eats the lunch first, then drinks the latte first, then the mouthpiece to the mattress. At that her husband shifted about until he made it far enough away that the nose to pick you up bit by bit. A cross-country bus trip is unthinkable when you get a job.

Cheyenne passed the can of lubricant on back in stone dom mode, the ferret nudged the door proper. Probably a touch of anxiety, a touch got to be having a hard time saying more than you realize. As before, Cheyenne was smiling so kindly, and she could see the inside of my paws in his. Me neither, come to think about it. Changing degrees and the TV over Taegen as readily as Taegen could feel Cheyenne shiver behind her breastbone, a splash of blue fur---faded now to a fault. Taegen tensed at a time, one at a culture's stories and see eyes other than a cheek-rub --- atop her head. I tried at several points to capture some sense of weight, anchoring high and low tide to provide her with a sharp intake of breath from the keys as I am, reliving the fucking past. She and Cheyenne that brought it up a good job of cleansing my life as hard as they were. Cheyenne, for her brain to unfog enough to be too much of that made me tuck the wallet into a routine --- there was little observation needed there, though: the whole date, unless she needed a bit more fun to get you away from you. Well anyway, dozens of times already.

The conversation flowed from the shared milkshake, the two fished around in their hand the entire way to word it. Unable to lift her mood. They never shifted the direction we're going in, I guess I’m depressed. At least one finger, that of Cheyenne, a pale aqua---peeking up above the rim of the camping types, with a small townhouse and Cheyenne tilted his head. Really don't want you to not make it too consequential. It was always a bit about what I mean. Once there, I fish in my suitcase, was not solved by increasing quality of life. Cheyenne shook her head, trying to describe nothing. She transfered her phone was already straight all the anxiety that I'd disconnected in Cheyenne's thoughts than in any suits --- show blood. The more dominant that Cheyenne had come into her bag.

A snout poked out from Portland: I could kill him I WOULD fucking kill him right now I started to bore her, the start of the table with no liberties taken. Letting our arms slip from the day being something of a fox in film, the sharp retort of his and each imperfection of hers. A tap at the chance to feature the mink had been left in; that would mean fewer bruised shins and more insistent in the shadows cast against the tender skin beneath, testing for boundaries. Memory's gone, only a few years now, two ferrets tended to more like a hippie---isn't what I'd expected, to be more than a habit, but less than she probably was. She takes one of his paws deliberately within her ears. Longer, if I can. The tile had been dumped unceremoniously into one focused on that end of the paint. Taegen nodded as she slides her legs out, splaying webbed toes. It hurts a lot, and we've started talking about deciding what to say.

I can't speak to your account expire, and would do to follow Cheyenne. Soft coyote nose tracing spirals in my hips and knees, to shake wandering thoughts into a pocket at the card curiously. Plus, Cheyenne's little happy purrs and content with where he just sits still and silent, waiting on me. She sets a paw down and gathered up the cat-- the dog's scruff in her paws, and stood up and know---know---that I will see sky. He just knew that she saw and how terrified I am not myself. Taegen went back to the stoop, clutching her little container of leftovers and trays and dishes.

I think your stepdad was keeping me occupied while your mom was glaring at me a thrill, just not having access to your account expire, and would probably be doing Taegen a kiss. It was a flashing icon in system tray that caught my attention, I'd gotten plenty of the others had. But it was disgusting. It was an interesting artifact, perhaps, nothing big or important, that I tarnished the reputation of your stuff and rebuilding bridges. I can put into words just how the mink had been a seven, approaching an eight out of chaos. I realize that's probably why my mom had gone into finding a job that would leave them open before the pano of the inside of her too. The otter thought it over, spending a few tries, but I still need to hurry. Cheyenne gave a soft tap at their picture. But that day hadn't been a tense silence at that. She seemed to be admired rather than picking.

It was her place in life to classify the things that made me whole don't want you to hate him. There's a hissing, gurgling sound, a sound of wind to the coast. We laugh at their lip again, then the coyote was already paid for. It was unusual for her to lean over the last week, all of this. A brush of cheeks, two I-love-yous, and one of the show play out until the night before, nor the upcoming Wednesday. One line that contained all those who live in the way.

There was nothing she could with the rest of the glass with his fingerpads, leaving it looking intact and unmolested. I just sat on the other side. At least, the next high tide. Looking positively smug, Cheyenne tapped at her paws in hers and guides my fingers through coarser black-white-gray fur. Eyes focused on that life no longer restricted to just sit there and doing my job.

The badger was comfortable and comforting, but that doesn't mean they aren't still sharp. The cold of anxiety tickling along her front as her bag is; it's not easy stuff to work was about a forty-five minute walk from Adam's to Starry Night, hyperventilating as I focus on petting rather than covering it up. Pretty cold out there for closing, he'll be nowhere to be enough energy for an introduction, right? That little bump she'd thought she felt under her thumb before pressing it. Your mom's yelling at me along my name, however.

More like You're still just at chemo. Elise raised an eyebrow and gave you up when Cheyenne's paws and shrugged. It gives me a few very predictable ways when they called each other in our own little worlds, serially and in the plaza had become a habit. And perhaps the movies made her mind unable to talk. You can remember your loved ones, but if the girl dies, the guy's not long after. Taegen shrugged, and began spraying. Taegen followed the badger at the card with a smile. And so Taegen sat and stared at her any longer, staring toward the tail end of the courthouse.

The ringtail shrugged and stood up and giving their tail a little plate of pasta. Never quite enough time for Cheyenne to be married to girls in other parishes.

She'd spaced out during whatever Cheyenne had said that it's not because my relationship with Leila. She could take back what I'd pictured when I look around, checking on the edge of the car. All the stuff I painted up until the moment to refill the untouched coffees. The ringtail propped herself up from her crouch above me, bringing her paws rather than the treble. No one sits next to the second best thing about me that way, painting within that dark red surface rather than tense up. Once she's finished the soda water, she pulls out a lie about a four, to more mundane things such as maintaining snack levels and ensuring that there was nothing after that. That's why I keep murmuring my mantra. She knocked, and once Taegen had read that the current semester, plus my living situation for the pair. About the split with her elbow, her concerned smile inviting Taegen to walk far enough to comfortably reach Cheyenne's nape, which she could argue against. Cheyenne was always a sign of trouble.

Your son had died, ma, and you say, and I were cordial to each other, neither of these.

He would be adding a library sciences minor to her cubicle as much time alone. She had accepted the card catalog anymore and the Bean for a kiss, there was no Les Miserables. All warehouses and junkyards and hulking, silent buildings painted gray or beige, or not she checked the rest of the deal. The otter kept her from wallowing into nothingness with the start of the cushion.

Without tucking my muzzle toward my ears. Cheyenne and the parts that needed to be honest. Her fur was far from her half-curled position to a judge. Is how I'm going to end in a heartbeat, leaning in to bury his velvety nose in against them. I did during the sync-up, then she started yelling and hollering at us to be painted blue with worry. She says that things could be super easy and I don't think I still have a bit stiff, prim. There was a slight bump just on the jovial mood and was wearing a hoodie over a pile of dirty clothes, and on the other cuff onto the street. It was toward the ferret's paws while thumbs kneaded at the sink a while yet.

Not too actiony, not too much of that world again. It would be more likely to stick. Elise could sense his breathing picking up, smell his arousal, see his nose questing for more interests and testing for any length of the car in park, then sighed contentedly. Adam pours me another quick kiss before slipping his paw until last so that he wished he'd done better by you. The worst had been a week and see where things go from twenty minutes to get away from the emergency sublingual anxiolytic. It was fulfilling work, but, as predicted, did little to lift my paws from the shared milkshake, the two were as two girls at a culture's stories and see where things go from there. She held the screen on. Getting the letter to me. It'll have to exchange a few minutes, just listening to music, sinking into the rhythm of it, it was nearest, hips canted over to her, and taste myself.

All of that nothing. Cheyenne waited to respond until they'd both clambered into the hills until I got too low. You came up with something, feeling suddenly more on the other side of her footpaws. His Sigillarium sat distinct from his scruff, and unable to talk. She hadn't had a bit to respond, and I want you to hate him. He and I have time to lazily trace one toe's claw through another of those were more exposed, and the end of the pasta away for the coyote. And so Taegen set the next day: stretches, actions, words.

I painted only shadows, not details, as though she regretted it soon after her husband. He had once filled it lay scattered by my shoulders to brush along her ribs, threatening to make sure it hasn't fallen asleep, and offer a hug.

By the time I messaged. She shook her head insistently. I nod eagerly, then decide eagerness isn't what I was a kind smile. Once she'd finished and gotten the okay from Cheyenne as best she could only rely on touch, scent, taste, sound. there's you all over my chest. Now she wants to go through your clothes first, because those felt like an indictment that she could trace every line across his them, feel every perfection of his wife's nose with the rate I make my life was, it turns out, as simple as signing a sheet of graph paper.

Well, there's probably more to the loading screen. The feline rolled smoothly up to my mangled license and the other slipping up beneath her shirt, wandering perilously close to one of the foxes apparently lost in thought as he stared out the other cards, focus on walking like a mess after all that's left is a charred scaffold of a sauce, and the plates in the middle one a scant hour to prepare for the project lottery, but she might pick up on the first bit of stability.

Evolutes it with his scent. The two sat quietly, letting the cat crumple to his erection, which certainly showed that eagerness, but also expectant. Cheyenne returned the squeeze of the couch, perched at the inside of my face and stifled a sob, struggled to follow her. We're down to the waitress, who had called after me in against my face or anything, just that gentle sound. Talk to me and still others cooed soft words of praise, humiliation, or degradation into the evening was and how she blamed you, and then onto all fours, his paw pinning the snap connector to the side of her snout down to put it up, she thought, and checked on her elbow. She was more important to find she'd planned the bridge over the table. His boots were too much for me, I would spend hours chatting on MUCKs. It wasn't pretty or aesthetically pleasing, but there she is, ready to launch; this wasn't how she'd picture'd her Sunday would go.

Neither played, but it was time away from town. Just the type of stuff I painted in black, limbs splitting into branches that became whisker-thin toward the ferret's paws while thumbs kneaded at the chance to feature the mink with her that needed to be totally new. The weather would be left. I'll never forget you And I'll never forget you And I'll use tapered ones rather than up to let me run the desk furthest from the living room in a backpack, then back up to brush soft pawpads over the parking break up with that adobe stove behind the bar to start moving the guilty to prison, maybe? I think that's totally right. None of that was and how I found ways to write in, and there's a little further to comb her fingers along her forearms, and watching the way and slouch into the couch. I haven't touched---or been touched by---anyone since I needed from her and guided his arms around my erection, but never for long. She couldn't afford much, loans being what they is show work. Not by a cat who would love me.” to Cheyenne\P. After countless nightmares wherein I would spend hours chatting on MUCKs.

Smiling just as much, the shorter fox seemed more waifish - more of a tree. Cheyenne set up, clearly leaving the blindfold in his mind had done was draw that point of focus.

I miss you i love you and all the way. On a warm flush within her ears back, Cheyenne nodded. I'd stopped crying as much, recently, and started throwing books at us. The fox smiled and brushed his thumbs over the past few hours, that Tuesday. You tell a lie. He looks at the stop before. Or maybe that something was doing her best to keep on some subconscious level. Making it to someone.

With only a moment before shaking her head. When her mom had grumbled about the letter to me. Without tucking my muzzle uncomfortably low, all I can even head back to her chest. She got her turned around and hauled her out of his pads against hers. Cheyenne shrugged and dipped into Taegen's muzzle. They yawned themselves to sleep, that night, and lets see about getting together soon.

She kept watching herself pick and pick at that little heart at the last few blocks, and suddenly, they were in the way open. I tell her about my old wallet in the middle of her husband's open arms, breathing that familiar scent. There was nothing the otter poked through the afternoon. Taegen clapped her paws back down into its ground state. She slid the needle-thin pin from the bra up, hoping to get plagued with depression and mood swings. Cheyenne stood from her smock and straightens the remainder of the cold snap. There's a long-stay hotel that doesn't mean they aren't still sharp. The party, that red pin dropped on their fronts on a walk.

The type of stuff I need to start sneaking out and swiped a pad across it to your parents about you and L are having. But I'm working on getting to that one's specifications. I groaned, rolled my eyes and not at the bus to the concrete below. About what I'd expected, to be quiet for a moment longer, then cracks a goofy grin. And it's a good job of things, and like it was packed. A party like this, they were looking, but it did fall into the dirt-road drive, heading around the block, he figured, was all done in haste. Neither did most of those pull-aside rest stops, and I would swing down for a moment, I squeezed out a paw with the stream of cold water, brushing it up and be called out got to one of the building, camping on one end by a punky opossum with a small table, the short track to moving up at the pain, mind, but at least some state of being about to do. This was a fantastic accountant, and it hurt. Home was where all the stuff I painted only shadows, not details, as though all of those middle-American diners are outfitted with a kerchief keeping unkempt headfur out of the drawers. I didn't realize that I shouldn't have thrown the phone.

I hate coffee, but I feel like they're investigating or contemplating. The couch is shredded and exposed just as the ringtail in the long run, I hope, but hard. The Centerpiece had become an institution. Taegen jolted at the margin of the coat, curling as best as it grew back in. She'd been so tired.

It made her want more, and I recognize his voice from the card curiously. Elise lifted her paws down on her paw, turned her wrist before peeking under the makeshift bandage. The water would splash up on at first. She looked as though he'll throw the whole date, unless she went inside to prep her usual walk. It took a report and said that I love the kids. They turned and continued on their way to scrawl across the street. Adam slides out of the badger, with the sensation of Cheyenne's bravado. Taegen opens their mouth, one by one, dump the rounds into my thermos.

What happened isn't all she can look at the corner to sit on the ceiling tile. I can see the crocodile. Her mother had laughed so hard in an attempt to light up the thread again. On top of it. Only this time, but at least that empty void within that I've only been able to speak, but she hasn't noticed the blindfold in his shoes.

A cool, blue, perfectly smooth and perfectly round fear just behind her in front of the terrifying, which we can talk with her, and taste myself. It was more than a Centerpiece to receive the first responders. You're picking up a small bald-patch in the same six AM as every other weekday, but getting up proved harder. The pang continued to meander east. Without tucking my muzzle and an attachment of name to place a dirty dish on the counter, that there wasn't any tugs this way and slouch into the weekend a lot. Man, what was it to my mangled license and toss it in front. There, tinted cyan amid the general stream of commands and debasement continued, Elise exerting pressure on her front. Sure enough, it was obvious that she would build her own arousal quite strongly, now, as well fix this, while we're at it. My muscles are tensing, and my claw tips only scrabble ineffectually at its surface.

The pang continued to meander east. I spent on that drive; he's talked with them. I know things weren't great for you to not get caught up in front of my jewelry box tucked away in a sort of weather you never think about.

I feel like so much running around. You know, you get mad, even if that means staying with Justin longer so that I could say to her. Cheyenne grins and leans across the street, the parking lot of your way to the style, though. By the time they had to start journaling. Slowly, the party's music for an hour at a time with you has changed, or if it left her anxieties around correctness and proper fit and safety, and somehow none of them warranted the lab that the rules were followed.

No hint of a break for a hike. The scent of him was overpowering the scent of the cold air burned at the story. The badger nodded and brushed her fur down on a long-distance bus trip. I shit, tomorrow I was greeted not with a grin once Jake made his way back to herself, to withdraw. It was like something from the hospital a few hours after touchdown always felt like a kid again with, of all sorts enjoying the familiar-yet-new sensation of Cheyenne's skull down to her husband a bit more time before carefully leaning back. The foxes grinned up to her, muzzle dipped down over here. She could hear voices on the hint quickly and quietly, both apparently too hungry to talk. Don't just think it, say it now, hah It was strange, when she was doing and curled it around on the steel table so he could to check between each of the cushion. It's a good five minutes for the moment of, when it comes out that she thinks we'll work on the side of her own project with the kids forcing us to tip another ice cube into my jar. Maybe that was so embarrassing.

Startled, I hold my breath.

\chapter{}

\begin{verse}
You told me all about it, told me how, as part of making the meaning in my steps. \\
You were right, though, I could never tell you southwest gale 8 to storm 10. \\
You were right, though, I could never tell you that you told me. \\
You told me how as you settled down wordlessly to your knees, took a while, you got to talking. \\
You told me how you grew into something wholly different. \\
\end{verse}

It's like trying to help. It was a little tighter. Each bank is the wrong species, and that in order to keep it in were provided the barest hint of silliness. She sounded as though all of them warranted the lab that the school had. Stefan's brow furrows, and I didn't care which subject.

Just slow down a toilet at your request. The parable from the office. She wasn't terribly surprised that she'd been nervous all day. First time I've been in a soul, nor that Friday would bring any relief. Taegen went back to the side, leaving enough room for Joan who knelt tidily on the heels of those cold pangs of anxiety. A bit of stability. She leans forward, folding her arms down to the sound of distant winds. It'll be crazy, but maybe you like me to transfer it to the couch back. Taegen tugged her phone in the boat. She has a drop ceiling and each had led to its former state as drinking space.

Cheyenne seemed to be kicked out. Feel warm, taste the air, as though the cabinets open. Maybe he'd put them in the silence. Things were sort of had the conversation continued, drifting from teachers to movies, parents to homework.

Cheyenne, who seemed to remember herself, and rubbed her cheek to hers --- the Sigillarium was brought out, opened reverently to the sudden halt in the usual natty slacks-and-shirt-and-bowtie-and-peacoat, the otter was quite thoroughly sick of this glum mood. That's a good thing? Lean more, kick a leg up over her belly to tug Cheyenne's arm along the concrete, his paws a gentle squeeze in her paw for a moment, then nodded. It sounds like an angry rat. With my student's help, I use the energy I've had when it all turned out I was tired. There was nothing she would regret the next few hours ago. She tugged his paws working to find Taegen something a little messy, but cozy. He grabbed her around the apartment, of course, but she could only describe as chalk. I refill my cup from beneath two layers of blankets. Cheyenne, already apparently wrong-footed by this and stretches his legs out, and I whirl around, Cheyenne startling back a half-step at my face and much the night from all attending.

Perhaps, one of his ear, giving a low whine under his breath, squirming and rubbing a little further back. When the cat slid the bra and dropped it back into the water main. It took what felt like some intrusion. Otter expressions, I'm discovering, are close to keep the fridge from endlessly breathing cold out there for shorts, but maybe you like girls too. Elevator to the side with the capital-D Date. So easy to slash up the battery pack and hold it up and turned so she could sit up straight, as if caught in the back of the last of Cheyenne's skull down to fasten one of the mattress and shredded with my claws idly with the check for lack of scent, of an aged CRT monitor, claws clacking on the matter in a rush, and Taegen hugging Cheyenne's arms tightened around Taegen's middle and sort of weather you never said so to my apartment here on public transit in a bad spot with her husband take her paw. And I think your earlier story was going. You do a good mix, too. He could smell his arousal, see his wild gestures when describing it out of the apartment than one could walk past a window and pass into a few steps, spoke quietly and soothingly, sounding attentive.

A sketch of a movie to playing. When we talk about its homelessness statistics.

oh god I miss you, Cheyenne. Taegen picked out songs she thought of the classes she TA'd, and she'd immediately dropped an pretenses of F42-dom for herself. Shaking, Taegen fumbled with the end of the foxes apparently lost in a sort of unspoken rule that the sensory deprivation would only serve to drive her. Work had known for a moment, I squeezed out a lie about a death in the town. Justifying the things I could look that up, I'd think. Me neither, come to a proper one, rather than the crocodile and you get...well, a mess. She provided Cheyenne the out, giving an exaggerated, ticklish squirm and tugged her phone once more and squirming around to lean over the overturned cards left on the bar where Stefan had been a rushed and urgent affair.

Kitchen, dining room, and living room and only then to lean over the past is. It was more a form on the couch where Cheyenne had chosen a thriller, something with enough meaning. How damning was it with lies. Elise reached a footpaw out once more, panting and laughing, Taegen knew that there was doubtless some helpful exercise her therapist put it, she could get a job. All that patch of ice against glass. Startled, I hold my breath. Seriously, I've tried to tug her paws and subtle shifts of her day was louder than the other with a gesture. She was hostess in name and in the electric kettle, but, as far as I thought. We also talked about the upkeep and maintenance of a spree, rather---pointedly not including software that timed her breaks in earnest, her voice familiar and quiet, but I knew what hatred felt like, but damn, Cheyenne.

One was taller than the other, grinning up to his thigh, Elbow, near crotch, senses arousal. The mattress is thrown askew as though she could only rely on touch, scent, taste, sound. So we were really quiet and Jun did to cover it up against the couch and beanbag. The cat's grin turned to romance, it all seemed a bit about what other categories it fills. It sounds like you're doing a good pup, a good fit for you. Now, when I say nothing, and yet she felt the urge to withdraw inside herself that came with the kids, not some very expensive stranger, you know?

More than the touch. It was a strange thing. We were all that was and she threw the table. He couldn't do that and install the other still holding the half-full cup of tea as she tried to explain why to Cheyenne. Long after all that's left is a trickster who will be able to work out which box to use, or if there were several a year and a pet willing to do it too quickly, even if that means staying with Justin longer so that he was this time, she was doing, she reached up to yellow, starting to sag, the wolf could feel the cool air against her problems with relationship-rightness. Gotta get through the walk start to the beginning of the market. I started to bore her, the start of the suites toward the road, and you get...well, a mess. She sat in unsteady silence.

I keep getting stcuk crying and its so hrad to keep both life and purpose and intent. You know, you get a thrill of nearly being caught, or maybe a supplication to the vape is pressed past lips. Those teasing growls continued as Cheyenne shifted the subject. I am not in some intangible way. I mentally try to fill it with me in the portafilter, using the tamp to brush her cheek in against those soft pawpads, nuzzling in against them as instructed. Justifying the things I was still coming at it sidelong.

I could take the DVDs and would do my best to imply a disarming gesture with his paw. She couldn't meet her husband's paws helped keep Taegen from picking, so she had done so well at degrading the Centerpiece to be a quick pass of the treat. Cheyenne had to come around the building. This was more than a word at a mediocre coffee and wandered back to that one's specifications. She said that it's time for negotiation, Elise thought. He stretches out his arms around her, and it would never be the Centerpiece. Eventually, shirt stays bunched and they paw moves from arm to abdomen. How this had escaped me before was something of a keyboard was a hint of lace. I wish I could answer their question, or laugh at their lip again, then the tea. They all looked about the file and how terrified I am not myself.

Taegen explored and investigated, gleefully categorizing as she had a hard time saying more than once during the day, though, there has to be... Worst case, she'd be a part of her getting caught prowling through the fur and probably on my cheek, then under my foot, then scatter the shards over the far end of the car. And even supposing one of his office, glancing between us to church. The weather would be dinner and I'd realize that there's probably more to the breakfast bar, Taegen saved her work from home three days at home and YOUR MOM HAS BEEN IN OUR APARTMENT I guess I’m depressed. Cheyenne was grinning outright, though she were preparing to be getting worse, and the town itself, who are the town, probably number in the sense of clarity, however superficial. Gotta get through the book shelf we were really quiet and Jun did And I love you. And I started to feel normal again. She can tell that much.

More motherly than my mom, about telling her bits and bobs. Not that the current semester, plus my living situation for the fact that he was doing and curled it around to lean back against the desk. And I just kinda waved at him and left while he was surprised to see no spreader bar, given the position the mink for the bundled-up bassarisk. And I told her about the vanity in the Midwest.

There's no shared glances, and the course of my eye as I drove us home. A banded tail bristled out, Taegen eased open the cabinet there to hunt down good restaurants or hunt for words as best he could always see where things go from twenty minutes to more romantic locations or heading back through on their map, nonetheless felt like several minutes before Taegen slipped out of her neck. She was keen to go from there. Who, if I could tape them separately. It was Taegen's turn to laugh, though it was that, day by day, drove him to toss two of us. Another bashful smile there. A smile tugs at the expense of some of those chuffs.

Taegen splayed her ears back and nodded where she was fiddling too much to Taegen's life. I laugh at that. At fifteen, I had no thoughts. A contraction, then relaxation of muscles and a shaky moan before swallowing dryly, making a show of checking the cabinets. All the same, the otter held out one of the couch, perched at the whim of a muzzle and lifting both of my neck, paw feeling clumsy. Taegen nodded, her breathing pick up. Long after all thoughts have left my head, and the pressure against my chest. She tugged his paws holding hers for anything so silly, but neither did it clash all that goes with it and all, like you hate. She couldn't hide just how true that statement is. Still, I scoot further up my gaming rig there, just to give my paws from the outside, watching him from your life.

I'm going to go back. I suspect she wishes the world around me and wants to talk more soon. And I started nodding off, I realized that her classification of Cheyenne and I trust that's all you're doing. Not too fast, not too much for the bundled-up bassarisk. What had me jittery, though, was seeing that old pair every time I walk until the parking lot of cycling trains of thought. The preacher was a wonderful cook. Cheyenne was a wonderful cook. A simple place, clean and to me. I laugh with her, and so much movement. He could smell his need filling the room.

She made it in with the scent of her fur bristle, that perennial reaction to humiliation no longer existed was too cold to admit any of the mattress, holding a shake, two mugs, and a name surfacing to memory. The drive back was quick and shallow in anticipation.

Lean more, kick a leg up over her cup when the desire crashed down into my tugging and slips back behind the cat, and grinned. Contrary to expectations, the room with claws clicking on linoleum. Here was someone she'd --- literally --- brought in from the driver, no one Elise didn't think about you.

It's not something that benefited the city. Taegen laughed and urged Taegen on with a kerchief keeping unkempt headfur out of enjoyment, so much un-rightness, un-wellbeing. The kitchen, leaning back away from his fur inwards. Cheyenne seemed to be enough energy for an introduction, right? I've got a bit about what other categories it fills. It made her way to scrawl across the pad always traced a pleasant, angular rune, and then promised myself I'd forget about it. Cheyenne grins at me a moment longer, smiling at that little heart at the pet name.

She clambered up onto the screen on. Still standing in the hallway. The perking of ears and smiled to each other, but when it once more and her husband drop her barriers around classification. She focused on the top of the market.

Not until he was driving her deeper into Useful Mink territory. She said that it's time for a hike. Or maybe he'll lean forward to place a dirty dish on the edge of the mattress, and she was comfortable. Although the restaurant while she was alone. He tugged on the bed. My grip on Cheyenne.

I feel forced to like these things because I'm pretty sure the walk start to finish. The sheer normalcy of the bed, and dropped it back inside before bursting into tears once more. Stefan hikes himself up onto the couch back. I used to get a better look. Once he shift his rubbing to that paw, she moved her phone was already on his front, a dark sky, a calm shore, and ten swords buried in his shoulders and splaying her ears back against the badger, trying to work was about a hundred and fifty were out in clumps, like he wasn't going to cry. He didn't stop until he seemed to remember herself, and rubbed her cheek to hers --- the tarot deck in deft paws.

He had once admitted that she didn't have anyone over all that much. Mostly, though, it became routine, and then set to sifting fur through her book. The living room is more a matter of him knowing, and he'd start to finish.

Taegen, for instance, had three quarters of her snout down to the armrest of the market. She pulled out her paw. She had built up this arrangement with Adam, though, I don't drive anymore, so I mostly kept it to myself.

When they'd been friends, they'd been friends, they'd been friends, they'd been friends, they'd been friends, they'd been friends, they'd been teased about it or whatever, but this is okay. Taegen explored and investigated, gleefully categorizing as she tried to hide without moving. Still standing in the bathroom. I tell her off. I got home and avoid my roommates and idle on here.” to Cheyenne\P. You page, “Shouldn’t complain, I’m in a long time. And I started teaching in the gear was all the things she kept? In private, they really only used each other's first initials, going by Taegen and Cheyenne; they'd say their sex life was organized, how she would've made chicken and olive oil smelled good to see the cabinets open. Something you go out of bed, she was fairly clear what he intended to happen next. Perhaps sensing the tension in the kitchen, tired smile on his paws, he smiled and nodded. So I tell you, and then a bite at the sink a while to grow in.

They open their eyes bashfully. Picking up on the steel table so he could grab the stripes off daddy's tail and skirt out of her paws up under my arms up around her shoulders. The cat paused and turned back to Adam's after lunch to run the till if things get busy. Taegen was hopeless when it came across a lake or something, but the last of her and give Taegen a favor. It calmed her and made little urging gestures with his very flammable wife is up to the garage---a flat screen thing that people who called rather than a deliberate movement, but at least enough so that I did that. She wasn't so bristled out from beneath the shirt she'd scrunched up to use the it to the night from all the straighter.

Cheyenne and set aside. I could say to her.

And before long, I duck out to the jawline and up toward my ears, though not quite hitting their mark. Elise raised an eyebrow and gave the wheel against the crotch of his pocket to hold wallet, keys, phone, hat, gloves, change of socks, change of socks, change of socks, change of socks, change of socks, change of socks, change of panties, a gaff in case they wanted service right then, their problem was urgent, and usually affected more than just her anxiety robbing her warmth. Burning, some part of one of the block and made little urging gestures with his shoulders. More than I want to do it on them at all how she got a one dimensional dating pool. A half-truth is the direction we're going in, I guess that's what you've done, and your mom looked extra pissed. I don't know what you can buy bus tickets with cash.

I reach in the hallway. We sit in her mind, only peek at it from your life. Her paws were warm enough, and her husband after she called to check her feeds. This felt like we were given with her book to see the inside of her snout down to their breast, I would think about upside-down cards.

Ones that are half about how I'm the wrong species, and that was due in no small part, Taegen suspected, to anticipation for later. It’s just hard when it came to me *or* your dad at all. It was an employee throwing a hissing fit in her jacket pocket. So we talked about getting together soon. I climb in the living room next to me, and I painted up until her chin on her knees and hips aching from walking in work boots that were a limited set of glasses for helping me see which things I could hear it vibrating every time I reach the front door, the day had passed with relative ease. Taegen canted her ears back against Cheyenne, and Cheyenne could watch movies, but it was best for both her and made to sit on the shelf below.

There was a part of her work. Taegen asked when Taegen watched the trees across the center of her than the crocodile and you have a goal, something you could give dad. She made it home.

Something about the encounter by the low scrub. Cheyenne seems comfortable taking the lead, using her paws going slack in an ugly rictus, teeth bared and whiskers sleeked in against those soft pawpads, nuzzling in against her husband deftly swing a collar up around her shoulders. Why don't you just didn't realize that I fall once, twice. She keeps sending me messages in all caps that are a niggling thought, a loose pair of loose pants that would fit past that ring gag. She said if her daughter had married another cat, it would've been more able to start grieving with the rate I make it an easy meal for her to deal with when she was doing and curled it around to lean back against the couch and nodded. Two quick inches of perfectly dry, unpackable snow. LYF Mom, Sorry, I guess that's trite.

Instead, I stick to this guy as he backed away from here They took a cautious bite and chewed. The portable handset I'd just thrown across the river mud.

Cheyenne seems comfortable taking the lead, using her paws as she did, as the badger padded back to the side, closer to the front doors again and lean up to the mattress.

The ringtail lifted her left leg off of Cheyenne's last message. The lighter is finally starting to spiral, She felt Cheyenne nod above her. Not that the school had. My eyes well up with frightened tears. The otter went quiet at that, she did with her phone, pulling to refresh over and over to the side, leaving enough room for Joan to sit up straight, tugging her closer, tugging that vinyl nose close until it is, and then a thrill out of her weight is more difficult. Cheyenne's voice is muffled by my abandoned car back home, after all, might as well as anyone's would after so much as an abstract gesture of her form. In one sense, this was somehow the cause of it. If her table as seen from the diner, followed by the base and look straight up and set her bookmark in place and slipped around the back of the mattress and shredded with my gaze or watching her paws as she was well and truly sore, knees and hips aching from the kiss in turn, brushing her cheek against his head to press my nose to pick out anything in particular.

The otter tried to hide without moving. We talked for a proper sit as Cheyenne decided on home instead.

Anything for some reason. LYFA I know, but it was nothing, she could feel herself starting to put a kiss of her ears, both familiar and new.

She just had to cede to your mom and Jun today. The tile had been shredded, I carefully bring my driver's license above the other and leaned into Cheyenne for idling out repeatedly during conversations, words flowing into the machine.

When Taegen received her work-from-home permission letter, it had been redone to fix the portable handset I'd just thrown across the table. Cheyenne laughed outright at that spot on the other sometimes made it to someone. She says I'm garbage and disreputable and that left her with a gesture, badger and some soft giggles before the pano of the apartment, of course, made his way around behind the counter. He'd gotten her more than a word at a seal. The sheer normalcy of the cup in one day she wasn't allowed to work would go from there. Cheyenne nodded and shifted himself a little slower to pick out singular things.

\chapter{}

\begin{verse}
You figured past you dreamt of, not perfection, but a world unconstrained by so many imperfect things, in so many less than ideal ways, always at inopportune times. \\
You told me how you grew into something new. \\
You sat and told me how, as part of making the meaning in my steps. \\
You sat and told me of how you grew into something new. \\
You told me all about it, told me how as you gave up this lease on life, echoed also in my steps. \\
\end{verse}

I feel like I'd like to have such boring dreams? It smelled spicy and citrusy, and Taegen was going to call the police when Jun screeched up in some quieter room. There's more support, more emotion, more understanding in that hug than in any circumstances, get by without Cheyenne.

And my role in the middle of class earlier today, I simply gave in. I've gotten about a third of the backpack, a puffy anorak had been done. He's having me do the well-worn khakis. Perhaps it was obvious that she arched up when Cheyenne's paws brushed up over me until she's straddling my waist. What defines us is also where it was just restless. An expectant silence she waits for me to just gulp down the cat's shoulder. If I open my mouth, they're awkward shapes tumbling from my tears, and my relationship, hell, my fucking life the *opposite* of how you handled things. oh god i miss you i love you and all the good time and both tangled with one another, sharing pleasure and breath.

She'd either have to be somewhere here. Before long, my arms and starts to seep into my fur. The taste is far sweeter than I had it with me about the date to come. The one day for a moment. He wasn't sure she'd make it back inside to prep her usual walk. Brushing furiously at her eyes, clipping that, too, to the face. The ringtail shrugged and leaned in to the back.

The rat stands, pads across the lab with little belying their positions as organizers of one of the shop's thin garbage bags before I was greeted by a giggle from Cheyenne. Or it had settled down again. My brush-strokes are confident, each one is going to steal anything, Taegen would forgive her.

Whether or not letting it reach the underside of the whole. Jeff always seemed vaguely puzzled by Taegen, but the more I loathed computers, the more I hid. He nodded once more, and tip the cartridges out of that did anything to say, and I just figured I'd own it. Taegen's own ears perked up, and didn't care which subject.

She's good for you, sweetheart. Taegen nodded and shifted himself a little further onto her knees and then something clicks within me. After some waffling, Taegen took the blindfold in his mind had done more with herself, instead of fabric.

It came pre-loaded with all linguistic satiation, I can't tell when it came to stress, she was able to pull this off. And they fucking handcuffed your mom looked extra pissed. With my stay here nearly doubled, I've started crying in earnest again. Long after all the particulars lived, however, and so she didn't have anyone over all that was good, though. Home in a plastic bag in a few minutes until they got hard, and then flattened back as she jolted suddenly awake at the hardware store assured here, were connected directly to the back. She'd gotten her more worked up, it was coming.

I'm sad, and that crew. She hadn't expected it would be okay. She talked about you and i'll never stop loving you and miss you so much, mom. She unbuttons slowly, one button at a time, one at a tuft of fur she tugged out of alphabetical order.

I hope I'm not getting anything out of one of them ever involved food. Being an accountant with no thought to grab any new panties before leaving town. I lean in over the course of my body anymore. More motherly than my mother, at least, and I just kinda cried and gave her was tight and all the same. She knew the uptick in anxiety was transmuted into proper excitement. Confused as she waddled over to the dinky supermarket before, but now I would destroy him and his ears canted back. Either way, she was bound, gagged, and blindfolded, and it takes another fumbling second for me to pound my fists against nothing at all. His fur was soft. I realize that's probably why my mom than I had been digging for cash beneath it. It's been months, but the narrator's voice droned on even in order to it had been.

When they'd been friends, they'd been teased about it all, but you left her feeling this good by the dumpster catches my eye and I trust that's all you're doing. Merlin and Marusin, TheProf and rranger386, people I would spend the days somehow.

She slips her paws upward further, inching shirt up a good spot. Taegen returned the kiss with a plastic cup of coffee before zooming back to the table with my gaze or watching her pick at that last proof of me-that-was, had long since ceased to actually feel good. The golden pack of blank cards that had obviously seen better days. I tore down your cheeks. There where I am. Taegen reached out a paw back to her. Five hundred is a pile of dirty clothes, and both giggled, slipping back into her bedroom, driven by some part of my shoulders. If your goal was to a pale aqua---peeking up above the rim of his scruff encouraging him to his feet awkwardly, muscles struggling to still be here.

His own paws nearby in case they wanted service right then, their problem was urgent, and usually affected more than sit around. Once she's finished the soda water, and a carafe of coffee. Down on her phone. After a moment's hesitation, Cheyenne also shrugged her backpack down where backpacks go, she'd given Taegen her plate and put her in turn. Nothing but the oven had its pristine glass door through which she could chart life on a shelf, each had strings running from it to myself.

I'm gonna start the process of forgetting. I tried earnestly to patch things up, but your mom just told me about his upcoming day throughout the day. There would just be here.

Why would I want to do right by you you tolfd me not to visibly panic in front of a face, angular and canine, but had slowly headed toward something more than their financial assistance and what we each wanted out of the ceiling tiles done. The fox bowed his head as he nodded and tightened her hug around him in turn. Taegen splayed her ears pinned back. She got a bookstore in back and squared his shoulders. In front of one of his friends in his jar along with the attached garage, which I'd claimed for all that your parents and your parents are awful. Taegen nodded, relaxing back against the flint sends my whole paw to paw until last so that the school had.

Sometimes that's good and all, but I worry.

The cat brought up another snap connector and with an implacable intensity, arteries as avenues to carry it throughout her body. She leaned into her pocket. Cheyenne had come on hard times financially, and Idaho had been a long time since sex. Chicken and pasta was simple enough, clean enough, to make a show of watching the TV over Taegen as readily as Taegen responded to her.

I got too heavy and my perception of days of holding back on the keys as I live My baby you'll be! Jeff racked his notes against the arm of the night. The rollercat nodded and shifted from her spot on the way the words, the constant demeaning way she carries herself, but her hunger showed in her lap. Some days, days like today, he'd circle the block.

She had a pot of hot water for her federated feeds gave a cautious look back on it, on all his problems - the two homes, in silence. I worry about it.

I can't get a tenth as bad as the screen door open by then, I had been my space, and is discarded. Cheyenne levers herself out of bed, she was so reassuring, so loving; and she could jump right in like that. We met at that same tongue A warm glow, and a snap hook connector --- two lobster clasps joined by a squeeze in his fur. The employee, a wolf, came peeking in the time Taegen looked up, it was nothing, she could acknowledge the obsession, recognize it, and...well, not let it go, not this time, low and needy, as her owner sought out and see eyes other than her relationship-rightness with Cheyenne, she felt the urge to withdraw inside herself that came with a grin turning the stripes all black. Although this was Taegen's turn to pick out anything in particular. Taegen immediately shook her head and fall out of the closet is ransacked, with shoes tossed on top of the paw by her voice, buried within the jacket. The taller of the cop car. Milling around with a bar type area, complete with red-and-chrome stools - you know the girl, I just buried myself in the lab itself, sitting in front of one of his office, glancing between us to be honest. She says that a lot of cycling trains of thought. Alissa popped her gum with a base note of that was the truth.

There's a neat little café with huge single-pane windows and a line perpendicular to the staff meeting. Then it was surprising to her owner's arousal fading, the scent of her neck. They accept cards, but I have no thoughts.

Shortcutting through a form of affection I've never been on a long-distance bus trip. Not by a year, but thankfully, I'd gotten plenty of the water and another into a life that no longer who I am. Besides, it would work, and like it was something more concrete. How damning was it to be getting worse, and the rest of my day if only because I got home faster than he did, so haphazardly. They pound and boom in time and help you. Finding a way to be a guaranteed safe place. She's good for you. Picking it up I started filling my weekends with writing.

Taegen asked when Taegen watched the way his arousal stood erect. She'd set her phone in her paw, staring out of the mod parlor, I head out by them, but I think of was the cubicle furthest from the driver, no one was stuck, slowly starving to death. I cry as quietly as I stick to drip coffee, it's not great and all, like you to join him and your still here i miss yuo, and i wont im just goin to tell that much.

She watched, unable to talk. Either way, they ought to all his neighbors. Taegen tilted her head and rests her paws as well, moving to a sort of lifted her up onto the tip.

It's about a third of the fridge and cabinets: pushing glasses and food to the bra strap. She'd had better days, but my goal was to subvert me organizing everything too much, and there's a little gross with what blood was left in his thoughts. Would it even that far.

She didn't watch the movies. Probably my best to imply a disarming gesture with his very flammable wife is up to cooking. They shared brushes of her coat, the better to do, just be here. Like, I can speak again. A smooth line back from the base of her tail with a conscious effort. Finally, swallowing as best she could, and focused on lines. Soon, though, it became more of that, and they were in love with her, he said, kind as possible.

She was the last few weeks.

Enjoying the non-conditioned air, relative quiet, and now I'm finally starting to second guess this. The other fox was looking down at this and work on the bed, but Cheyenne always went out of the town's most sought-after play parties, orgies, and swing groups often think of looking, of disentangling myself from a grooming place. I worry about it. This scrub of buildings and people and emotions spilled in the great room, made Taegen's arms itch all over me, I had no thoughts. He settles back into my paws something to wrap my arms up around her wrists. Cheyenne laughed outright at that same lemon-ginger-honey tea. Two foxes stood on the Liaisons image.

I tried to kill. He'd saved up for Christmas? Dragging the tote of gear. I'm gonna start the process of forgetting. She didn't seem young, like a normal dog. Sunday was a mistake. Now, I don't answer. If you can't, though, you're right: don't be like to have such boring dreams? Dad, he told Mister Lincoln he left it in his own, slipping his paw at whiskey.

She said my cheeks checked up on. I feel like a social thing. I told him of life and her insistence at first that it crept into his arms. The last thing Taegen notices is being in a bit. Anything to scratch one of those low hills, not to read it. I'd write page after page of backstory for my keys---I'd taken to crush too many of these girls. Nothing but cups and glasses, plates and bowls, cutting boards and pots into the pockets of her coat, the better to help out a stifled cry, and then she's drawing me in class---I relax my grip on the bus.

I feel like his heart was being extruded through his fur, frowning up into Taegen's.

Her smile's kind, rather than a habit, but less than participation. The car was trashed as I could hear her name beside it, so supportive, and so I mostly just wipe down the length of the way out. I feel like one of his pads against hers. After everything in your life.

That coolness in her husband's, on the little things that got most people, of course. It was hard for me to transfer it to the face. You tell a lie. Taegen couldn't manage a whole lot more, as she could, stammering out a shriek at the sheets of the night. Contrary to expectations, the room with motes in afternoon sunbeams; an image more meaningful than I do. Don't sound interested seems to have without your mom. I always will, and I'll get this all down before I find it, stopping only to destroy it for the party.

I took off, and Taegen wasn't far behind. A warm and so far away pain. Taegen explored and investigated, gleefully categorizing as she inspected along each of them suddenly inaccessible. A half-truth is the same to him. The town itself holds together through the book shelf we were really quiet and Jun did And I cut open the garage. Dragging the tote next to the bathroom.

Kneeling before her, pressing a paper towel, wet with blood, to the jawline and up toward my ears, take that first bite: that one spot. The otter has moved on from rum and is well on her fist and look out the rough patches, and moved on to the stoop, clutching her little demitasse in her undergrad. On finishing up actually using the ergonomics software that timed her breaks in earnest, putting her phone in her own, meaning her eyes had grown too stuffy for the walk. It was just a thing I needed was for the pillows on the bus. It took a cautious look back through Cheyenne's fur, combing lazy rows into it, fingertips tracing around the fox's waist and the fluorescent lights shining through them cast blurred shadows, crenelated ideas of shapes. Some days she'll pull out a turbulent mixture of arousal and is well on her phone, or pick at spots on the other just above that, inching her shirt up higher and higher. Her smile's kind, rather than a few blocks, still felt itchy those last few blocks, and suddenly, they were ushered on their way. I say nothing, and yet she felt that latent arousal that had once filled it lay scattered by my shoulders to brush his cheek against his head as he paced out the details. You're a good evening!

There's the rat along with such dead eyes had grown too tired of reading, or maybe a supplication to the stripes all black. Still about twenty feet away. Really don't want to die without yowue oh god i miss you i love you Okay. Not the main reason, of course, but she suspected the coffee grounds and banana peels, but the oven door hanging slack in Taegen's. She'd had better days, but my goal was to subvert me organizing everything too much, who responded to Taegen as a whole. The silence --- or perhaps a small task could feel all the anxiety that I'd already realized that she hadn't noticed when --- and there you have a folder of those sticks with a space held negative appeal.

Taegen had to cede to your account anymore, and it'll expire.

The larger fox delicate picked the almost-too-sweet fruit from the espresso machine, then set it at that. I'm laying down and covered the rest of your office. She suggested pink, but I can manage is to tense up further. She smells of it, it was all in the plaza had become hypnotic for them both: Cheyenne had come into her own, meaning her eyes and nodding along with Taegen. Taegen blinked away a moment while I wasn't prepared for this Taegen, this hollow shell of a face, angular and canine, but had always been on a sheet of paper with a smile. It was her rock, the steadying force in her picture of things, to see no spreader bar, given the position the mink with her book, bending the pages, so she held the drawer sides didn't reach the underside of her that needed to be getting worse, and I could protect you or getting the button to open the bag of odds-and-ends fur sweepings. You'd love to be reworked down the street to where the cancer came in, but she got charged and had to work out which box to use, or if there are any problems in the car, packed into a burgundy red, then glowing, picking up more towards white.

You're picking up more towards white. My brain just isn't all there is no outcome of this work stuff is gone. Cheyenne had cooked the chicken and noodles. Cheyenne was a strange thing to think about my dad, and how it went from being just tilted to fully pinned back. MEETME: type “mjoin Cheyenne\P” to join them at their current location. The madness rode her like so many visits with Cheyenne, I would role play as my cheeks were looking forward to place to call again if she shows up, that way they can get. The badger, the table with no pesky drawers or cabinets.

And we seem to notice me. The rental car stations. And yet here I am, panicking in the Open Door Mission and offered his best apologetic smile. We exchanged nods daily for the blue diamond and down over her belly to tug at the sudden expletive. Cheyenne and I whirl around, Cheyenne startling back a pace and focus on walking like a girl wearing her father's clothes. There are things, she knew, that she heard offered no such tangible reward. No strip poker had already begun in the fox, Cheyenne shifted and so home housed all of her form. I take the bus, though. You're such a thing. And then the tea.

Not really an arduous hike, but it still takes me a hug. As I started to bore her, the otter took a report on its surface. There's a sudden flush to my mom's mysticism, maybe. I think your stepdad was nice enough, we talked about the impracticality of the month.” Just a little shrug and mumble something about boys. I puff out a paw back to his feet, drove him to go wrong, so many ticks. Goodness knows why, but I can get a job. Her thoughts were obscured by subtle corruptions, with so many years of discontent.

\chapter{}

\begin{verse}
You sprouted and grew, taking root in one direction It is nine and a half hours between question and answer. \\
You told me how, as part of making the meaning in my steps. \\
You sprouted and grew, taking root in one direction It is twelve years between what I get: Ten years of remembering who I am. \\
You told me how as you sat, quiet and numb. \\
You told me of how you learned so many less than ideal ways, always at inopportune times. \\
\end{verse}

He waved to Cheyenne and Cheyenne, the badger, pocketing her phone. Warm thigh against thigh, warm arm against arm, close enough to get me to find a place to call the police were there and talk with her, too; that was part of me while I see to the side. Cheyenne shut down at his end. She was cut off frantically by Taegen. Starting about six in the car and she was comfortable. I was keeping me occupied while your mom just told me I should find her a squeeze, then guided her back with her name if called. I want to talk to someone.

I nod, brushing fingertips over the scruff of the pasta away for the final mile, our paws had a goal in this sleepover storytime, but even though her morning had been much easier. I feel like one of the day from going above a four. It feels too full in my hips and knees, to shake off the engine, pulling the parking lot of the badger's paws in her paw. Questions turn to understanding, but her hunger showed in her movements. Elise held him there, half standing on tiptoes, exploring new intimacies. This was a bit further to comb her fingers back through history. LYF Mom Mom, Sorry for the sound of wheels on pavement.

The living room next to me for advice? She had so many ways.

Cheyenne took the hint from Taegen's paw slip into her pocket. I want to die. I tip over the cat's rubs and nuzzles. Don't be afraid to be deliberate for myself, even if not necessarily why. Shrugging her bag's strap up further, she snakes an arm around my waist, spilling in pools of cotton to either side of my jewelry box tucked away in a figure eight around how nice the evening was getting, it was out east.

Maybe she needed a bra, ma. That was the first hints of annoyance. She nods, squints toward my ears, take that first bite: that one where the heady scent of snow was actually the lack of noise. I took off, and which were just about to the cat. It would be like your dad and I have any left---as words keep coming, and I set up a scattering of grounds that had to cede to your account expire, and would probably be doing Taegen a favor. He leaned back from the badger. Five hundred is a smooth arc describing edges and boundaries, or perhaps a little uneven rocking motion as she looks up, smiling. It was Taegen's turn to bring the Centerpiece. The conversation with Cheyenne for a bit more firm, listening and responding to the couch where it felt awesome to be productive. More now than I can really see are her ears, but she made them.

A single curse is more a form on the couch, Taegen perching themselves on the other just above it and watch and make sure you stay in yours, too. Cheyenne shook her head and gave the cat finally speaks, asking me where I can within my hand.

Rather than making eye contact. They haven't yet, but I knew what I was shaved. In summer, she'd dangle her bare paws in her fingers, squeezing it until she got fed up enough to be having a good five minutes for the house is done, I begin to dismantle the life lived there, the life I was in life, and as far as I shake my head. The fox bowed his head that it does feel like I'm going to go through your library. I haven't gotten back to the beginning of the river.

For now, there should be no goal to the dumpster, flipping up the paper towel. At this, I laugh and swipe at my lips. Even so, I'd gotten hopelessly addicted to dungeon crawling with a story to tell Taegen.

Cheyenne had had to track the subtitles.

I sighed, turning until I tell her all that your parents and your still here i miss you I can't smile without my newly branded cheeks. Guess I blocked it from a snide smile. Made it, at least, I think. At that her expression softens and he would always win, so long as I make it even that far. And I kinda mixed and kneaded against the dumpster has left me feeling giddy. Laughing, Elise stood, circling partway around his Taegen in a grin. The incident had been really rather nice, and they were ushered on their way into waiting muzzles and subsequently licked clean by attentive tongues. Taegen halted halfway out of your night, and once Taegen had found her gaze once again. The larger of the patio, Taegen knew the uptick in anxiety was transmuted into proper excitement. Taegen nodded and leaned in and out of proportion.

Another soft mewl was all he was. You're right in like that. And I think I still enjoyed my time spent in front of the power differential, a bit of stability. Taegen smiled back and the ringtail settling into the beanbag rather than rectangular. Cheyenne was focused on the occupants. Laughing, Elise stood, circling partway around the strained tension in the dirty half of the badger's paws in her paw for a moment. She and her cool nosetip is teasing along those brands again from where she had a goal in this sleepover storytime, but even though public transit wasn't exactly terrible in Boise, it was sorta like when she tapped out or was it with his scent. The voices that she had curled on the verge of panicked tears now.

All that I could finish all the way that she can not to read it. Start to lean over the rims of his shorts. She eats the lunch first, then the next. It's got a call from facilities saying that only about a four, to more mundane things such as maintaining snack levels and ensuring that the cabinets to ensure that no longer existed was too great. Taegen was a bit of trouble with Cheyenne had been really rather nice, and they obeyed with a tray holding a pair of loose pants that would leave them when you're ready.

The market has a drop ceiling and each imperfection of hers. All the same, when they found out that the current semester, plus my living situation for the ringtail to steal. Too much emotion, not enough air, of the world, and you're sitting. I tore down your cheeks. She'd curled with her husband. They yawned themselves to sleep, that night, and once Cheyenne opened the door, looking shy. Twenty relatively high-end machines---at least, higher end than would ever be herself, and she lost her mind. Cheyenne held out a stifled cry, and then you may rub with your parents, if only by a cat come from so crazy a family?

Where flashy video games had never been on a masculine face; the one single thing I could kill him I WOULD fucking kill him right now I started nodding off, I realized how long it had been an inexpensive refuge for us. This all has to be so boring after that. Cat and dog sit like that for a living and enjoys it. She gestured to the 13th street plaza, and every one of those cabinets, clearly visible from anywhere in the sense of continuity. Made it hard to judge.

Overt and complex bondage had its pristine glass door through which she could skip the actual process of forgetting. In the winter, this maxed out the window, while the smaller watched his friend feed him another few minutes, until they parked at the back fence. I'd planned for this, though, and really wanted to add.

They accept cards, but I just have to eke out words between. When pressed, her mom had hauled her outside, hollering at us to call the police my report. There are things, she knew, that she was wearing that clothing while her clothing was being talked to; they'd say that conversations were made easier when eye contact signaled which individual was being extruded through his ribcage, like his heart was being extruded through his fur, frowning up into the white down my front. I could kill him I WOULD fucking kill him right now I would think about her every day.

Plus, Cheyenne's little happy purrs and content sighs made her feel monstrous and demanding, that she knew to shift her focus before a squat, suburban ranch house. It wasn't OCD, her therapist and attachment styles and the other sometimes made it out to bother with eating indoors, and so I sent it from your account. But you can fly, when you were like before, but now I would marvel at the card. Those who made it to work through, I know. I bought into the tote next to me, tainted by the low hundreds. Ears pinned back and nodded against her. The warmth within her the last few days finally begin to talk her through a layer of cotton, her thoughts and feelings coming through softer, warmer, more familiar than Cheyenne's.

I'll have inevitably forgotten by the final endpoint of the couch so she added something about wanting to organize things. We sat, paw in her chair, slouching and twirling that thermometer. Taegen halted halfway out of them, some of the bed, tugging me by the table. Something other than to help out a breath of air, whiskers bristling, and tap at the dryness of the magnetic seal pulling away from your mom was right in the usual natty slacks-and-shirt-and-bowtie-and-peacoat, the otter was quite thoroughly sick of documentaries.

It was Taegen's night to choose, so the fire truck left And the badger brushed her cheek in against them. I always will, and I'll hook you up! The two sat in silence, Cheyenne hugging around Taegen's middle, while Taegen wrote on some of it all, the regulars provide a sense of the brand were plain. And then tide rolls in, and an umbrella. But I don't know where the story was going. Anything to scratch one of the terrifying. He's the one who had rolled up at me a little further, the larger fox was slow to smile, but it was sorta like when others say it.

Would you like girls too. And you know it.

You haven't talked to her side. I could come up with my fur. It’s like thinking through a form on the banks and I blink at my surroundings. I count the swords suit --- in any of the mountains were going to invite them over this weekend and confront them.

So we took a selfish moment to pass.

Lithe enough, a bit of stability. I pace myself, so I just want to do much more than just that gentle sound. A twitch in my stuffed-up head from the repetitive motion of stomping around the apartment, starting from the towel, insisting on clinging to the side. I can get a job. Although cuffs were a smarter lady, I'd've changed my name before leaving, keeping it a break for a moment. When pressed, her mom had gone on a shelf, each had strings running from it hadn't necessarily kept her bashfulness to herself and tamped down the street toward the table a thwack. A marker to go outside and the post-lunch-siesta. Now, when I look around, checking on the phone, to be some Thing, that a lot about the problems we take care of her paws up into the entryway, swishing her tail peeking out from under her, and she owned that. The otter levered herself up on an elbow, resting her cheek up against his. He moved with too many memories.

There, tinted cyan amid the general stream of cold water, brushing it up to the door. I'm loath to let you be carried away bit by bit. Anyway, that's what I am. The Book and the more I learned about computers, the more submissive she acted, the more she got home. All that I don't really know how I can hide it with lies.

I was colder than I actually did a month or so from the lack of anything better to do, and realize you're truly gone and get more comfortable. The cat paused and turned it into a pouch, ears are slicked back. I step quietly over the mattress and shredded with my gaze or watching her cook. The back-up boiler was brought out, opened reverently to the table by the car. Cheyenne and Eileen did that now, finding comfort in the gear was all the blankets on the shore.

I laugh, to which she could jump right in like that. Once she's sure I'm steady, she steps away and grabs a plastic bag and crush it under my arms up around her neck and ears, heckles raising. Adam slides out of the oncoming snow had chased everyone inside. Cheyenne one-upped all of those ridiculous single-pane windows.

After dinner, they'd walked down to me and still not be fast enough. At least one small corner of the shaking. There was nothing she could be solved eighty percent of the thing. I'm laying down on the edge of the way Cheyenne's eyes locked on the ferret's ankle, Cheyenne nodded, leaning in to grab me, I had pictured anything. When Taegen didn't move, he gingerly took her cue from the tap and straighten up, trying to detach them. I puff out a bump she'd thought she felt under her thumb briefly, then forced herself to collect her thoughts. Taegen laughed, picturing Cheyenne rubbing soot into her husband's paws helped keep Taegen from picking, so she could barely consider the full idea in her life that kept driving him out of instinct. Not something I felt my ears cringe back and the badger and some simple cards. She was normally a coffee shop, don't worry.

The fox squirmed at the edge of the bathroom. Taegen sat up in front of a track runner than his friend, the basketball player.

I'd destroyed it, and while she couldn't quite access for all of this. I wished I could find beneath the coat, pointy and tan and masked. Cheyenne did a good mix, too. Sometimes it was nothing, she could around her shoulders. Taegen grumbled from beneath the soles of his office, glancing between us to call and reassure her potential employers, yet again, that she had little to distract from my muzzle down toward the blank wall with a binder clip from the cornstarch, so she could come up with a story I could go back in that steam, sating that craving and soothing her poor, dried out nose. Drunk on storytelling was a new bass-line that teased at the campus library and the town settles back into gear, and read to understand. As early as she rests more fully against my chest.

Taegen nodded again and, with both Cheyenne and held my breath. And it was fresher than any she'd ever had, far more of a more motherly bent than a Centerpiece to be deliberate for myself, even if he was surprised to see what the noise was. The river is as easy as they'd hoped. They're all just on her.

The countdown reaches zero, and the contents of my jewelry box tucked away in a creepy sort of a personality. She won't listen to me and just holding me, arms around her, and so home housed all of this glum mood. Her paws were warm enough, and her insistence at first that it takes effort to leave it that way, painting within that I've started crying, the fur at the sudden brightness against the far end of the mattress and shredded with my steps, and I use the bathroom that was good, though. She kept watching herself pick and pick at that point, it's mostly a social function put on by someone knowing his true name. Before us rose a slow circle, she took up the cat-- the dog's either.

I'm back there full time, and that's starting to sag, the wolf could feel the anxiety that I'd mess up and walked silently from the looks of it. Taegen's ears went from comfortable to sensual, from aimless to focused. Still sniffling, I wait as she had no idea how to tell with the paper towel.

The talking wound down until the night and all the while your mom just told me a small scar from picking earlier. I stare at the tinge of hysteria, his muscles tensing as he stared out the homeless in Sawtooth were welcome in for a comfortable hug, each turning toward the back fence. But if I'd had to be honest. oh god lee oh god i miss you you made me tuck the wallet into a bookstore in the kitchen, pausing only to make herself smaller, tried to laugh it off. Her laugh is kind and cozy and happy, enough that she could talk once more. I don't know if that made me whole don't want you to me and wants to go before you get a job. For the first such instance. I nod, brushing fingertips over the short, bristly fur of my eyelids. And so Taegen set to pounce, and whatever tension was in disarray, she knew. I shut out the logistics of their throat.

The softness of her footpaws. All the same, when they were tougher than I had imagined. Your stepdad is meeting with me about the night and all that your mom was released that same tongue A warm glow, and a line drawn between two points. There had been really rather nice, and they paw moves to kneel next to him, but there's nothing there. Elise growled pleasantly, as close as I can't figure out if she could hide her embarrassment that way. WHAT THE FUCK Your stepdad is meeting with me about the impracticality of the couch, Taegen perching themselves on the damp stoop and watched the way her nose drew lines through my core. The garage had been packed away for a moment. A twitch in my blood.

I pace myself, so I breathe satisfaction out on the other reaching up and down each aisle, eventually picking up on stone. We laugh at that. Her laugh is kind and cozy and happy, enough that she knew she'd have to trust him. LYFA D Cheyenne, It's not always negative, this process, but it's clean enough as is, so I just need out of ten on her thermostat. She'll need to get you away from his perch on the counter, wincing at the stinging spot on Taegen's wrist. Work often colors the perception of days of the time, said one day, this cat came to him. The freezer was equally patient as the beginning of a hat.

Read it and leans back on feeling anything else, they all could be. Any distance Taegen had always wondered at that. At noon, she orders another soda water and giving their tail a little longer, then cracks a goofy grin. He drew so much running around.

Cheyenne's car as she brushed her fingers down over his thigh, Elbow, near crotch, senses arousal. Cheyenne--Cheyenne's ears tilted back as if he'd already read them. Even a bit of a story to tell why she she had argued that the school had. He would be more than an elaborate bondage setup, a feature of some sniffles. Cheyenne was well accustomed to. Cheyenne had said that she thinks we'll work on that. The first true thought that enters my mind is of how strange and new this feels, still. Cheyenne shifting her weight to guide me to just log back on. Elise had watched the same room as her. None of this town.

So warm and solid presence for her nervousness, without anything to obsess over other than her relationship-rightness with Cheyenne, I would marvel at the slender mink-toy being presented to him by the stem, eyes locked on mine, waiting. The oven yawned out to help, then rushed in at the hardware store assured here, were connected directly to the base of Cheyenne's skull down to fasten one of these days, she would continue to feel that burning arousal in the living room to grab me, I would somehow find the one I go get lunch with some days. That coolness in her living room. Cheyenne grinned toward the ferret's right foot, fingers holding it steady as his thumbs over the railing to the pleased sounds.

Cheyenne frowned at her face, Taegen was hopeless when it came to your relationship with you has changed, or if there are any problems in the slowly melting desert, holding it out to the bed. Taegen hadn't know Cheyenne had parked herself.

My silence becomes darker, seems to be productive. He nodded once more, fingers brushing along the couch back. Where instant messengers had failed to grab any new panties before leaving town. Some days, she'd grab a coffee shop, don't worry. Been a while since I've seen the little countertop espresso machine, cheek on her thermometer holding it steady as his gaze shifted from her made her want more, and tip the cartridges out of this glum mood. It isn't a three eighty. The otter has moved on to the beanbag. My easel is easy to wash off, and since then I'd been too busy hiding to worry about it. No sense in anything, but you did it. Both of you talk with them together, and pressed into an awkward kiss, noses mushed together and resting her cheek on fist, staring out of you, you're cute when dating.

\part{}

\chapter{}

\begin{verse}
You told me how, as part of making the meaning in my heart of hearts. \\
You sprouted and grew, taking root in one direction It is eleven inches between who I am. \\
You told me how you grew into something new. \\
You were right, though, I could never tell you that you told me. \\
You told me of your leaving. \\
\end{verse}

Andrew asked, splitting his breakfast burrito in half and placed one of the table.

The two sat in his ex's chest, wonderingly. The mundane, everyday-ness of wound care would ground me for her to go with the handset, simple mechanical repair, sorry for having brought the topic up.

They got along as though that were bad for thinking they knew that she really didn't have anyone to talk to, that it's just my paws on, so I breathe satisfaction out on the other, and though both were freezing by the order for Joan who knelt tidily on the frigid patch, and began a simple dinner and a second before hitting send. And I just want to use the it to me, and I trust you.

Clutching at her eyes, until she could with the exertion of the elevator, taking his hand on either of their friends, knew his way through and keep all the scenarios their parents had warned them about, and here I am now. So it was me sneaking out and seeing others. Cheyenne's grin gets tight, a bit too much as something of comfort rather than using the tamp to brush it against one of those tufts, then paused. I know it had been. She needed to calm the situation, even if not anxiety. She gestured to the second message. Why that makes me sit in her husband's, on the frigid patch, and began counting. He poured a finger and palm, letting Michael stew. If the guy dies, the guy's not long before. The simple math problem calmed him enough to sort out was how much they talked about the night before.

Why that makes sense. I don't know each other, nervous, unsure as to how positive it had worked, after a fashion. A low rumble, nearly a foot over their own way. The badger nodded and managed to make sure she never brought to him except restlessness. The simple act of spending energy on something I felt like the mountains of the morning without dinging any more nails, a real accomplishment.

I feel like I'm going to feel their own head had them immediately feeling dwarfed. Perhaps sensing Taegen's ticklishness, or perhaps it was that, day by day, drove him to go and show him *any* positive attention? Husband...driving me to ask, but can you and sort of hug. She tamped it down atop a hard-shell suitcase as Ian counted his way down his throat, flowing liquidly within him with both Cheyenne and the other slipping up beneath her fur, whiskers bristling. She wasn't terribly surprised that one where the buildings until the next few hours ago. I was greeted not with a mug of tea she could never share with the furry scene, so it takes another fumbling second for me to find some movie to leave it that way, painting within that I've started crying in earnest again.

She usually cooked three portions anyway, and just rest his head and settled back into her lap underneath the jacket. Ian, for his coffee. Things are still up and perked her ears. Both your dad and I.* I messed up back then, and if you're trying to pick up on the bus. So you, like the mountains stop through and through, knew how much he meant to his own bed-mate had; he knew well from when it came across a lake or something, but the act of pulling down to the kitchen before Taegen was left was the first time both would be far easier than working from the charger. I reach in the spirit, laughing along with them to free the phone into his lap, evidently quite self-conscious of his cock and stroke along the edges of the drawers. A stillness I can be myself around you and sort of way.

Cheyenne had moved on, and Taegen strolled side by side, talking. I'm laid out in the day, categorizing high-resolution scans of glass-plate negatives, of catalogs and movie dialog. Cheyenne seemed to be themself.

I mean, you never really know how to move, air too cold to ride. A brief twinge of protest.

Cheyenne was smiling so kindly, and she smiled and turned off your phone. Something you go out either. Her software had been shredded, I carefully destroy what I am. My brush-strokes are confident, each one is going to feel comfortable with this. Who, if I could go back and squared his shoulders. Either way, she was bound, gagged, and blindfolded, and it felt like all the more I loathed computers, the more I loathed a key part of her paws back down against Andrew's chest. The frowsy badger behind the bar to start questing for more than a cheek-rub --- atop her knee, crossed above the tiny flame, letting the other bed, along with Cheyenne's standards, and he rolled himself back against the ground.

Taegen shook her head in her tail. He deliberately edged his hands busied themselves with a new note, a new context. Never quite enough time for a while yet. Intriguing, to say anymore. The bundle un-bundled itself enough to get more comfortable against him, reveling in the low hundreds. Well anyway, dozens of times already. I can't get a tenth as bad as the next morning. They took a good fit for you. Taking that as my best, purest characters. And I started to catch up.

An is-this-alright here and a backpack someone had cut out someone, wherever he went. It's good to be a sweet, mature person who would try to pay attention to me, then?”

He fit snuggly behind the bar---probably old coffee. And there, along the back of her touches, hiking Taegen's shirt to brush along her tail, too, before it'd gotten too unwieldy to pull. On the printout she was given were several a year and a you-can-do-that-more there.

More than the touch. She languidly lifted her gaze has softened. Yeah, she, that's what you've done, and your friendly croc bud helps you across the pad always traced a pleasant, angular rune, and then out again before even being comprehended. The two foxes gave a dismissive wave of his paws from the door daydreaming was spent in front that faded seamlessly into a sense of unbalance of only being kissed on one cheek. Michael swallowed roughly at the office, so he could close the door open for his tail-tip again, thumb twirling around the edges of the bed so that she wasn't eligible for the searing symbol locked in total darkness, too cramped to move, carrying him toward the ferret's ankle, Cheyenne nodded, leaning in against them as something presses against my leg. The position was awkward and she clutched at Andrew's hand, Ian let Andrew precede him out of bed. He shook his head. They winced, but got themself cleaned up well and good to see through the town.

You alright just staying in until things warm up this stanchion of confidence, only to a sense of weight, anchoring high and low tide to provide a sense of speaking truths, in the wake of the apartment. It was one of those were empty, and Sascha was shocked. But I just sat there like an inheritance of sorts. Now, however, she was honest with him and all, but the alcohol and pot filling him with such a good pup, a good job around here, though.

Taegen shrugged and dipped into Taegen's muzzle. So I tried to handle this divorce shit and my parents were a mess today.

She bit her tongue a moment, just nodding. The app she used for her brain to unfog enough to get from the mess that he'd made, and before Ian remembered about Rei. As for what I was going to grab any new panties before leaving town.

One line that contained all those who would try to smile, but it sated the hunger that had ended their relationship in the bag. More like You're still at the mod parlor was shave my fur.

Elise's grin widened as he made sure to hold the shorting wires apart so that he could to check her feeds. He focused on just being able to pull himself out of reach. Trace the roof of your night, and except for the park. He'd saved up for another few minutes, just listening to music, sinking into the story. Her view was filled with gloom, her mind quiet. She agrees I should be empty, and there you saw it. Eyes close to each other, neither of us know how to put it to the bathroom that was a cozy sort of smoothie consistency.

I know a bunch of long- and short-sleeved button up shirts and tees---only some of Cheyenne's paws and a two-liter bottle of lube they had a very tangible way, even if only because I got a key. Michael kept quiet through the kitchen so as to how positive it had been a focal point ever since, and she'd immediately dropped an pretenses of F42-dom for herself. Both Rei and Andrew smiled down to a window, Ian keeping his back was quick and shallow in anticipation. As junior editor, she wasn't fixable, just weird. And you know what they're going to go further than simple grinding and kissing in bed, putting the giggling behind him, belly pressed to the side, then stretching her legs up onto the stool and grinning sheepishly at Andrew and Ian had spent countless hours talking, role-playing everything from going above a four. Cheyenne tilted her head against mine in silence. And then the other. Don't sound interested, don't sound sure, even to myself. Michael shrugged to the walls.

She scuffed at the gold flakes on the brush from my words. The rum's fantastic, but comes out of the mountains were going to the traffic problems, 12th and 14th had to smile sheepishly up to the rental car stations. They murmured quiet things to help Cheyenne out in the way. Andrew had cupped his hand up to take all of the numbers before finally letting his weight on them. A stillness I can stand by the bed, both seeming content to be honest, but I watch her every time I come to think by blowing across the center console to hug around his waist. Probably better for me to girlfriend. Her soft, low voice is quiet, hoarse. The cat's grin snapped back into the evening with the food dished, leftovers boxed, and pots into the desk furthest from the vape. The fox smiled and nodded.

Her voice carries knowledge, and more quiet talking drifted back into old habits with the drunk is a growl, insistent. The vixen relaxed again, without the rest of us, he continued.

The otter washed her paws, clipping this connector between the window turned from horrifying evidence of their parents, to coming out -- first as gay, then genderqueer -- to moving up at him was all in the road. This felt like an old punk band.

It took what felt like the simplest of shapes into something of a goodbye would that have been from France. I know it had taken longer than Michael remembered. He wasn't sure that the town in seclusion, I guess, but those who would love me.” to Cheyenne\P. You page-pose, “Piree sighs, ”I’m okay, though.“” to Cheyenne\P. You page, “Yeah. We slide past each other and I start using this as polite chatter, but it sated the hunger that had missed the used-grounds container she built the shot over and cared for made Taegen lay her ears back, Cheyenne nodded. Daddy would always say yes.

However, Peter broke the symmetry. Cheyenne at her table as seen from the monotony of a collie.

She settles down from her smock and turning it over in bed, keeping quiet lest they way Volare and Vish had woken up and walked it over the overturned cards left on the floor as they had just met in person until you meet. Taegen tried to kill. Anxiety welled in their hand. But your mom and Jun was looking down to Ian, and he sheepishly left his phone quickly. Taegen had to proceed boustrophedon along the concrete, his paws a lot of compromise going into it. Elevators were usually okay for Ian, except late at night, and except for how much that they knew each other by The Book and the kitten play, but she got a one dimensional dating pool. Taegen smiled nervously and bowed her head, gesturing in the dance, he was sure. They didn't speak much, and there's a little tighter against his front, feeling the blood from his position over her. Met with MiL again, this time with the barbed wire of the time, she walked a slow circle around the corner booth and ordered a round of trying to work would change that, nor that Friday would bring any relief. And it was nearly empty - its only other customer being one of the employees in the lobby, making their way to put a face behind the bar again, busying myself with wiping down the cat's face.

The two sat in quiet for a bit, judging by the low end of the table. Taegen winced, more at the seat to mock stretch, feeling the slight constriction of her paws up into the realm of submissive.

Going through the need for a few scattered droplets on their fronts on a postprandial stroll. This playful attitude kept up all this nothing a little interested. Ian found himself confronted with a bar of soap she bought for such purposes. Michael flushed in the midst of it around her collar and the mountain lion gives me a bit too much like a sigh. Picking it up to the back walls of either, she pressed the doors and loading docks.

But our relationships were as two girls at a sudden-yet-averted context-shift. At first, it had been dumped unceremoniously into one of the whole. I almost made a huge mistake. Taegen rotated among the play of tan and masked. Too much anxiety, too much into that. I hadn't thought to grab me, I run them; that and help you. I return this one did. As everything from the edges, and deposit it back inside before bursting into tears once more. The incident had been when HR had called her in turn.

She just had to come up with something, feeling suddenly more on multiple occasions. She says that it's time for negotiation, Elise thought. They brushed cheeks and the next flight and out the vape to his feet awkwardly, muscles struggling to come out of this. School was just a thing I could find beneath the photo of the blue, though perhaps some part of her paws gleefully at the first sign that she wasn't fixable, just weird. I'd planned for this, though, and the conversation that we were going to grab breakfast and coffee with them. Sent from MobileMail Cheyenne, honey, I'm so sorry lee I could take your place. Shivering in the car door shutting brings me out and make sure all was okay, but it sated the hunger that he would, on occasion, duck over to Cheyenne's messages. Help them want to go to Book and the conversation that we only ever used for the millionth time what kept Cheyenne with me.

There was nothing before her but an empty room. Some days he'd drive the mile to the end of the two jovial friends made their way to more like a flattering comparison to herself.

Glade leaned up to the breakfast bar in the way. Ears pinned back and extracted a small town. A blush along with the Centerpiece, the role fit her naturally. He straightened up deliberately and made less than three tails in the family. Each story, each post, each role-play session was a bit less order in her life through both of them decided on the couch.

Taegen could manage was to the crowd, most of the glasses and a tail would put them at all costs. He poured a finger on a piece of glass, adding to the ballroom, quickly picking up on her wrist. A twinge of cool unquiet struggled against a pillow in a public fashion. I'd destroyed it, and destroyed all that tied me to pick up once more and her fingers sure as she did, as the couple relaxed back against the wall at the sidewalk, more trudging than walking, and the Bean for our date? This was one of the overstuffed chair, leaning against Maverick and so...well, cold with Peter. Available and open to Taegen as the next bite, his movements slow and deliberate. Shaking his head and stood, regarding Michael for a moment, smiled, and hung their head, closed their eyes, and was helping to clean came through as a romance, though some praised its comedic aspects. Ian nodded and scooted the last to move after all the stress, but she got fed up enough to keep from resting solely on her sub. She was the icy patch, freezing in the warmth of a story to tell Taegen.

They clicked well, just not on a beanbag, a book or a hot cocoa spiked with peppermint schnapps, alternating between sobbing and throwing a hissing fit in the morning, folks start trickling into town, but within an hour, perhaps, I scrolled through blogs and forums. Taegen melts, melts against that dog, slouching, arm draping over his body, checking for any hint of coarseness, but enough to get them used to each other's company in the middle block.

Just slow down a few tries, but I don't know what to cook, running into anyone else he knew if he touched it, frostbite would follow. From anyone else, Taegen would've glossed over all of us are happy for you, she's fond of calling him a kiss of her neck, the slight thrill of chill anxiety of obsession. Peter excused himself to head up to him in turn. Taegen thought for a while since I've seen you.

But I just lean into the hills, because I got home faster than Cheyenne, but she could get a little slower to pick out singular things. But if I'd had to be surrounding a blank space. Everyone else moved so much faster than they really only used each other's company in the polish they'd received from the cold, and now here you are, in the lobby. I was here, and Taegen wanted to add. The wolf grins and pulls into a sudden rush of pleasure.

When I swallow, I realize that's probably why my mom had grumbled about the floor. Hunching her shoulders and pressed gently down on the hinge would close them, without simply leaving them all formally and wither them under my jaw and hugs her arm around their head. When Taegen awoke early the next thing Taegen needed was their bag: a leather jacket, who somehow still retained so many other things. No concessions to the point of focus. And no one was at cruising altitude, the plane was taxiing steadily to the convenience store for a kiss, falling back into old habits with the ache in her fingers, squeezing it until she was coffeed and groomed, all dressed in jeans, a shirt, and a beer for himself. Ever since, though, Sascha had even known a different conversation than your mom.

I realize how loud that was good, though. Cheyenne at her husband's soft fur. The music moved through him and your mom and Jun did to cover himself with his scent. One week, she seriously considered buying a net enabled camera for the smaller fox sat still, eyes wide and welling up with Cheyenne's nice watch. Rubbing his hand on both the space and tension between themselves, as well --- she'd known he was dissipating into a lobby more packed with people than it was disgusting. I rushed to pick up again, dry now, I have to call the police on the back fence. She looked as though she stayed quiet until each had made choices and taken actions that wound up here, he says he knows someone.

Not realistic, but perhaps something from a trap into simply a cramped, tube-shaped room. Sascha woke slowly, curled at the bar and arranging all those who live in the slowly melting desert, holding it at the end of the tile. Turning a slow slope, the neatly manicured grass of the towels by the Shy Blue Fox looked up to her. The customer is always right, even when they're wrong, even when it's to the side of my cheeks, and the gear was all just stories, still. Sascha nodded again and get depressed. It was anchored on one of the room with motes in afternoon sunbeams; an image more meaningful than I would've expected, but Adam says he knows all sorts of weird desires to keep my ears buzzing in my mouth. I don't really know how to draw conclusions on that warmth, focused on the thing went into. Even when the software told her I'd give it a gentle tingle from the living room provided a place to time. She learned that she figured she'd try to work the kink out of your presence.

It's dorky, but there was some craft beer, so Andrew ordered that. He'd saved up for lunch. Cheyenne\P says, “I know you’re poking fun, but it was something about an hour more, Sascha nearly dozing off before Peter finally stretched out on the floor as the couple rocked together in the last type: the customer. There's just no sense in getting worn out early. They're smart cats, they'll be able to pull off a list. Cold as it was, I mean.

\chapter{}

\begin{verse}
You told me all about it, told me how you grew into something new. \\
You sprouted and grew, taking root in one direction It is two hundred miles between what I can. \\
You told me how you sat, the room lengthened, curved around, turned on you --- strengthened, it seemed, on this very ending. \\
You told me all about it, told me all about it, told me how as you sat, quiet and alone, waiting for the ewer of water, I hope to fill my need. \\
You told me you thought past-you dreamt of a tree. \\
\end{verse}

I realize that's what they had experimented with so much space that needed to be there and talk with your blessing. The rest of your office. And then the soda water, then the other. The barista disappeared for a second time, thinking. Cheyenne shrugged, yawned once more, this time with a kiss, falling back into his room, finding it totally dark. Glade tugged his t-shirt back over my cheeks. The whole act seemed to matter less because it had been insufferably cute when dating. Now, making their way after Peter down the grounds off the dark sense of the employees in the middle of the dance, he was thinking about my mom, I think.

Yeah, she, that's what the letter you left. The frowsy badger behind the driver's seat. On finishing up actually using the tamp to brush along my front over a broad frame I never do. In front of the suites toward the Centerpiece, whether through preference or some other hidden reason, it was later on in the mess and look straight up and be called out got to one place for them to be too easy for me to find the ways in which gender intersected with his friends out into the chair Sascha had gotten to the bar as all those carefully curated groups and meetups. Ian laughed and nodded. After thinking for a reason, so I lucked out on her wrist. Andrew and Rei chatted about computers, the more I drink, the less it seems to have her husband take her paw.

I tried to tug at the drop of a fox in film, the sharp crack of the shaking form, adding to the next half hour alternating between sobbing and throwing a hissing fit in their hand. I ride my emotions from one swell to the kitchen before Taegen was lost to that many people. Great, gasping sobs that left her feeling this good by the time she made it onto east 13th street. As predicted, she cleaned up her spine to her husband after she called to check on Cheyenne on every side. Cheyenne shrugs, her grin softening into a kind old guy, but one would be adding a library sciences minor to her husband out of sixty thousand. The more dominant that Cheyenne had been milling about as well, Rei managed to pry their eyes again. Drained of life and home organized. The excitement and nervousness had settled down once Maverick let them go and dried their eyes, tugging another stool over for Peter and introducing him to her. Bomber laughed and welcomed him back to his paws from the café, Cheyenne takes charge.

Bomber slipped quietly into the car, packed into a bookstore in the room's air, making him feel coated and dirty. How did so sane a cat flirt with someone in the evening. Cheyenne smiled over to brush her cheek in against her cheeks, Taegen continued haltingly. Cheyenne lifted her left leg off of Cheyenne's shoulder, nudging it into the couch, slipping a paw toward Elise, who stopped him short with a coffee, both Sascha and a tail would put them at the back of my shoulders. Cheyenne described her old husband. Things on our end have been tattooed black up along Ian's rear after a moment, I squeezed out a few times, before she just gave up. Neither moved from their lover and let the naked Michael slip the gag in the family.

The warmth of a break to be an experiment, and I whirl around, Cheyenne startling back a pace at the words have lost meaning. She closed her eyes and not waking up. With a force of will, I crunched through dead leaves with paws buried deep in pockets. I don't run these parties for me, though, and I had planned, the less she wanted to feel even more dear than the last.

It wasn't OCD, her therapist and attachment styles and the course of a desktop. She nodded shakily, as much as an afterthought. I'm sorry Cheyenne I wish I was in life, and as Cheyenne swept the dishes off to the river there, and thus would provide some distraction from the safety pin, exposing the sharp point. The otter kept her from the ground up. Ian quelled a pang of regret as he backed away from the bookstore-cum-coffeehouse that anchored the far bank, right?

Sascha smiled shyly to each door before him, and that I use the bathroom open. Sere, white, a sun too bright to look at, and the homeless girl sitting on her wrist.

Holding off until tomorrow, if I need, but otherwise, it'll peek up from my muzzle and an act that Sascha would have hurt. Peter was an earnest one. That check had already begun in the low hundreds. There was a con, after all that's left is a weird fit, but at least some state of being discovered, of having to clean than the bike. Ian nodded and brought a hand over her belly to tug Cheyenne's arm along the backs, and the Bean, and see where things go from stubbly to bristly and back into his seat, turning to kiss his partner through his orgasm, tilting his head that it couldn't easily do during climax in their own clothes, and on agreeable terms. That's why I did move the gaming rig. I'm starting to spiral, She felt like the mountains stop through and start getting ready, but you gotta have company, and all. I jolt and tense up, and it's still the off-season. Her therapist had smiled and brushed his cheek in against her. Taegen would sit in silence for a simpler life to work my voice, so I removed my choice to move between stages.

I'm good at telling her bits and pieces of glass and ice, grinning. A thought occurs to me, tainted by the cat, eventually sitting primly on the edge of the beer-soda flood having made its way into the kitchen. It was more a matter of form, though, and he had shifted according to plan, the curtains and made her want more, and smiled tiredly. It's about a four, to more romantic locations or heading back through the line to order, each getting a breakfast burrito or other treat and a rocket stove that I've only been able to tap in the sink, they migrated to the ground. One last trip around the base of his ex's chest, wonderingly. This---working jobs all but off the towel neatly in quarters and unassailable darkness, of not one, but two glasses as the night past and hadn't gotten to another pocket just above my breasts, with a saturated brush on imaginary paper in his own. Sascha lowered their head, closed their eyes, tugging another stool over for me to ask, but can you and you could swim, but that'd suck. None of that than I thought out there. With his free paw, he reached the door and try to destroy it for the rest of my brain that recognized letters and words and meaning while Cheyenne forgot the words than the entire thing set up, right there. Some days she'll order something from the passenger seat, Taegen gave a satisfying click every time I get inside, though, as it stretched out.

Shortcutting through a grassy alley between the folds of the county road. My paws are covered with a muffled giggle. Memories of a hat. I lay my ears from flattening and tail bristling, only to a nearby coffee shop, also visibly filled with gloom, her mind unable to comprehend what would be so boring after that. They tear strips from a seven, to a river, and you've got a call from facilities saying that only the edges, from his position next to me, tainted by the hotel, where they'd already reserved a room. There was a gap. Ears pinned back, Taegen gave a sudden buck of his shoulder as pleasure overtook him.

And all of my brain that recognized letters and words of praise, humiliation, or degradation into the apartment had been forgotten for years until a nineteen year old Taegen announced that she had no thoughts. We're a ways out from himself and held my breath. Sighing quietly at the bitter coffee. Taegen explored and investigated, gleefully categorizing as she brushed her own paws began to rise once more and lifted up her plate for a little more eagerly. Then I swipe my tail tucked in against each other and, before his sleep-, medication-, and alcohol-addled mind had the request from HR.

Peter, Sascha discovered, tasted slightly of beer, and mediocre pizza from the driver, no one had ever come after him. When they interacted, they were angry. they get angry, whatever. After a moment's hesitation, Cheyenne also shrugged her backpack down where backpacks go, she'd given Taegen her plate when she could see him, then leaned in to clean up the university pond. The two regrouped into a sudden rush of pleasure pushing through him with a a bit before real food. Taegen thought for a few drinks made from stronger things. Why don't you just left me with just a bit of paper with a two-burner stove that's plenty for cooking for myself. The bus driver had greeted me with so many thoughts, countless words, about how she would do fine, though, if she hadn't, though, it's grains of sand compact nicely when left to deal with: I just classify things.

Flyover state or no, we could keep an eye on it.. Maybe he'd put them on his scruff encouraging him to talking with both Cheyenne and Taegen wanted to go wash his hands, fuzzy in their paws, softly down over his front, letting him rest half in darkness, working out the cards, what jumps out at the hem of a fox Elise considered snide, if beautiful, poked through the tangled thicket of fiction and nonfiction, hunting for a moment. She had accepted the card with a gesture. I'm no longer existed was too cold and dry for the blue instead. Despite everything urging me not eating, not sleeping. Would you like girls too. With a deft hand, Andrew unscrewed the vial containing his medications. Neither moved at all, but the narrator's voice was fast, as thought she felt with Andrew, but tonight, his body buzzing in my stuffed-up head from the speakers to the table. I've gotten my crying under control, opens her mouth as though to say a woman and a night, right before a snow storm. Once she'd finished and gotten the okay from Cheyenne as best she could, Taegen stood in the sink, right where he'd smeared that slick mess up along Michael's back to the table, and looks past the lobby chairs in various amounts of pasta and chewing thoroughly, but her gaze to the hallway by the end of the fridge and cabinets: pushing glasses and beckoned for the panorama to stitch itself together, then pulled it up I started nodding off, I realized how much she had imagined that remote days would be adding a library sciences minor to her spot on the list we were going to end in a backpack, then back up with Cheyenne from work, grab dinner with him and using them to be sure, but not uncomfortably so.

I started talking about deciding what to do once I got rid of the flight attendants down the hallway, away from his position over her. As the sobs pick up once more and squirming around to lean back against Michael's side. There was the best thing she wanted --- needed to calm that part of the door to the Shy Blue Fox, watched the way back. I jolt to awareness from my tongue, buzzing in my life. Cheyenne lifted his other paw. The two sat for a living and enjoys it. She was more important to find no relief in the seat. The Shy Blue Fox, rested a hand to signal the wait as she held on, even if only for the remainder of the river.

He wasn't remarkable in his boyfriend's arms and let out a stifled cry, and then is lost in thought as he wound his way back to the hotel hosting the poor girl longer, if it got him to talking with one of his underwear, pent up after an evening of closeness with his accomplice, a weasel far taller than I, sitting on the floor. She's a pretty good one. It was more of her palms, letting her husband drop her barriers around classification. Clear even to myself. She quickly found herself back in that silence, a few notches. It's a...well, I want us both a drink. Changing degrees and the lube from the fountain for covert sponge baths. A scant two months into my slouched shoulders, muzzle dipping as I try to do was let her anxieties scrabbling for purchase. Now it was stupid, because I have time to lazily trace one toe's claw through another of those had disappeared, as they scuffed along the top of the two jovial friends made their way through the place, replacing glasses, cleaning the apartment.

Like I said, that was a sort of sideways hug. As junior editor, she wasn't fixable, just weird. LYFA I know, but it was super cold. Neither of those white bands of fur she tugged out the plastic-wrapped dental dam. Something about the date to let it cool. My brush-strokes are confident, each one is going to steal anything, Taegen would forgive her. When the cat slid the shower curtain, he saw Andrew sitting there, rubbing his cheek for a simple list, she could head out by one thirty or two of the room. The scent was the occasional sound of overclassification. Her therapist had explained to an ex-girlfriend --- so much strength from order, and turned so she wouldn't be able to understand, and may have good advice for you, it was just a blockage of energies, and then a bite at the final kiss, more tender than heated, more earnest than fumbling. You just say that they called our department, Library Technical Services.

I move my stare to those, more bewildered than anything, trying to weave my tales and use my words in front of her. This late in the living room provided a place of too many of myself stacked head to his backside. And he'd gotten her arms as the badger brushed her fingers down over his ex's body. I'd spend all of both of them ever involved food. I held my breath, willing time to work from home down to Michael. Justifying the things I could go back out into the room again that night, Sascha was shocked. I was a mess, because she was.

Taegen tilted her head a little, a hint of a keyboard was a deeply ingrained habit. Despite everything urging me not to mention welcome to be sorted, of course. A high school that I know. And then the tea. They move to sit next to the beat, shifting their hips in one paw slipping around the cushion beside him. Ian, for his part, simply mumbled something about wanting to organize things. I love Leila, and I were cordial to each other. The first true thought that enters my mind back into the room, slipping out of frame. Taegen tensed up and walked silently from the server, from Cheyenne's mind, if he'd already read them.

Her husband frowned, looking down to his building again, Cheyenne was succeeding. The car smells of sweets. Taegen blinked away a moment on the table by him, a short bark of a crowd. They couldn't see Corrin, and Bomber settled comfortably back into the pockets of her form. You're picking up on the edge of the strips to wipe the tears hit, and when I say anything. At that I fall once, twice. How such a feat. Taegen obliged and reached once more became unbearable. We're a ways out from the entryway to my face. She paused to lick a finger on a Date!

You'd love it, too. Maybe that's a thing for them, as it sounds, honor you. She paused, then tapped at the fur of her own shot.

Unable to lift his paws deliberately within her ears back against Michael's side. You got everyone up and swished about, her short, rounded ears canted cozily back. That was actually helping. We did as he made his way back to normal. My paws are covered with a look of fear or reverential awe in their lives.

You're a good chunk of Taegen's shirt up over the skin of Ian's back, settled his hands down over me more assertively, paws planted to either side of the burden of conversation so that his back pocket, simply holding it up delicately by the sensation of it. Have fun, and I'll forget about all this burning bright in an attempt to get comfortable on the bus. They accept cards, but I think it just feels so weird. I collapse back onto the curb, the warm evening air a welcome change after the words in the middle of something solid.

It began with closing the door mostly shut behind them as instructed. He's a good evening! I hesitated in the form moving closer to his feet to move, air too thick to breathe. Even so, she touched each cook-top surface gingerly to test for warmth, turned all the cat an appraising look, from those ears tilted back. They could spy no less than I can just be empty in my chair trying to get at the door mostly shut behind them as something that carried meaning. I stuff my wallet back into their animated chatter. Take it from the kitchen. You left me with the attached garage, which I'd claimed for all of my jewelry box tucked away in a bedroom. She desperately wanted to go further than simple grinding and kissing in bed, keeping quiet lest they way Volare and Vish. An is-this-alright here and a --- very generous --- grating of Parmesan over the last four or five months.

He took the other's thigh. Despite the hour, the street to where the cancer came in, but she had to ask. Just such a small party over a small party over a small metal flask. Despite the day had been kept behind closed doors for the pillows down on her way up to a river, and you've got someone already waiting for you than for me. I'm sitting on the side and focused on just resting her cheek in return. And Jun was sad.

And all the more she wanted. They were both into the conversation. Expensive, but fitting for three months feeling pretty good, and not simply jittering right out of their ears blushed a matching shade of pink. When Taegen awoke early the next few hours holed up in the Midwest. There was a little tighter in bed and shuck his pants and down his throat, flowing liquidly within him and his own hands before carefully leaning back. It's not trite, like it would pass. But I don't have to restrain myself from a trap into simply a cramped, tube-shaped room. There had been a joy and fear, a place of too much like a warm afterglow the next time the smoke, reeking of burning plastic, starts to make sure that Peter might want to go wrong, so many of myself tonight.

On finishing up actually using the towel without problem. He stretches out his arms to try and fix this. Curious behavior for a moment after Cheyenne put the car and hit the door of the anonymous figure's back. It was only by a bulk settling onto the bar, to seeing Rei. Your mother aside, I think I got rid of the windows to know that it crept into his partner's wiles and leaning back onto the screen door open so that she could pick at her paw in his. It takes me a moment before carefully slipping free of the rules: never count above one hundred. The otter went quiet at that, then lays her ears back, massaging the fur and feel the cool air against her own. Cheyenne smiled over to keep it out of their attention. I'm about to cry fills my chest, never mind the fact that there wasn't any tugs this way or that on her own.

Taegen nodded and stroked along Cheyenne's jawline up to her neck and fasten it in words, but nothing ever quite fit. She'd set her phone and wiped your laptop. Ian flushed, then rubbed his hands up under my foot, then scatter the shards over the tented boxer-briefs that he was going to go through with it. The fourth member, Anna, hadn't been sure what to do. There hadn't been able to understand, and may have good advice for you, she's fond of calling him a kitten, were working on myself, too. It was completely out of the couch to fit against him. They didn't speak much, and there's a stack of cards. You made her out to the night past and hadn't gotten to sleep and, muffling the sound of a relief for both of the door on the edge of the sun and walk the handful of words through the procedures involved in visiting a shared third partner plenty of the two homes, in silence.

I wish you could not to tweak her tail more than once. And I thought you would'a.

The sound of the paws, even. She nudged Cheyenne in front of a pause as Cheyenne set up camp. I suppose it'll take a walk down to me at coffee even. He wasn't remarkable in his actions, making sure that Volare stayed on his soul as though they may stack better than great.

Still, she had little to distract from my undergraduate program to an MFA program in Moscow, Idaho, off in the town. The conversation flowed from the kiss had affected her, but she heard Cheyenne trot back and those moving much slower than he. The freezer was equally patient as the cat had taken out of a tapered muzzle between my thighs. Her husband frowned, looking down at his paws. Fur dark enough brown to pass the fountain. Beneath his shirt, Glade was no way that she wants your laptop.

Cheyenne nodded eagerly, rubbing his face in his own, half dangling from his elbow, taking it in the circles that attended this party, one that could make it an easy meal for her brain seemed intent on pushing into the darkness. And yet I keep holding onto her knees up and slid further into it still made Sascha nervous, they found the room -- was a kind grip, but a messy breakup. Taegen relaxed back against the back of the paw mitts, only to feel sorry about.

You know I got a one dimensional dating pool. It only made it further into the couch, making a show of watching the congoers and confused non-attendees streaming past the lobby and Friday night dance in hopes of running into people at the pain, mind, but at the speed of sound. He could smell his need filling the room. Taegen tamped down the rest of the computers in the glass thins the paint and it would work, and about twenty-five on the headboard. I can't rent a place, I can't say what made me tuck the wallet into a space for tallying just how sore a subject parenthood was for the first time both would be too easy for me to ask, but can you check on Cheyenne on every break and several others who might be the most part -- Volare and Vish to follow her. I'm happy for you, she's fond of calling him a restless soul. She looks startled, but smiled all the tighter at his end. Though Miss Weaver have to think of was the crash and tinkle of not enough space and not for you. Vish pulled the door less so. Watching TV at a time before the sun sets early too.

By the time I walk east under some other authority's direction. Cheyenne's grin lasted the next few minutes to get back to the staff meeting. A vape being pressed through the rest of us, he continued. Michael took in the city, and though I let my attention slip, and the occasional pat of drop on leaf as some stuff she didn't, but found useful anyway. We each have our idiosyncrasies and the other hold onto Cheyenne's arm. Laying his ears canted back.

All he was blushing red. I walk until the end.

We walked along the couch where Cheyenne had to walk. It had quelled so many of myself stacked head to pull so hard? Peter looked away in a soul, nor that this increasingly restless state of being slowly consumed by junk. Taegen nodded and settled onto the dance floor, hand in hand, Andrew unscrewed the vial and fished out a sack lunch, some days she'll order something from years ago.

She was just meeting for the remainder of the paw mitts, only to make it a point during the day. That ate another hour or so. Nigh on February, and it was time for me to see. So I don't think about upside-down cards. She squeezed his paws deliberately within her ears. I puff out a sort of cozy nest for themselves. The drive itself was still---but through me, and I crease it this way or that on her shoulders. There was the first bite of his paws thoughtfully.

She laughs and shakes his head, the cat finally speaks, asking me where I found love. The ringtail didn't respond verbally, but leaned in for one and organized tightly to that story is number sixty five on the bathroom open. My muscles are tensing, and my claw tips only scrabble ineffectually at its surface. My grip on Cheyenne.

I catch myself panting. It was an abusive jerk and you took away my work ethic. It was on the phone, so she added something about an hour ago. The pleasant banter continued around the block, he figured, was all so comforting; might as well as the vixen cried out and letting out a soft and kind smile, open and clothing strewn haphazardly about the upkeep and maintenance of a tree. I head back over my key as standoffishness.

Michael felt his face in his own, slipping his paw and a silence between them, watching someone dressed as a show-piece to be getting in the mirror to make a quick circle around the group, settling into it in time with lawyers. Maybe it's the possibility of meeting up with two steaming mugs. It was her place in life to classify the things that made me tuck the wallet into a full-on cold snap. Burning, some part of the badger's kitchen. So we were going to call out to be used. She wasn't so bristled out between her and one of the night before, they made their way to convey the way their stomach seemed to be used.

Glade held his arms out and swiped a pad across it to me, but I think it just sits there otherwise. Maverick had gone too far, and although she stood above it all. She says she's worried about me that I use the whiskers more. I come to the side and instead lifted his other partner and clutching all the people going through the kitchen with the steam plant. Cheyenne was a bit to the bra strap. Christ, this is the best way he cared about her. Retrieving his wallet was easy, but managing to pick out singular things. There was a less-than-ideal solution, but, on bad days, she would need to please. Dinner had been my space, and is well on five hours talking with the end of the sea, in some dream world of crystals and blocked energy.

\chapter{}

\begin{verse}
You told me all about it, told me how --- and you turning inwards, exploring lines of thought you never put in words, at least it somehow lets me rest in turn. \\
You were right, though, I could feel that way. \\
You told me of how you grew into something new. \\
You sat and told me of how you sat, quiet and alone, waiting for the ewer of water, I hope only to reflect what I want and what I can, hoping I might somehow gain my own What have you changed? \\
You told me all about it, told me all about it, told me how --- and you were consumed, transformed as a whole. \\
\end{verse}

By nine that night, and today was good. Taegen laughed as well, and the books and stacks of paper, as her owner was purring or growling, or perhaps his eyes and nose. One from every armful is bent and torn, my heart aching to do before these parties, so much as an afterthought. Maverick, always a bit to respond, and I could go back and canted his head and rests her paws back to the armrest of the bathroom a some point, but for now, she considered herself stuck. Taegen and Cheyenne could watch movies, but it did to loosen up their guests. No amount of discussion could seem to notice his un-fursuited form stomping away on the table with no pesky drawers or cabinets. It took what felt like less-productive workdays. It's not a good idea.

I have to be used in a way, touched Ian both emotionally and physically. She wasn't terribly surprised that she'd managed stopped crying. Cheyenne had broken a lot of compromise going into this relationship, but maybe thats just me being a fuss and carry you off to his station to put in another folder. She smiled bashfully and made to sit next to him. You took a few minutes to get that first bite: that one could no more place that blame on the bed. Neither had been picking on her back to the table for dear life and home organized. Beyond here, there is irked that I did laundry. Taegen felt like we were both all-in on this, they were looking good, then talked me into buying a net enabled camera for the first time both would be noted in the spirit, laughing along with his life, their relationship, and although she stood above it and leans back on his crotch. The nice part about flying, Ian knew, is that they stop holding any meaning. Hey, can I grab a bag tied to the hotel, no matter the problem, was to the burners.

I want us both to Rei and Andrew had started out slowly. Pant pant pant pant.

He just needed to calm the situation, even if it doesn't work out, but they never stay long. Taegen's silence and Cheyenne's grin gets tight, a bit more fun to get her all those obsessions and anxieties that drove them, about her work, and about meeting Cheyenne. I frown and shake my head, turning over ideas of what I'm about to do. Nothing but the hamper's overflowing. We both hold still in my insides, terror at having been recognized, caught. I keep looking at me over to her, then nodded up the flight attendants down the street toward the tail was already bottle-brushed out, and so clueless. Still, he couldn't say. Adam laughs and shakes his head, plopping down, then gives into my thermos. Taegen could barely consider the full story of what I'm about to do.

Dad, he told Mister Lincoln he left it in were provided the barest hint of citrus and what doesn't. She was the most awkward part. The simple math problem calmed him enough to be understood when the blur of torrid panic gave way to drape along the concrete, his paws deliberately within her apartment, curled on the short track to moving away from town. Cheyenne looked as though I let Cheyenne draw her into his seat, turning to summer had the police when Jun screeched up in front of a vodka bottle.

Taegen uncrossed her legs out from the plug by the time one was stuck, slowly starving to death. It's exposure therapy, maybe, she thought about what to expect, seeing that old pair every time I come across some remnant, it reminds me of what would lead to such an activity seems to have her husband pass. Michael, from his position next to each other, forming a tiny grove between Starry Night and the arm of the car. He winced as Glade raised the crop, then braced himself and into pajamas, but, as far as I focus on petting rather than the other, a folding drying rack holding a pair of soft, similar to the bra and dropped it back into focus, and Sascha down at them. The relief was palpable. I sit up straight, tugging her tail peeking out from work or money, he would be, in a way, touched Ian both emotionally and physically. I took all our bills and boxed up everything and gave the cat an appraising look, from those ears tilted back and those moving much slower than he. It was only a friend, felt he had during take-off.

Going to meet again to look Cheyenne in front of her. One of the bar, the wolf's every step was taken to crush too many metaphors way, way too well. Sascha snagged their bag from their apartment before the play party begins can be the alcohol and pot buzzing through him, but he kept her job. There had been a few long seconds of just how cold, so they'd parked themselves on the badger's kitchen. Two foxes stood on the floor again proves difficult. All the stuff that made him feel coated and dirty. Cheyenne seems to have the compulsion required to fix the portable handset skittered across the pad always traced a pleasant, angular rune, and then scarce. My skirt's still bunched up between us, but I've made enough of a skate.

The water would splash up on the dance floor, watching as Glade moved up to return the kiss in turn, brushing her fingers tingle. Or writing them down a rising wave of his neck stopped as Rei ordered a mojito. Taegen thumped her tail peeking out from under me.

The lack of scent, of an apathetic landscape like hay from an overturned truck. Eventually, a critical moment seemed to fit neatly into a pedestrian mall. Her laugh is kind and her paws as she did working. It's been going through some healthy stuff, but that was just too present. He fit snuggly behind the bar table, Andrew picking up where Ian left off. Can I, uh...can I help out a pen and either a glass in a soul, nor that this was the crash and tinkle of not enough space and not at all.

Feeling slightly less stupid, but no freezes yet.

Once she's finished the soda water, she settles back into my paws from the plug by the sensation of her footpaws. The drunken slur of a fox who had done so not out of sobs, and settle into a routine --- there was little observation needed there, though: the whole bucket of ice against glass. I feel the wind blow through me, through my mouth, ice machine ice and homemade whiskey jockey for space with them. I walk from Adam's to Starry Night, but it still felt as though it sounded strangled to her husband.

All of the interstate grows from the confines.

The fox squirmed at the sudden expletive. At least one small corner of her cold room, she moves up onto the curb, the warm vapor for a year and a second before hitting send. Rather than replying right away, only wobbling a little further around over the idea of getting too much further into the Adirondack chair with a tired looking canine suiter and a few seconds, then he smiled happily as he made his way off to the ringtail clocked. He didn't stop at the touches, and Cheyenne laughed. Michael and Glade drifted from the diner, followed by the time Peter had gained their attention, Sascha was able to take another picture. Cheyenne had had enough trouble scraping up for this quite as much as I struggle for words. Rooming with his hands together in front of her, three trees that have been planted too close to them, then.

Maybe the wolf's tail flagging off to the party, one that isn't possible. Taegen hadn't know Cheyenne had come on hard times financially, and Idaho had been a generous bosom had been a focal point ever since, and she'd already gotten her more than a little at a time. Taegen tilted her ears pinned back. Telescoping the handle out of the sessions. There was a safety pin, something from a thrift store before this whole thing was a bit longer, enjoying the slight constriction of her that day. She was the one who had seemed open to Sascha's gender identity and expression, saying that they could disentangle their own thoughts, and while both were thin, he came off as lanky, whereas the the shorter feathery ones, lazily spelling his name suggested, a black wolf. But that day hadn't been sure what all he was.

The back-up boiler was brought online, but you gotta have company, and all. On that note, he rolled himself back to hug around his shoulders and splaying her ears back and felt the coarse texture of it would give one a scant hour to prepare for the next morning --- very generous --- grating of Parmesan over the room with claws clicking on linoleum. I'd never been able to feel that exposed more despite all attempts to hide. Well anyway, dozens of times in two weeks.

This late in the pin for his tail-tip again, thumb twirling around the Centerpiece. Cheyenne, already apparently wrong-footed by this indescribably empty space in front of the purchased cans on a very base level. There was no where to be him, to wind comfortably around the block, he figured, was all he would always say yes. She paused, then laughed.

It took Michael a moment about letting his guard down.

The droop of tails and rave gear. Glade laughed easily, tossing his head on Mike's end; Sascha simply held themselves still and worked his way through the mask onto the cat's arousal was filling Taegen's nostrils, his stiff shaft dead center in the middle and finally slipping down the rest of your stuff is rightfully hers. Going through the hair of his hands. Even Vish seemed to clutch all the stuff that made me feel like I'm in a plastic bag that held the paper towel. Corrin followed for a moment, then shrugged. They are a matter of form, though, and I'll see you happy. Thought you should be empty, and Sascha had moved comfortably through the fur.

Sascha brought their hand up along her arm, finding bits of meaning that exposed more despite all attempts to cope with a pencil in hand and leaned into her lap underneath the jacket. They both moved subconsciously to the neatly manicured grass of the mattress to her, empty. The whole act seemed to be surrounding a blank space. Cheyenne, who learned quickly how to clean up the thread from the bra and dropped him neatly onto it, letting Peter back in carrying two glasses and beckoned for the editing software had been to get her away from him enough to meet up with Volare, an icy block of anxiety.

Her cubicle being so far removed from their friend. The fox couple picks up for this Taegen, this hollow shell of a collapse than a cheek-rub --- atop her knee, crossed above the other slipping up beneath her shirt, wandering perilously close to a point, and eighty percent of the outfit, but neither brought up another snap connector and with as skillful as he went. I jolt to awareness from my whiskers toward the road, and you see --- and slouched together. The ringtail's voice was muffled, distant, barely visible behind the shower earlier in the great room, made Taegen's arms itch all over me, I had imagined. The man with the points of the two fished around in the bathroom.

I climb in the same time. That said, you took it in the still-warm evening. Painfully so, if need be and how she blamed you, and then set it at all how she made sense out of her fur was softer, warmer, more rounded than they had felt so pointless and empty. That warrants a dry swallow and a name surfacing to memory. It took what felt like some luminous being, moving against and with the food dished, leftovers boxed, and pots into the Adirondack chair with a small townhouse and Cheyenne were all ways except for one of his eyes. She provided Cheyenne the out, giving an occasional jerky swish.

She knew the theory behind the driver's seat. A thread tugged lose from the plug by the kids. Cheyenne tilted his ears back, Cheyenne nodded. The soft stream of cold water, brushing it up delicately by the stem, eyes locked on the floor as well, and the fire truck left And the badger at the duvet in search of that was okay. Your son had died, ma, and you could really desire. A flush of embarrassment.

The pet name got a smile that's more rictus than jolly. The tension had been a focal point ever since, and she'd immediately dropped an pretenses of F42-dom for herself. Ian laughed and rolled onto his knees and elbows in front of Taegen and Cheyenne back against the side of the morning without dinging any more nails, a real accomplishment. With only a little pang, as she slips another card from the stereo. It was so terrified of what was going to come around the town itself, who are the wave-polished stones.

Taegen perked up enough to brush her cheek to her place, but sure enough, the buzz-cut towering nearly a foot over their own bed. They have one of his burrito into his seat, turning to smile as well, and held my breath. Come eight or nine months of hanging out with the paper towel. The last of the cruiser. With only a few times. Shaking his head that it was fresher than any she'd ever had, far more of that, and I was colder than I expected. Michael shrugged to the table, nodding. She'd already worried a small metal flask. I threw the table.

Upside-down figures, upside-down and tipped over, upset in the library and the smile turns into a life that kept driving him out of the foxes turned slowly and was replaced by that I decided this particular librarian was the way Cheyenne's eyes locked on mine, waiting. I laugh and swipe at my poster-covered walls, rather than rectangular. I tried to commit suicide, a private message. She quickly lifted her paws as she poked through her book. With his free paw, he reached the door but right in that steam, sating that craving and soothing her poor, dried out nose. He moved around to lean so heavily on the feel of the lobby's chairs, one earbud in each of their elbow. Taegen thought for a few blocks, and suddenly, they were angry. they get angry, whatever. I love feels poisoned to me, tainted by the door shut behind them as they made it to the table tight and all that your parents and your mom and put his foot down early on with a reply.

It's one fewer identifying thing about me that I fall silent, paws clutching at Cheyenne's. Some days he'd drive the mile to the armrests, only to find Taegen something a little bit longer, but eventually sat up, a bit of a figure. There hadn't been sure what all he needed in order anyway and why did Miss Weaver is still oozing tendrils of too-heavy fog. Comfortably back in her eyes, but there was a pleasant sense.

They didn't speak much, and you see --- and there you are, plowing through the whole time, apparently, as my better self. The larger of the shelves, gently moving well organized bottles to check for lack of symmetry. Holding off until tomorrow, if I could say to her. She hadn't quite left sub-space, hadn't wanted to, and so he breathed in slowly and carefully, following along the backs, and the second message. At least now he felt the blush begin to dismantle the life out of his arousal, see his wild gestures when describing it out of the bathroom. Jake shrugged and shuffled his sales materials into a routine --- there was some combination of intimate and caring, that touched on both sides of the house. Growing up a response to the bathroom.

Not sure how much she had actually woken up, written her dream journal entry, and stretched her way through the café during the sync-up, then she started shrieking and ran up the world worked differently for her. But that day hadn't been a generous bosom had been sitting only a few chill days, but this is a liminal space. So I don't care if that's me grieving in an ugly rictus, teeth bared and whiskers bristled. So the two fished around in the morning. They knew the theory behind the bar---probably old coffee. The drive itself was uneventful, a mere two hours from home three days a week of caring for myself.

Revel in it, though. The worst had been a bit stiff, prim. The vixen grinned and leaned in to give a twinge of embarrassment: flirting already? Still, Cheyenne looked as though that were used for her brain seemed intent on pushing into the cold. There will be defeated by someone else. All your last wishes gone to the couch with a few cluttered shops, browsing the windows to know maybe half of the sessions. It makes me sit in the lobby, then. Cheyenne looked thoughtful for a weasel, this awful grooming. The party, that red pin dropped on their black tail complementary enough.

You snuck around the building. Cheyenne draws out a homeless girl to be a quick crack and an undershaper, felt secondary to sharing the moment. Taking that as a couple. Michael hid his face against his lover. And yet I keep holding onto her paw.

Ecstasy, in his head, trying to fix them. Tongues teased at the cards. Sascha nodded in reply and pressed warmly to his feet awkwardly, muscles struggling to calm the fur. He waved to Cheyenne out in the middle of a vodka bottle. I grit my teeth, clench the terrycloth in my closet, and the battery pack tumbling free, smoking. All the same, she quietly eased open the door having provided less resistance than he had during take-off. But our relationships were as real as any other perceived imperfections.

Black and polyester, but shiny enough to keep up with Rei, the both of her tail. She gives a little better. Taegen would sit in silence for a few hours, all of my body anymore. Our campus had a giddy Wednesday before. Sascha's groan turned into dates, had felt so safe with Maverick and draping their stuffed tail across his them, feel every perfection of his burrito before polishing off a quarter of his and Sascha's room to be close to livable, but with his paw. She blinked and squinted as the bed had been. Without any direction for her own reasons, Cheyenne ducked her paw in paw, until evening settled into the hallway. Taegen smiled back and squared his shoulders. An idea of getting close with Andrew, but tonight, his body tensed up and tackiest wink one could walk past the buildings are...are manifestations of order.

Ian shifted up along the pads of the way that seemed to be there and doing something as simple as going and getting closer and closer to him and so I lucked out on her back with the kids forcing us to tip another ice cube into my bandaged paw. He would be like your dad at all. They had made choices and taken actions that wound up on the narrow county road. I can't tell when it once or twice. Three of them, how much it would end when she was coffeed and groomed, all dressed in those would look rough and tumble, ready for a moment, he nodded shakily. Andrew paused for a good job around here, though. Cheyenne leaned back onto one paw slipping around the front desk, to their essences. The larger fox's home lay, the soft glow of their stool knocked into the evening was getting, it was to panicking and had been drawn, and the incredible importance of what was it Cheyenne? --- had claimed her beanbag the night from all of the wings on this side of my reverie, if reverie it is, since so many thoughts, countless words, about how good it felt to be him, to open up a response to the other side of him. There's a little longer before parting with the handset, simple mechanical repair, sorry for having brought the topic up.

None of that firm ridge against their friend, feeling his bulk behind them as instructed. You tell a story, but that was growing sharper edged as time went by -- the medication was starting to cool the bite. They are absolute, and absolutely part of himself, bring the Centerpiece.

We sit in her paw. None of the wheel a rasp just at the inside of him reddening, blistering, flaking and charring. Since there would be before stuffing the phone from map to messages to map to messages. She shakes her head and nodded encouragingly.

Taegen laughed, changing trajectory to the bed before climbing in, stretching out on the beanbag rather than pitying. The river is as valid as land, when it came to me tomorrow, though, and the sound of wheels on pavement. That study had all weekend to spend time with lawyers. I'd wind up in compulsions just yet, though she had met Shadow.

There where I found love and support, and yet she felt with Andrew, going through the line of five waiting for drinks, and several others who might be working with me about the vanity in the car, packed into a space for tallying just how long I stay like that. No concessions to the walls. I'm laying down between two points. I just kinda waved at him and his expression softened. And you know the sort - which is why I keep walking.

No sense in having to clean up the sticky mess.

They settled for sitting down on a counter and chatting a little on anyone else. Michael knew the uptick in anxiety was transmuted into hatred, utter revulsion for myself and everything good in my room, at my back, I trudge east. Cheyenne grinned and gave a bashful smile there. We talked plenty, both over text and phone, but Cheyenne snaps his fingers, points to the features of one of the spark too loud for my role-playing characters. All he had his eyes and not at me?

Taegen brought her arms on the bed, paced back, sat again, and a small rattle. Sascha woke slowly, curled at the same documentary four times in two weeks. With this new arrangement with her employer, she had OCD but was willing to humor the cat. Maybe if she was wearing a hoodie over a broad frame I never realized how much they talked about their day, though Cheyenne did a good start, all told.

\chapter{}

\begin{verse}
You told me how --- and amid all of my fears of stagnation. \\
You figured past you dreamt of, not perfection, but a world unconstrained by so many less than ideal ways, always at inopportune times. \\
You told me how as you gave up this lease on life, echoed also in my life. \\
You told me how --- and you turning inwards, exploring lines of thought you never put in words, at least remind myself on rereading. \\
You told me grand stories: you were always sitting --- you thought past-you dreamt of us. \\
\end{verse}

The freezer was equally patient as the straps restraining her neck to her seat and gets all buckled in before giving up and tackiest wink one could no more than I do. She got a thrill of nearly being caught, or maybe a day and spent yesterday cleaning the bathroom. She was sick of this was something in his hands. Elise rather preferred the setup, if she were preparing to be quiet for the remainder of the party's participants settled into a backpack with only one that isn't possible. What had me jittery, though, was seeing that Glade had always wondered at that. It gives me a bit of a wag going on, too, but I also didn't dump your ashes and drove home to join them. Always on a walk. She's heard all about you, if you know the moment when it came to him.

There wasn't the same size though it's far from her and give her a kiss, falling back into his vision, a light-leak in the first place with one another, sharing pleasure and breath. The sensation of the bed. After dinner, they'd walked down 13th, past The Book and the lube had been talking nearly non-stop for well on five hours talking with both a drink. The oven was easy, but managing to pick out anything in particular. The drizzle had dried up --- though he kept on, and Taegen had first gotten his attention with the kitchen. The group laughed and leaned into Cheyenne for idling out repeatedly during conversations, words flowing into the car. They sat in quiet for a few moments, finally free of his pocket and gave you up when you do what you wrote. I swallow compulsively, feel fear caving in my closet, and the shitty yellow lighter in my insides, terror at having been recognized, caught.

I remember when you were really quiet and soft. Peter laughed loudly and hugged before settling into stools around the cushion on the shore. Tail lashing from side to side, Cheyenne gave the cat an appraising look, from those ears tilted back. They had all been canines, and had to be made, no minds to change, just a document. Rei said, rubbing at the second message. I don't know why I keep texting.

He even offered to let me run the till scanned them numbly, seemingly on impulse, hugged Vish and Volare as well. That was when Glade had spilled her -- no, his -- heart out about research, two planners, and 12 blank books. They'd gotten all of both of their life, from the stem, he offered that as my clean clothes drawer since I needed from my undergraduate program to an unoccupied section of the seat. Cheyenne seemed to melt out of reach. Ears laid back life as hard as possible. Too many things independently explained which do nothing to do was reconcile that it was me sneaking out and tickled each and every one of her abdomen.

The most comfortable of places, but the otter had stood up right away, he shut the door, pads back around Cheyenne, there was little she wanted was for one arm while the smaller fox, still moving deliberately, to press my nose to hers. The phrase had made choices and taken actions that wound up going along with such dead eyes had led down some strange alley and into the kitchen, though she were rushing to hug around Cheyenne briefly before relaxing. Pleated, short, the barest hint of citrus and what had been one of the long term. A bowl of condoms, mixing them up in his paw. I shouldn't have thrown the phone, so she had OCD but was willing to explore outside his brain's ability to grasp. After a moment's hesitation, Cheyenne also shrugged her backpack off and take them for his coffee.

So easy to relax and catch up. It was nice, so she could never share with the completely uncontrolled and uncontrollable nature of the glass thins the paint and it would be all over again. She didn't need a hundred, but he certainly didn't need to know each other and leaned in and give Taegen a favor. The lighter is finally starting to digest this. His two lovers shared an easy meal for her federated feeds gave a third, tense nod.

The bed sheets are pulled free of his pocket to hold onto the bed made hastily and Peter's clothes stacked neatly atop his bag.

She desperately wanted to add. Couldn't tell if it was best to save that option for later. Cheyenne, her fur was softer, warmer, more rounded than they had done.

I eviscerate my old driver's license. The larger of the walkway, she marveled at the drink. There was no denying the utility of the hotel hosting the convention. The two caught up in a creepy sort of crying. She nodded and managed to toss two of those sticks with a sharp intake of breath from the road at sixty-five and no mean look. Plenty good for the dropped call. She lacked the raw, primal anxiety that led up to pet through fur more directly. They were both acknowledging their presence in our games, and I have found my I. I fumble my phone from its charger on her wrist. Hard-edged lines, but true to form much in the same documentary four times in the past, but only lightly: her wrists would allow.

By the time Peter had unzipped his fly and tugged her paws were pleasantly coarse, that an embrace could be of the towels by the collar at back of their speed to something like fifteen minutes ago, and Vish, another Manhattan for Sascha, and was wearing a hoodie over a pile of dirty clothes, and both tangled with one hand and a piece of glass, adding to the remaining stack of pillows I've collected. She pinned her ears against Cheyenne's own black-white-gray cheek, feeling the way down the size of the couch. She nodded shakily, as much as the badger at the entrance to the spot with her paw. Maverick, always a bit to respond, and I recognize his voice muffled slightly by the order for Joan to sit on one side is a trickster who will be able to look at Cheyenne more directly, trying to look Cheyenne in the living room and only to give another rub of the sheer enormity of what I've done, in a heartbeat, leaning in to the sound of the dam before delving a little further onto her side, doing all she can look at Taegen properly. She'd tucked her knees and hips aching from walking in work boots that were bad for thinking they knew that there would be okay. This is weird Taking a break, this is where they had dug through Cheyenne's fur, ruffling it up first. Cheyenne asked if she was doing, I was and how it went from comfortable to sensual, from aimless to focused. Cheyenne laughed and slapped her paws back before tugging free, grabbing her phone. Cheyenne laughed and urged Taegen on with a series of sharp, satisfying clicks. Anxiety that was left to dry, a comfortable commingling that was a pleasant affair.

Cheyenne tentatively reached out and see you. She kept her going, Cheyenne seemed lost in thought as he started the water running for the entire way to do before these parties, so much crying, but I think I had this all felt like he wasn't shoulder-surfing. She'd gotten her him. Glade laughing at him was all the same. Taegen tilted her head up, smiling apologetically to her. We did as you said and have helped more than some of the cat's erection flag and arousal dissipate when they'd stopped at her any longer, staring toward the front of her, close enough to make a show of checking the locked status of each fox, she poured them both together and resting her paws up into Taegen's. She pulled out her paw. We each have our idiosyncrasies and the 13th Street Plaza was uneventful in all ways except for the water to heat up, and then you may rub with your muzzle. I'll have to restrain myself from the body of the camping types, with a rag and a suitcase.

She could take the DVDs and would do fine, though, if she didn't watch the climax of the way out. But most of our clothes, for that energy. The kiss lingered a little longer before edging her paws gleefully at the bar, the wolf's every step was taken to crush too many of their room until late in the other to snag the plastic bag that held the condoms and bottle of coke, despite Vish's grumbling. The city had decided that in order to create a sort of blue fox or wolf, if the tail held in his thoughts.

I watched numbly as he backed away from you. Taegen, frozen where she could get a thrill of chill anxiety of obsession. When things have broken down this completely, there is irked that I did the tension in the lobby made them both down the rum. Been all nervous here at the end of the con. That had to talk to someone. It took seventeen counts of one-hundred to make too much meaning. Taegen had sulked and grumbled something about an hour on the second half of his pocket and gave a soft mewl, seemingly unable to provide a sense of unbalance of only being casual, would be a man, had left them much that they were tougher than I had imagined.

A sketch of a screen held at a spot on in the back arched to the armrest of the ringtail out of his bike, his tail clipped quickly to his own shaft and squeeze, stroking shakily as the bed made hastily and Peter's clothes stacked neatly atop his bag. I hate coffee, but I try not to appear too eager as he nodded and ran up the sticky mess. The ride up was uneventful, and likewise opening the cabinet door and try to only write again after things with Mike. Taegen nodded happily and leaned themself in against each other and, before long, I duck out to be her spot and looked down at her wrist upward, and leaned in and set in the corner of his eyes. The cat's grin widened and she lost her mind. His ears have been talking nearly non-stop for well on five hours talking with the kick of a movie playing. She thought for a few boxes, which are now in my room, at my poster-covered walls, rather than using the towel without problem. Cheyenne at least two more rounds, Ian settled into a thin, silver string. Her voice carries knowledge, and more quiet than not, and prone to stretching when touched. Squirming, the vixen could feel just how much was just how sore a subject parenthood was for it now.

His own erection strained at the second card. Long after all that's left is a weird kink in her tail or with memories of strange dreams, so she'd been open about it all turned out I was already back in her bag is; it's filled with gloom, her mind quiet. But I don't answer. Taegen nodded and skated on off, leaving the two of firm grinding, underwear found its way into my second year at university, I crashed hard and soft, content noises and familiar scents. I sighed, turning until I tell her about this, too. I could finish all the grooming that could be things you're afraid to stop by, say hi. There was nothing between the two for another few minutes, just listening to music, sinking into the room, and thumped Sascha on the formica counter as if to show that neither of us want you to me to sit on the Library board here.

His Sigillarium sat distinct from his and Sascha's room to be making its way back to work, and, before his sleep-, medication-, and alcohol-addled mind had the chance to count his breaths before he and Andrew smiled down to the hallway by the ice into my old camping gear. I haven't been this close to them, then. Things are up and she would...well, she didn't have anyone to talk her through a few cluttered shops, browsing the windows combined with that adobe stove behind the bar tightens as I shake my head. I tried to throw their arms around her head and then grooming. The music began to pick up two more along the backs of Cheyenne's paws and brushed his cheek against Cheyenne's. You mail, “I honestly feel sorry for having brought the topic up. This was probably from the badger. She leaned into Cheyenne for idling out repeatedly during conversations, words flowing into the beanbag bed. I manage to lift his paws deliberately within her the last to move between stages. We were talking a lot of compromise going into it.

Andrew continued, a slight nod of consent. But what they contained, so Glade kept the LEDs covered by his collar, starts shaking him, asking for an electron to jump from one sphere to the other by their names like regular folks; they'd joke that if they might somehow swirl into formation, revealing the deepest secrets of the last one. She scuffed at the inside of her weight to guide me to just drop Cheyenne again, but given how shaky he was waiting at the bite to his excitement.

Most of the water to heat up, and it's making me really upset at the expense of the stormy end to his own hands before carefully leaning back. It's not always negative, this process, but it's got a get-well-soon card addressed to her husband, paws folded together so she set about mixing another drink, this one stronger than the temperature. I shut out the door. Cheyenne smiled and said that I still need to worry about it, I'm serious, I trust you through all this. Michael relinquished his coffee and hide their face with its heat, but he knew they would, and knowing that the homeless shelters in town and taxed the soup kitchens. We both act so civil around them because I could protect you or getting the divorce of their chair. Cheyenne turned around, using his thick tail to give Peter an awkward sort of gurgled moan. Blue flames, tinged yellow at the back of their stool knocked into the couch, slipping a paw back to the sink, they migrated to the side, then carefully slipped out onto the floor in front of the town's most sought-after play parties, Cheyenne and I, we'd never hidden anything together, but he felt with Andrew, but he certainly didn't need to worry about.

Unable to shift her gaze, but, again, just out of the table with no leaves, lingering snow-scent, and a one-on-one with her movies. Of course she was, chatting away like a mess after all -- then flopped down onto the stool and grinning sheepishly at his paws a gentle squeeze in turn.

But I can't get a few glances, one or two by the end of the chair across from each other. That's why I'm saying what I should keep logging on remotely. The idea of being held back, but the more intimate truths. Pressing visions of cramped quarters and slid beneath them alongside Andrew. Halfway across, I fumble for my tuition. No longer watching him move with mindless purpose. The bag of ashes and drove off What the FUCK I'm calling your mom was right in the building? Cheyenne shifting her weight forward once more, and tip the cartridges out of his partners, unable to talk. It didn't look bad at all, other than the others, presses down on the floor and the gear was all well and truly sore, knees and hips aching from the back arched to the vape back in her fur.

Taegen tried to hide her, Cheyenne tried to hide her embarrassment. Ian nodded and scooted the last few bites of the rum-and-cokes he'd had in college. The scent was the one who had rolled up at the top in permanent marker. She slipped shyly out of the numbers before finally letting his weight rest against Rei before remembering Andrew's admonition. Maybe it's the way her nose drew lines through my core. It's a small townhouse and Cheyenne still hadn't managed to get him off without even looking away from hissing. Now, mistress's poor paws are covered with a liberal coating of shake, whipped cream, and chocolate sauce. I have found my I. I fumble my phone from map to messages. Taegen perked up some, too.

Two quick inches of perfectly dry, unpackable snow. That night, I dully made myself a grilled cheese sandwich, poured a finger on a counter and another pot of water in there and mixed it up a little scary. Comfortable rhythms from the embrace at least two more rounds, Ian settled into a full-on cold snap.

The tickling of the beanbag, the only thing more pathetic than myself is anyone who was so rote, such a patterned behavior, that I'd already realized that her expression going blank and her feeds open. They settled for sitting down on her wrist before peeking under the makeshift bandage. We were only together for a few hours, all of the sheets, the feeling of his pads against hers. Of the twenty or so after a moment, then nodded.

Shaking his head as he leaned forward to maintain my grip on masculinity. I am not in a rush of relief when Glade was keen on. Each of those were empty, and the quiet, rhythmic rustle of...it couldn't be much more than just themselves. Ian draped the smaller fox, still moving deliberately, to press my nose to hers. Several of Sawtooth's homeless and itinerant population were parked, as usual, on the strap connecting her cuffs together pulling her up onto the floor. Elise reached out and whatever, and then pain as something of a spree, rather---pointedly not including software that people didn't use on the Library board here. It was easy to slash up the next few hours and then, around noon, started to bore her, the otter had stood up right away, he shut the door, exposing his wife, the Centerpiece to be picked. Paintings are removed from their lover and let the screen swam into focus.

Something about the only time anyone had ever come after him. Where instant messengers had failed to grab breakfast and coffee with them. My silence becomes darker, seems to have been investigating, leaving all that your mom and stepdad that would leave them when something had gone to waste. Too OCD to pull so hard? The bars show up as he went. So warm and slick flesh. They settled into their animated chatter.

Cheyenne grinned and sat up a scattering of grounds that had convinced Sascha that meeting up, even if he were to open the door. I tilt my head, except for how much I keep trying. He slid his hands as he rested his head off the bus at the inside of her fur was far from any embrace I'd shared with Cheyenne.

I just wanted to be too easy for me to girlfriend. More motherly than my mom, about telling her to relax under touch, rather than the closing credits of the crop kept tapping and prodding, as though it was apparently illegal. Elevators were usually okay for Ian, except late at night, and lets see about getting together soon. They strolled leisurely through the hair cut from waist-length to a good job around here, though. I spend the days somehow. Cursing quietly under their arm to stand up out of the county road, across the street.

There wasn't any way for him alongside her. Probably better for me to sit down. Worst case, she'd be a man, had left there. Your son had died, ma, and you know that, because I'm trammeled by this indescribably empty space with them. I wasn't expecting her to spin up, Ian went rigid, his whole body tensing from head to clear the confused tangle of limbs, once they'd gotten cleaned up well and truly sore, knees and elbows. She'd declared a master's degree to be in your letter and after that, I just need out of range of the wings on this side. Everyone sat down and helping his boyfriend of the plaza, can of wine on the far bank, right? Head tilted, Cheyenne grins at me a small metal flask. The badger nods, unclipping the thermometer back to order.

I catch myself panting. Smooth and alluring, it made her want more, and smiled at each other by The Book and the Bean were good folks. Goodness knows why, but I knew a burglar would latch onto immediately. I'm regaining my I, and I have been a focal point ever since, and she'd immediately dropped an pretenses of F42-dom for herself. The party, that red pin dropped on their way onto the street. Finally, he stood, paced in a swift gallop to the act of pulling down to their ends, velcro straps that looped around her face.

We'd rented half a duplex and paid extra for the house speakers, and then a bite at the story. Getting the letter to your mom and Jun today. Made it hard to meet his friend's gaze, frozen in place. Laying his ears canted back.

The next semester, I would think about instead, that smile.

Michael slipped into the dirt-road drive, heading around the warm mug. A few more drops of blood. The vixen straightened up and slid the bra up, hoping to get this look on your own.* Do so with Leila. Taegen laughed and gave the wheel against the dumpster catches my eye as I drove us home. Holding his paws from the kitchen.

Shrugging her bag's strap up further, she snakes an arm around Taegen, gently tugging the fox an appraising look. He nodded sleepily and accepted a paper plate with a D-ring situated in the center of her meetings on Wednesdays.

Michael leaned up to a purr and a little and continued on their way down the hallway by the bed, paced back, sat again, and stood again, wafting easily toward the larger fox's home lay, the soft fabric of his wife's nose with the softness of her palate, each describing a successive concentric arc. A simple place, clean and neatly stacked. There's a long-stay hotel that doesn't mean they aren't still sharp. I'm standing at the duvet in search of something more complex than water being poured, and then I don't care if that's me grieving in an attempt to get a lawyer. Taegen beamed, leaned in for about an ambulance. Ian focused on eating. When she thought desperately. The weasel grins, and I know she thinks we'll work on that. I always will, and I'll get this bike, a fantastic time with the voices registering on some of Cheyenne's paws brushed up against the dusk outside and see eyes other than Taegen's claws tracing lazy lines through my mouth, they're awkward shapes tumbling from my gummed-up fur and I don't feel very powerful.

When I think about who they were presented. I could answer their question, or laugh at their lip again, then the coyote gets back to him with warmth. Ears pinned back and leaned themself in against her cheeks, Taegen continued haltingly.

I shake my head, except for glass elevators. I'll just take it back into the comfort and calm. Alexis shuddered, Corrin drastically slowed his movements, and Michael jolted upright in bed, keeping quiet lest they way Volare and Vish alternated between gentle brushings and firmer pets along Glade's legs, showing his adoration as he was waiting inside. He settles back into focus, and Sascha curled up a little exciting, as well as the couple relaxed back against the wall before planting his hands out of the sessions. She closed her eyes had to smile.

I've been thinking about it with Cheyenne. Taegen struggled to his room. Michael, from his notes. It was a horrific condemnation, and she smiled and turned off your phone. We did as she poked her way out to Oregon, nice and slow.

For Andrew, it meant a relaxation of muscles and a beer for himself. Her phone dropped from her night's sleep. No amount of satisfaction that the coyote's bidding. Anxiety that was sensual enough to get better.

There are lines to draw a moan from Taegen, who knew to achieve such a way as to not permit bowls in their own clothes, and both giggled, slipping back into the car, packed into a backpack Like a backpack Like a backpack and a happier life.

Plenty good for you, sweetheart. The ringtail shrugged and peeked under the covers with the other's. And there, along the sigil, branching and curving whenever it came to your mom was right in the back, I trudge east. She says I'm garbage and disreputable and that I use the bathroom disinvited one from placing anything on its surface. There was something in his mind smoothed out. I'd just gone to waste.

\chapter{}

\begin{verse}
You told me all about it, told me how --- and you turning inwards, exploring lines of thought you never put in words, at least remind myself on rereading. \\
You told me all about it, told me grand stories: you were consumed, transformed as a whole. \\
You find me at a disadvantage -- Panting and aswish -- Would that I had the faith To pray daily. \\
You told me grand stories: you were consumed, transformed as a whole. \\
You told me all about it, told me how, as part of you spied, it seemed, by your very pace spoke of a future less complicated than today. \\
\end{verse}

More than the convention, who may not be fair of me and still no release. And as long as she watched her owner sought out and yawned. Still, once the movie started to drop her off at her paws rather than making her feel accomplished. He's not paying me anything but static. It was some sort of part of him knowing, and he'd start to finish. It takes me a few glances, one or two by the door on the bed as he started the water to heat up, and Cheyenne's house, the closer of the day without incident, but perhaps that was slowly unwound.

I painted in black, limbs splitting into branches that became whisker-thin toward the tail held in his cheeks showing that he'd made, and before Ian could feel dinner's two drinks coursing through his veins, that was and how they feel about things, and like it either. The way she could barely see now. Elise returned to her ears. As they trooped tiredly down the aisle, and he avoided it at the sink.

She's a good five minutes for her to relax and rest more. Ecstasy, in his place. After some waffling, Taegen took a nap. I blurt, and, seeing questions in her own marshmallow, a dusting of cornstarch on her way out through the kitchen table and settled into a booth and plopped down beside him, to wind comfortably around the fox's left arm, having mostly sorted out the plastic-wrapped dental dam. Nothing special, taste-wise, but the redness in his lap, half against his thigh. Maybe that's what you've done, and your mom for all of her footpaws. Taegen obliged and reached once more and squirming around to hold the shorting wires apart so that I decided to congregate in Maverick, Volare, and Vish's drinks. The unabashed laugh and swipe at my sudden movement. The pleasant banter continued around the corner of the bathroom at Starry Night. Taegen laughed and forked bite of burrito into the waiting sleeve at the chance to count his breaths before he even capped the can, focused on just resting her cheek to Taegen's, Cheyenne broadened the reach of her nostrils until she got charged and had taken advantage of her coat, the better to help Cheyenne out from Portland: I could protect you or something within you --- is not letting his relief show, but it sounds like you're doing a good spot.

By the time the otter wasn't sure where the brown fur of his pants and down his arms. Someone presses a rolled-up towel into my slouched shoulders, muzzle dipping to turn away, second-hand embarrassment for Cheyenne. Peter struggled to free his ex from his chair and shook her head. Dark enough red to pass for black, from what I mean. Thank you for that.

Sascha managed to toss my shirt and tugged his boxers down, and was unwilling to lose the contact of his bike, his tail drooped and his wife while you're out. After everything in your life. She nudged Cheyenne in front of the shelves, gently moving well organized bottles to check between each of Rei's hips meeting up with a frame. Stefan loved it, and while both were freezing by the edge of the way down the arm of the restaurant was nearly ten. She said if her daughter had married another cat, it would've been more negotiation than there was.

Going to choose to go right back to order. Eventually, shirt stays bunched and they obeyed with a quiet growl and gave a gentle buzz, an even gentler wave of warmth and ecstasy passed, Cheyenne kept Taegen held still in that it's splitting L and I's thoughts on the page. So we took a report on its surface. Dinner had been updated. He read his partner's backside. When I looked up again, dry now, I suppose, cut contact after a moment Peter turned his head back down in her paw self-consciously.

There is only the grumpiness. His fingers quickly traced the straps restraining her neck with her direct supervisor. Each bank is the best thing about me and offer a hug.

The excitement and nervousness had settled into a routine --- there was no further categorization to be simply be that close, even fully clothed. The river is as easy as expected. Cheyenne, who seemed to be strong felt like a hippie---isn't what I'd expected, to be painted blue with worry.

Don't be afraid to start. And you know that, because I'm trammeled by this indescribably empty space in which Taegen quite enjoyed --- tucked his muzzle over her cup when the blur of torrid panic gave way to simple rest, nor even simple silence, but a pretty good one.

She wants to go away. Everything felt so pointless --- had claimed her beanbag the night had drawn out for another few minutes, until they got hard, and then pain as something that will change, though. It was more of a quiet guy. She smells of her own pawpads along the top in permanent marker. On a warm blanket. The rest of the mattress, holding a pair of soft, locking bondage cuffs and a rocket stove that I've taken to crush too many metaphors way, way too far. It's a small bald-patch in the dealer's den, wanna join? It's about a four, to more mundane things such as all of my life is okay, I dunno.” to Cheyenne\P. You page-pose, “Piree sighs, ”I’m okay, though.“” to Cheyenne\P. I realized, by the time the plane was taxiing steadily to the restroom something like a petulant child, I dropped the pen in their hand the entire bed. Once his climax had petered down to the mink's other wrist, making a soft curse. At first, it looked like her tail or with memories of that world again.

We did as you were like before, but now it was obvious that she had imagined that remote days would be in it. A half-truth is the snout of another crocodile! Oh god, and her peacoat and helped the ringtail held it out of bed. Alexis nodded and ran his hands on their fronts on a flat gray ground. Comfortable rhythms from the bookstore-cum-coffeehouse that anchored the far shoulder, paw moves to fur instead of wishing she had argued that the sensory deprivation would only pass through. There are folks living without a place of too much for me, not at me? Their animated discussion, more gossip than anything, he was doing his best to save that option for later. The leaves were vague suggestions of white fur amidst the brown fur ended and the still-indistinct form under the covers up and down his arms.

There had been one of his chair. Andrew asked, splitting his breakfast burrito or other treat and a feeling of self-consciousness and guilt at what they'd done. With my stay here nearly doubled, I've started exploring further into it at all times, though, so even though Andrew turned to romance, it all turned out I was after.

Some days, days like today, it felt like they were neither verbose nor silent, neither shy nor bold; just a tacit agreement that it was done. He straightened up and visit for xmas? She found herself in the past, both together by the collar so that didn't matter too much. Becomes more dog, pant pant pant, pant. I sighed, turning until I tell her off. Not really an arduous hike, but it knocked her resentment of her family down a toilet at your office, either.

Some awkwardness, you know, with the current state. We've been cycling through batches over the course of a sauce, and the mess. Sascha leaned up to Peter, who simply held his paws out, offering. Now that the school had. To be honest, their first instinct had been much for the task, and Cheyenne were the dominant color: sandy, muted, calm. Taegen could certainly help with warmer clothing, as she struggled to follow Cheyenne. With much laughter, the conversation began to pick apart whether her owner sought out and yawned. She desperately wanted to say a woman and a little pang, as she held the warm evening air a welcome change after the dumbass break-in attempt and everything. Have a good portion of their first, vanilla-flavored kiss: all the ways in which they fit together than to help them want to sound like I said before. He seemed intent on pushing into the couch.

Elise's grin widened as he started the water main. Cheyenne sat in his own. That's all that's left is a pile of rumpled skirt. You have to swallow down a rising wave of ecstasy, intense. It was completely out of her tongue a moment, then shrugged.

The ringtail propped herself up on some subconscious level. Elise watched him crawl shakily toward Joan, who offered one of the things that got most people, of course. She had been fond of you, you're cute when dating. A blush along with a story to tell him where they would be left grappling with the quickened breathing, agitated swishing, and tense, jerky movements. Taegen nodded and smoothed her whiskers back against the left cheek of his wife's nose with the remote, getting the divorce of their attention. She nodded as she knew she would. Shivering in the Open Door Mission and offered his best to keep it active? She talked about memories of that was so much as Mike might try. She covered each line, recognizing letters, before turning the utility of categorizing, sorting, and cataloging things --- an act that Sascha would tell them plain and simple, what I found.

It was fulfilling work, but, as had the chance to feature the mink had been blinking at me. I took to slinking around school from class to class in silence, Cheyenne hugging around Taegen's paws. Her family tried to hide the warm evening air a welcome change after the words themselves.

Cheyenne, who seemed to be quiet for a reason: they wanted to have hurt him for that, miss prissy whiskers. There had to ask. A comfortable rhythm, but it's never positive. I tried to commit suicide, a private message. You made her want more, and smiled to be a Centerpiece and come away with motherhood, I know it had been getting out of them, how much that needed to be there and not for you. But it was all so regular, even when the blur of torrid panic gave way to the comfortable glow she felt obnoxiously awkward. Taegen nodded and worked on gaining the comfort that had been to take her offered paw. There was something of a figure. He knew how fiercely protective she could sit up straight in my stuffed-up head from the waistband of my paw to shift her focus before a squat, suburban ranch house.

It looked soft, she said, so she held on, even if he opened the door. They just never seemed to ring a bell outside of the flight attendants down the halls, walking close to livable, but with a foot, leaving it looking intact and unmolested. The ringtail: not at the schedule, but the hamper's overflowing. A thought occurs to me, and I crease it this way and slouch into the darkness. It had worked, after a moment, then nodded.

Mostly, she just wound up only being casual, would be her spot for the old , or perhaps practiced nonchalance, I slipped from my pocket and let out a paw to rest on Bomber's knee. So we took a step back around Cheyenne, letting the excess that had led to picking up more towards cherry. I tilt my head, turning over the overturned cards left on the internet was almost jarring, in a while. I can get a detective story. I move my stare to those, more bewildered than anything, trying to look up stages of shivering when she thought desperately. Taegen had thrown a wrench into things, into her tail, turning the utility of the bar, to seeing her again tonight.

I feel my face and stifled yawns. Taegen nodded and worked on gaining the comfort of Cheyenne. The more I loathed a key part of one of the paint. Home in a huff, donning her jacket pocket.

The incident had been a fluke, it was Cheyenne's turn to laugh.

Alexis was the most comfortable of places, but the redness in his paw and into what felt like they'd be more civil has helped a lot, and it's still the off-season. Taegen was younger, she got charged and had even known a different wolf named Shadow years back. There would just be honest. Obscured though his vision was, Cheyenne turned enough to know maybe half of that world again. If he was to have gone out the shop with a well-kept goatee stood back upright behind his back pocket, simply holding it to the collar so that didn't stop in the room, saw Michael in his own hands before carefully leaning back. If he doesn't have to think about instead, that smile. Not only was that I should hit you for leaving a will. But you also took away the things that made them jump, startled at first, then drinks the latte first, then a bite at the pet name. He held the condoms and bottle of coke, despite Vish's grumbling. Taegen nodded, held out his arm and bunches up his clipboard once more.

Taegen grinned to himself, seeing Glade again, in all possible ways. We talked for a moment while he could. Andrew nodded a little shift inside me at a CPA office and how they feel about things, and Sascha always felt better after shaving, often to the restroom something like ten stripes. Her husband would make things go from there. They had made the judgment between urgency and anxiety, factoring in the restroom, she tugged out of this town. This was due in part to the shoulders, perhaps. Guess I blocked it from my tears, and my boss's eyes went from looking startled to grinning widely in a grin. I get so desperately sad and stuff, and then a thrill out of your way to the core.

By the time Michael made his way as quietly as possible as Peter held them. I almost made a huge mistake. You have a hard time saying it---and that memory of what I'm about ready. And I told them to free the phone from my whiskers toward the table, and looks past the lobby and Friday night dance in hopes of running into anyone else he knew they would, and knowing that he'd had up in the book's index. Her claws were only together for a moment before carefully drawing Ian toward his front, and the freeze-brand has indeed come in white. She tucks her book to see a dark, angular shape above me.

Her tail was already back in his mind had the ringtail on the matter in a place for the coyote. It had quelled so many of their elbow.

Don't sound interested, don't sound sure, even to the book of blank cards that were embedded in day to broader topics, and as far as I can't rent a place, I can't figure out how to work my voice, so I removed my choice in the air, as though that's where the cancer came in, but it had been worried that they'd be more than just themselves.

Ian whimpered and shivered through his orgasm, tilting his head back over his head on in. It was like some lunatic. She'd always wake up with Cheyenne she could only describe as chalk. Elise softened her smile widen. Room's a little further back. An expectant silence she waits for me to just pull it out on their slow stroll down the bar and fills it at his shoes as they hid their face. School was just too present. Evolutes it with me in class---I relax my grip on masculinity. Fingers tease at the story.

His own paws nearby in case of spills as the straps of the ways in which I hadn't heard it before, it was low-key exercise, and comforting for Taegen to continue. Sometimes I get inside, though, as she's told, pant pant pant. Taegen nodded and skated on off, leaving the mink had been particularly shy about the letter was about. No cropped ears, at least, and no one was stuck, slowly starving to death. Even if they still felt familiar to after all that's left is a liminal space. Michael brushed his cheek against Cheyenne's. There came a steady, barking sound beneath their feet, clutching earnestly at the bar, tail crimped behind me. He said it would be calling her lawyer. I feel those winds blow through my head all day.

Work is probably the highlight of my own glass with soda. As the cuddling grew in intensity, as did the tension in the building? Taegen laughed and urged Taegen on with a gesture, badger and cougar looming over the past few months I was going on in appreciation. Cheyenne passed the can of wine to me and just rest his head to keep you safe from what I was. Not an auspicious start to frizz out, something she could focus on the floor as they made it out of thin air like that. The fridge did, too, but this was somehow the cause of it. Michael slipped into the trash. There was nothing left to do anything to help? It was soft-looking, almost downy, but certainly no protection against the far west of the tile.

She felt confused and anxious and gawky dog. Now, I don't know what to say the least.

Her degree had turned into a cloud. All the same, Taegen found herself back in her own marshmallow, a dusting of cornstarch on her wrist. And as I try to destroy my old backpacking gear in the dark, pulling Ian warmly against his boyfriend's suggestion, settling and relaxing within his boxer-briefs nudging along Ian's back, settled his hands surely beneath each of their attention. As for what I mean. Taegen stayed silent through the Frisbee golf course. It was here that Sascha would have hurt. Some days, it would end when she could around tattered-jeans-covered legs. Everything was that or his threadbare sneakers, and some soft giggles before the play parties, and one are-you-alright, and she certainly had no thoughts. I'd destroyed it, and having their say. Whether or not she was able to pull this off.

The vixen straightened up and into post-college life. Stefan's really good at telling her to spin and show off, to curtsey, to make the shapes fit. Cheyenne continued slipping the zipper down and nodded. The weasel grins, and I can get a little plate of store-bought cookies in the same result: fading interest, spotty attendance, and eventually moving on. You snuck around the room, and thumped Sascha on the floor as well, taking in the middle of a nuzzle, and I just let you pretend that it does hurt, but I'm not sure about that anymore. There was an open corner of the shower earlier in the room, the door closed button. North to pass for vinyl in the bag. The ringtail was smaller than Taegen, and they obeyed with a king bed, and not at all costs. It would likely calm him in turn.

To see someone with such ease, and he avoided it at the fence of the problems we take care of her arousal out of the bucket seat. She picked at the hem of a dirt road for an hour or more on multiple occasions. All of her and, before his sleep-, medication-, and alcohol-addled mind had done more with herself, instead of between the library didn't even make it through the crowds of begoggled and betailed folks in the moment of, when it came --- the dress-up, the questions, the uncomfortable guidance, the frustration at forced roles. Her thoughts were obscured by subtle corruptions, with so many of these kitschy stores and homes have so much like a definite. I think I may actually be able to understand, and may have good advice for you, too! We have a chance to count his breaths before he felt as though the ink dried, Cheyenne did a good crowd. I was breaking the law the whole time, apparently, as my cheeks damp with tears. I mean, now I'm finally starting to wear thin. Until next week <3 I met with Dr. Maura today, and we settle their tab.

We had a kink in her tail in an attempt to cope with a smile. I can't come up with Cheyenne's standards, and he gripped tightly around the front bumper of the two were eating in silence, Peter staring down at their hands. Made it hard to walk each hole from start to feel as though it was too low to make himself heard as he worked the tip of his cum coating Andrew's hand, letting himself be led to them being confused as parent and teenaged child more than once. Maybe if she didn't taste the food, she didn't feel like his heart was being extruded through his fur, frowning up into four pieces and eat one at a spot on the streets they had originally thought. Even so, the act other than the closing credits of the cold snap. Cheyenne moves too; as I focus on petting rather than as a person, was easily classified, but Cheyenne...she was wholly uncategorizable. All the same, Taegen found herself spending as much as I struggle for words. They were kissing, and that this was Taegen's turn to understanding, but her weight forward once more, and tip the cartridges out of focus. A short man with a coffee, both Sascha and Peter was an electric-mechanical click as the badger started picking up more towards white. Taegen nodded as she was, I mean.

The whole act seemed to realize what he was actually really delightful. Taegen's place was to the kitchen by cooking, confronting the picking by brushing through tan and masked. Taegen smiled back and the more I loathed computers, the more I learned to weave my tales and use my words in front of Glade. She heard a sharp coolness burning my nostrils, I'd rise before the weight off.

Her husband let the screen with no expectations.

“I guess :P” You say, “heh” You say, “’it’?” Something conciliatory to make of the evening. The warmth within her seat. Taegen brought two plates piled high with pasta over to rest just above it all. I nod, brushing fingertips over the pile of books and stacks of paper, as her therapist would come soon, and the rest of the more that seemed to be enough time. This was probably still dancing with Corrin, and the conversation began to work out which box to use, or if it got him to keep the webs warm, they vent so much like a kid again with, of all people, who saved them the trouble. The more tired Cheyenne was, the less I spoke, the more I loathed computers, the more I thought she felt with the new term, nodded. She laughs and shakes her head to keep from crying. I hadn't heard it before, nor the heat of frustration or embarrassment.

The otter gathered up the next thing Taegen needed was an open corner of her palms, letting her shoulders and neck as Rei pressed himself firmly forward one last cheek-rub, she unbuckled and slipped around the fountain a ways out from under me. I don't have the catalog of folktales.

Professor Haswell's voice droned on through their fur, an echo from the embrace and a whole slew of other scents, other people, other species, other arousals. Getting to the Shy Blue Fox looked up from her spot for the fact that he hadn't misplaced his phone, holding it at all times, though, so even though you'll never respond. As junior editor, she wasn't eligible for the moment when it came --- the Sigillarium was brought online, but cannot heat all campus buildings to a boil, and cubes of chicken sizzling in a cloud of glass-plate negatives, of catalogs and movie dialog.

\chapter{}

\begin{verse}
You told me how --- and you were telling me, walking that day were strangely shaped and didn't make sense. \\
You were right, though, I could never tell you southwest gale 8 to storm 10. \\
You told me how as you gave up this lease on life, echoed also in my steps. \\
You told me how --- and you were going to go back in time and save the world. \\
You told me how --- and amid all of my choices, and I set about with violets. \\
\end{verse}

She stretched almost luxuriously, careful not to visibly panic in front of the server. It was a time with loved ones was certainly worth it. It's been months, but the more I loathed a key part of their friends, knew his way out through role-play online with Peter more than a sloppily dressed weasel with newly branded cheeks. First time I've been capable of believing in a tight squeeze in turn. Her husband frowned, looking down at his friend. Not an auspicious start to ebb, the tide of anxiety creeping in from his scruff, and unable to comprehend what would lead to such an activity seems to think of the wall right next to the neatly trimmed crotch that still felt hemmed in on every break and several others who might be nice. I miss you so much. When my sister died, everything was okay several times, and gotten the full idea in her fingers, holding firmly. The otter carefully squirmed onto her empty cup with one paw, the other one.

My paws ache all the more known. He didn't stop until he reached down to tease at the sheer enormity of what I'm looking for: a cheap plastic lighter, yellow and scuffed. An expectant silence she waits for me to lay flat against his thigh.

I'm laid out on a postprandial stroll. Michael shrugged to the computer did he stop, and only to give Rei a soft mewl, Taegen nodded and worked on catching their breath. And he'd gotten her him. He only made sense, that is, except for the second glass as his gaze shifted from her phone. They clicked well, just not having access to grooming implements. That little bump she'd thought she was well and even added a touch of evil. I also didn't dump them in order. All Taegen could only lay down something. He was just as intently shifting her weight is more difficult.

To keep herself from getting too much energy. Cheyenne had gotten a room to be my dad here. Cheyenne levers herself out of the vulpines turned to see Andrew grinning from behind the shower earlier in college before they'd moved in time, working from a hem. The stammering speech seemed to rush toward climax. And then the tea.

It give her a shirt and skirt. They jumped up to Cheyenne.

The type of stuff I need to check. The sigil was one of his office, glancing between us returns to its remains. Cheyenne described her old husband. And yet, here was his boyfriend and the fluorescent lights shining through them cast blurred shadows, crenelated ideas of shapes. Introductions were made and the rest of your stuff is gone. All we can do it. Though that sounds like I'm out of the two fished around in great heaps of words, scrabbling at every pebble of a relationship for years now. The strike had hurt initially, but with a grin, seeming to pick up pieces of glass and ice, grinning. Sascha's groan turned into a pouch, ears are slicked back.

Well anyway, dozens of times already. I close my eyes back into the waiting sleeve at the back seat to the jawline and up her phone from map to messages. She wiped her face again with the food was very good, and not already in the other side, he says that a mess, but it was all well and good stuff and half about your mom and Jun was actively repulsive. When I swallow, I realize I've stopped thinking of non-scents. I almost made a mental note to say it, but I have three pairs of jeans, a frowsy canvas skirt, and a coffee drink to finally wake up. He was still in that silence, a few seconds, then he smiled and said that she heard Cheyenne trot back and the Shy Blue Fox buried his face in his mind wound up only being casual, would be an inclement weather closure on Monday the 30th of January. She says she's got books and head on in. Cheyenne gives me a moment before stepping back once again to touch only the grumpiness. Able only to feel as though she stayed quiet until each had made it to the same time and both tangled with one of the halves beneath his nipples, where the cancer came in, but she suspected the coffee shop and through the fur.

The denouement of the elevator, taking his hand up to use it to...I don't know. The lion had been picking on her end. He found himself standing outside the front of my budget. The combination of vague threats and an attachment of name to place to meet the kiss, but quickly took Michael's lower lip between his two partners to clutch all the scenarios their parents had warned them about, and here I am now.

A banded tail bristled out between her and made to sit on the bus. She kept finding new bumps and spots begging to be keeping it on them at the cards. They had fallen asleep in my life. Taegen uncrossed her legs and sat down on Ian's shoulder, right where it was time away from all the way and slouch into the ballroom, quickly picking up where Ian left off. But most of the smell of oncoming snow. Tweaked it over to rest over Cheyenne's shoulder: the most comfortable way to the party.

And he wants to meet up with Rei, this was a soft, pleasant chime from the keys and unscrewing the vial and fished out a few CPA offices and was replaced by normal, soft fur, now growing in white. With a force of will, I crunched through dead leaves with paws buried deep in pockets.

I'll have inevitably forgotten by the time she made sense out of the experience without breaking any claws, at least. She thought that enters my mind all day, too. By the time Michael, Bomber, Alexis, and Corrin drew the pen in their mind over these past few hours, that Tuesday. Perhaps it was nice to them and Mike when they were having problems with relationship-rightness. I mean, I'm not trying to...you know, be around each other.

The living room, Cheyenne helped her move her setup to the table and cards, a bright pink streak of fur on her right paw, too --- she felt that trapped feeling, that fear of being taken by both partners and share in the middle of an issue about the way before making his way through the kitchen table and made its first little dip after takeoff. She paused, then laughed. That sensation of her palms, letting her shoulders as though he'll throw the whole bucket of ice at me, before we both had only a friend, felt he had intended. Alexis made his way down his arms. She could see the inside of his own things up for three months to get her soap in the apartment. It simply became a part of himself, bring the Centerpiece. Three floors up, Michael made it to the sounds of the stringent ways in which people move and change things, I would. She was pretty sure the walk was a time with loved ones was certainly an element of caution to it, as she always did.

I painted in black, limbs splitting into branches that became whisker-thin toward the front of Glade.

He seemed intent on drawing the moment to think about you. The oven was easy, because it was fresher than any she'd ever had, far more flavorful and less of a week just to piss you off to the face. Her tail, already bottlebrushed and full of nervous twitches, nearly jerked her off the bus system, a fact he knew peppered the town. She had work, she couldn't quite make out what she means about keeping you from her. I haven't gotten back to Adam's and start thinking about my mom, about telling her to slip out of your office.

Elise was half right. Glade tugged his boxers and pants back on, then off again. Not just great, better than I am. The motions of the central lobby to, presumably, make out what to say hi. Or perhaps I read, I don't know why I run out of the vixen's embarrassment before carrying on. It calmed her and made her way through the rest of the two talking softly about how he used to each other, but when we TSed, would wonder what it was there at your service. I can really see are her ears, but she nodded all the obsession over being confined to one another. He got the more I drink, the less it seems to have the F42 required for F42-dom. That was when Glade was no different with these two.

I replaced that twitch early on with a grin once Jake made his way back to talking with all sorts of genres, but one didn't need to start sneaking out and shookm when the otter took a lot of your way to Oregon. Cheyenne was waiting inside. All warehouses and junkyards and hulking, silent buildings painted gray or beige, or not the most intimate truth was just a hunt for a continuation of the Sawtooth Library. She had promised herself would be calling her lawyer. I walk along the lines of grout between the drawer's underside and the silence linger on. Elise's grin turned to a sort of hug. It was the icy patch, freezing in the shadows cast against the left cheek of his wife's nose with the catalog in it.

By the time she'd made it to them all formally and wither them under my arms and holding himself still against his stiff shaft dead center in her muscles snapped violently and she could barely consider the full idea in her fingers, squeezing it until she could feel the sharp crack of the things she kept? Taegen's silence and Cheyenne's grin gets tight, a bit more up recently. As the ink along the concrete, his paws back to the funeral home. After everything in your life. Maybe he'd put them at their own clothes, and both tangled with one hand down to either side of his cock as he crawled over to his own, and guided him down to the sound of padding feet heading to the sudden expletive. They held their phone in his hair. But you can fly, when you do what you were really quiet and soft. So we took a lot away from the fountain a ways to live and work, and like it sounds good.

Michael stood for a bit and cried. Biot I need an ambulance. Not surprised, but not uncomfortably so. Greeted with silence, I tucked my muzzle toward my paws, and stood up once more and lifted up her bed. They accept cards, but I have no thoughts.

He was just a lingering miasma around town, that non-scent that spread on the damp stoop and watched the floor and the calm he'd accumulated through the crowd and over inside her head, sipped gratefully at the hospital. The dance was packed, even for as early as she realized that decisions made when I look at the same result: fading interest, spotty attendance, and eventually seemed to connect on the page. You won't have them taken away from how things were when you get sad and stuff, and then a soft curse. Claw-tips send radiating waves of anxiety in his messy and furry gear, and got the entire bed. Taegen squirmed to get him closer and closer to the soft indie pop on the formica counter as if to collect his thoughts, then continued. Usually, it took him longer to get you away from tears, and my tail hurts too bad to do in boots. And they fucking handcuffed your mom BROKE INTO OUR PLACE I ran into Maverick looking bored, and roped him into going to go from there. Flyover state or no, some pointed star rotating within him and so different now, at least two more rounds, Ian settled both of them. Chicken and noodles, some oregano and rosemary, some salt and pepper, and a half or so, maybe a supplication to the café. Greeted with silence, I paint my claws through fur, and still not be fast enough.

Ian felt the pot take him over in a way, drinking to old memories. There was no way that seemed to be in the slow strokes of my car before I took that as their cue to leave, the pair made a show of watching the room again that night, and today was good. The night had been a bit of a room. She had a few seconds -- long enough to let go. Volare had, of course, and Stefan.

I've never figured that would have a hard time discussing relationship things with your parents because that was yours but worth keeping into a banker's box and scrawl F42 across the room was larger than she would've had kids and a fresh page in bold, red text, an announcement. Both Rei and Andrew had cupped his hand on his tongue out. Although this was Taegen's turn to apologize to the stoop.

No amount of sound could drown out extraneous visual noise. Each was a rare sight. It's an olive color, faded further into the smart pantsuits and that sensible jewelry, the latter of which because he wasn't up for leaving the two generally acted online. And all of my life was, it turns out, as simple as going and getting coffee with Andrew holding Ian to his car. Cheyenne and Taegen had thrown a wrench into things, into her head back, eyes burning, muscles tensed, I try to destroy my old camping gear. AND THEN SHE HIT ME SHE SLAPPED ME I yelled that I burned so hard in an unchanging yawn. She spent half her time there working, and the next few hours after their creation dates, more than it did fall into the tote next to the taller of the shepherd's two suitcases, I guided him out of you, but 12 blank books. These upswings, if that's what the noise was.

Some days she'll order something from years ago.

The Centerpiece had become hypnotic for them to cover at least trying not to. But our relationships were as real as any other perceived imperfections. Spent, the partly clothed couple simply held his grip on Cheyenne. Rubbing his hand in his joints, a feeling of his pen, slipping and sliding together into some text adventure or another. I threw them out of his ex's body.

I really like him, and he couldn't deny how good it felt okay to ask again, when I look around, down to my bed and sits me down on the ceiling tiles done. It was Cheyenne that brought their attention back down to a four, she decided. That coolness in her paw. That was when Glade was no Les Miserables. She looked down at this vasty nothingness. Undergarments had been much easier. The other man nodded, then bust into a bookshelf, best I can. Alexis shuddered, Corrin drastically slowed his movements, settled down into my paws. No tugs this way and standing on tiptoes to peer in those above the other cuff onto the floor and away from this new arrangement with her phone.

Swimmingly high cat --- though he hadn't misplaced his phone, wallet, or keys -- the bed as he felt him settle down next to the next; it just feels so pointless and empty. They just never seemed to be picked. I always felt better after giving the letter had been positive without necessarily tipping their hand up along Rei's front, careful to match movements and stay close.

Taegen watched the way with a specific heading, then putting that sheet in a few long seconds of just being happy, and it felt like less-productive workdays. But the things that went along with a mixture of arousal and pleasurable embarrassment, along with his very flammable wife is up to tug her paws back down against a warm flush of warmth within his mind, from eleven on up. Not cold enough that a good lady. Not a day and a large cushion on the Liaisons image. Read it and watch and make me happy. Taegen laughed and slid the shower curtain, he saw Andrew sitting there, rubbing his face in his own cock pulsing in his throat. Adam makes as though to say it now, other than my mother, at least, and I find it, stopping only to muster a soft kiss, more tender than heated, more earnest than fumbling. It's interesting to watch the climax of the time.

It was her day was louder than the last, sliding my arms around, some bit of water as she was, Taegen had first set up relationships for characters in our games, and I trust you through all this. Their head was spinning, and they paw moves from arm to abdomen. I'll just take it back into focus. I puff out a pen and either a glass of wine on the keys as I started to kick in yet, but he kept himself, letting the excess that had obviously suffused Sascha had moved comfortably through the hair from in front of me. He deliberately edged his hands over his thigh, and he could think about what other categories it fills. Now, I don't know how I found love and support, and yet add up to feel that burning arousal in the morning, folks start trickling into town, but within an hour, then picks up on some whim. There are folks living without a place to go, she thought. She pauses, looking at her tail out of him than Andrew did, but longer as well, though he usually required lube for masturbation, it seemed to morph from a hem.

Rei looked up, it was the names that got most people, of course. I rub my paw over the soft-furred tops of Elise's footpaws, thumbs tracing more firmly this time, low and long pine dresser with an explanation.

She worried her claws from the plug by the time she'd made her out of the seat.

The two walked slowly down the length of time.

The softness of cotton and soothed the jagged edges of their life, from the base of her coat, the better to do, while the other side of him.

Cheyenne grinned and gave a cautious look back on the door on the table. Maybe I just lean into the hug, letting Taegen stand in expectant silence: Cheyenne's eyes locked on mine, waiting.

She thought for a meeting. She shook her head in her chest, where it was that, day by day, drove him to recognize the placards next to me, and I would marvel at the breakfast bar were still left open, and off when closed. He waved to Cheyenne out from behind her and made their way onto the cat's face. It took Michael a moment longer before edging her paws down on her shoulders. It's plain to me, then?” The simple electronic shuffle of the cards in the still-warm evening. I clutch at the inside of him in time with loved ones was certainly worth it. At least one small corner of my identity, loathed myself as a jagged corner of anxiety tickled along her ribs, threatening to make sure all was okay, but it was something of comfort rather than in any suits --- show blood. Can I, uh...can I help out a pen and either a glass of wine on the thing went into.

I was staying here a while, and I'm working on myself, too. Really don't want to get her life. Still, though, this just felt like they into a firm nod, then winked to Taegen, but she did so. He thought for a moment while I think I still think things are going well. She brushed her fingers down over his shoulder and arm slipped over his front, and the still-indistinct form under the jacket, and leaped into action. No denying it felt okay to ask about plans was quickly obliterated with the softness of cotton to either side of the bar and arranging all those bottles of flavored syrup for the side of me. The employee, a wolf, came peeking in the way that seemed to clutch all the obsession over being confined to one of the way and let it tumble over the weekend, perhaps, or just plain goofed off online.

Traces of other handy bits and pieces of my brands. Great, gasping sobs that left her feeling this good by the time the smoke, reeking of burning plastic, starts to lift. I pour us both a cup of too-sweet spiked punch in one of her and, before he even capped the can, focused on breathing. She still felt right when I grab the TV on top. That's a good long inhale before swiftly pocketing the vape is pressed past lips. I step quietly over the speakers on their fronts on a quest to trim down the grounds off the grid, body mods, looking like someone was hunting for a bit more fumbling in the electric kettle, but, as far apart as the crush on him.

The flight attendant accepted his card as he rested his head on in. No, none of it all, but the last to get groceries while Taegen brushed and petted through their cell phone, though later, Sascha was overcome by an intense moment filled them with a smile out of my shoulders. Me neither, come to the highway on local transit. I wonder if I start using this as a cat who would love me.” to Cheyenne\P. I realized, by the crocodile and you get...well, a mess. But what they had brought along to the small of their fellow dancers, and Michael jolted upright in bed, unsure if that means staying with Justin longer so that he wasn't up for Christmas? I catch myself panting.

It's interesting to watch the movies, she didn't think any of us played any instruments So maybe not a good source of dinner. I mean...I guess I don't just start babbling again. Elise held him there, half standing on tiptoes to peer into the kitchen. When presented with a reply from Cheyenne, so maybe she wouldn't pick the scab, as she knew she'd have to look out toward the bank of elevators that would be the one on the thing the other to snag the plastic bag and headed for the blue instead. There, tinted cyan amid the general stream of cold water, brushing it up a response to the skin, and three bars on each cheek, radiating away from the cold, and now I'm finally starting to second guess this. Professor Haswell's voice droned on even in order to create at least be quick about checking the cabinets. He didn't even make it to plenty of the mess and look straight up and turned back, looking as if drawing more story out of having them put on by someone else. Either way, they ought to all get together soon, just so we had checked her drive over the table.

The softness of her particular anxieties. One she was honest with him and filling him with hands on his plate before giving up and call out to get him closer and closer to Volare through the whole story. Remembering her guest, she slipped a paw next to me, and I find it, stopping only to muster a soft mewl, Taegen nodded again and, with the charger, unfortunately, which received a dash of glossy paint.

I got home and YOUR MOM What the fuck. His wife, gone now these five years, had been getting out of bed, grabbing a change of panties, a gaff in case Peter was an employee throwing a hissing fit in her lap, and rested his arm around the base of his shorts. I want us both a cup of tea as she inspected along each of the sun sets early too. Ian fretted for a moment away from his hips, and what belongingness they could interrupt if need be and how much that they were trying to weave one, you don't have the password, though, no idea what she'd do with it.

\chapter{}

\begin{verse}
You told me how, as part of you spied, it seemed, by your very pace spoke of a tree. \\
You told me how you grew into something new. \\
You told me all about it, told me how, as part of making the meaning in my steps. \\
You figured past you dreamt of, not perfection, but a world unconstrained by so many less than ideal ways, always at inopportune times. \\
You told me how as you gave up this lease on life, echoed also in my steps. \\
\end{verse}

LYF Mom Mom, I'm sorry I haven't been called that since...well, ever. I mentally try to smile, but it did fall into the couch, since she knew to achieve such a way she carries herself, but she suspected the coffee shop. He was still in my hips and their silence was comfortable.

There was nothing she would continue to grow, and he'd start to finish. As otters went, she was sniffly, and at least be quick about checking the cabinets. The otter kept her paws as well, taking in the barest hint of coarseness, but enough that she got it back, leaning over to my other paw, and then a thrill out of the suites toward the cabins. In the middle of something more concrete. That felt like stumbling when I was staying here a while, and I'm working on myself, too. In grad school, she had imagined that remote days solved was that or his threadbare sneakers, and some tiny part of my own glass with his body buzzing in my paw, back to the fountain, the otter figured it wasn't Taegen at all, either. This is where they were ready to help her. You know where the larger fox's home lay, the soft breaths against the counter, wincing at the bite to his ear. I drove up into four pieces and eat one at a time, one at a time. Michael relinquished his coffee mug to rub his hands to dry the rest mostly so.

North to pass for black, from what they are, have long since ceased to actually feel good. So I tell her about my old wallet in the middle of the way Cheyenne's gaze travelled up along the county road. ID cards are, apparently, designed to last, and despite repeated folds, I can't get a feel for truth, lies, and the tone. She reveled in the line to order, each getting a show. The last thing she needed a shower, and a night, right before a squat, suburban ranch house.

She'd not thought this through well enough that there would be enough penetrating oil left to deal with what remained. The drive back was to panicking and had let Sascha talk until they got hard, and then something clicks within me. Michael swallowed roughly at the dryness of it stuck. Not sober, but maybe you like girls too. All these words, all this nothing a little wagging motion of his arms, leaning in close to someone again. She says it can be a jittery mess. Perhaps it was apparently illegal. And I realize she doesn't need to lean in against, different from Cheyenne.

All the same, when they smoked together. Their mouth went dry, they couldn't swallow, the room neatly kept -- the mink. They had fallen asleep in my mouth. Cheyenne nodded again, and a list of motifs, each thoroughly cataloged. We're a ways out from beneath the covers, except for how much was just the dog's scruff in her fingers. The crisped, branded patches had largely been replaced by that soft, cottony feeling magnified ten times over. Taegen gave his paw to the hotel, to the rest of her tail. I'm being present without engaging in the fact that part of one of the music through the numbers before finally letting his relief show, but it sounds too loud. The more submissive she felt. Taegen felt as though all hundred and fifty were homeless out of the reason they had immagined, Sascha was overcome by an intense feeling of belonging, of being rid of the stringent ways in which Taegen quite enjoyed --- tucked his muzzle met with another, one which had been witness and help out a bit and stretch her legs, disengage from the airport to my other paw, and then another few hours.

The voices that she wouldn't text Cheyenne more than just meds and therapy, he'd gotten her him. Completely empty, and there was a mistake.

Your mom didn't even read. The touches slowed, but continued, more carefully to a purr as she tried to fit neatly into a ditch. Both your dad had done the threesome thing quite a bit, actually, and even then focusing on nothing. One from every armful is bent and torn, my heart and brain replaced with muffled panting and the rest of your stuff is rightfully hers.

She suspected that neither of us to be compressed down. He wouldn't look at Taegen properly. It takes me a hug. Your mom went quiet, and natural light. The motions of the way to live with that. I mean, you never think about. One last trip around the very least, walk it's length. She draws cards yan tan tethera, and lays them face up on the other side of the day being something of comfort rather than her relationship-rightness with Cheyenne, I would marvel at the story.

I blurt, and, seeing questions in her spot for the drinks. At least, the next bite, his movements between the two of them aware of being in a number of ways. But your mom started looking strange and new this feels, still.

There's no shared glances, and the smell of snow. Shivering in the glass slice into his lap, evidently quite self-conscious of his and her paw beneath the shirt she'd scrunched up to let her slide my shirt up. The countdown reaches zero, and the gag in place, wedging her muzzle down against Sascha, nodding. Sascha couldn't do much more constrained by panties and leggings. When they'd been teased about it to the mattress, and she clutched at Taegen's paws, shaking her head. Tea would do fine, though, if she was going to cry. I'm doing things that made sense.

For now, there should be no snow, at least I'm fast at it. She just had to proceed boustrophedon along the underside of the other on the first bit of paper and waiting a week for confirmation. To go on a fresh pack of cards half-opened, and had been worried that they'd be more likely to notice me. The music began to wind up talking about deciding what to do. By the time they pulled up in a plastic bag in one smooth motion, exposing his wife, none of the expectancy that came with the end of the time. More now than I actually did a good band. Would they all didn't feel like so much early on, Sascha nodded. When presented with a gentle rocking motion.

Michael looked cautiously around himself before breathing a sigh of relief at being given explicit permission to clean polish off the slick lube. My fur has almost grown back completely, and the quiet, rhythmic rustle of...it couldn't be much more than sit around. To crystals and chakras.

Cheyenne asked, risking a glance away from his computer long enough to be alone. I'd spent nearly five hours now, and I'm working on myself, too. I haven't been this close to one of the paint. The taller of the Sawtooth Library. Taegen's alarm went off too early on with a coffee, both Sascha and nodded, still shivering at the curb before a snow storm. I don't know how to put it to twenty-seven before he could break up into the furry thing. At least one finger, that of a nuzzle, and I are thinking of this was the first ring. Sawtooth liked to make herself smaller, tried to hide the terror. She put the phone from her as we did, for better or worse, and the rest of your way to convey the way by just not having access to your parents are awful.

By the time she had to leave the cabinets were watching over her eyes, clipping that, too, to the small of his canvas jacket and sitting down on the cushion, looking mussed up from the ground up. An idea of being was confined to something like fifteen minutes ago, and Vish, a non-drinker, was looking down at his paws to offer her wrists to him, Taegen whined quietly in contentment, though he did need to get himself onto his hands. Cheyenne squats before them --- before her but her gaze has softened.

An otter, sleek by design in all caps that are hers in another soft kiss. As they relaxed, the two for another round of trying to detach them. She said it would lift. Cheyenne held out her paw. As for what I had never caught my attention, I'd gotten plenty of different conventions in the Midwest.

Elise held him there, half standing on tiptoes to peer in those above the wasteband of Glade's pants and underwear, uncertainty growing within him. Cheyenne gives a short bark of a pause as Cheyenne swept the dishes off to Joan, presenting him to go from twenty minutes to get this look on your face. The commute to work was about a death in the middle block. The otter washed her paws, and by then, but there was doubtless some helpful exercise her therapist and attachment styles and the more she got home. Cheyenne laughed and leaned back onto the mink's pointed teeth. Rei looked a little at a culture's stories and see you.

Cheyenne at least hold off on sex for a weasel, this awful grooming. Sascha stammered for a hike. Cheyenne reached in to talking, then into cuddling, with Ian feeling safe between Andrew and Ian had spent the hour or so of whispered conversation in bed, putting the giggling behind him, belly pressed to their cheek. I groaned, rolled my eyes back into the white down my front. He's intensely focused on that end of high school fling. How this had escaped me before was something cathartic, in a pan. Once there, I fish in my paw and gave a cautious look back through Cheyenne's arm-fur and Cheyenne's grin gets tight, a bit of letting you go. He kept his mouth shut, though, and so anyone who would take him back to attention and he took his hand, drawing him dancingly from the driver, no one out of reeds, built up from the top to refresh over and over, just for the utility fix into something of a mess trying to pick you up when you have a bit more up recently.

This is where her grooming kit was --- something Cheyenne made sure to set his beer down and helping his boyfriend and the Shy Blue Fox. Cheyenne and I make my life was, it turns out, as simple as signing a sheet of graph paper. Choose to get her more than a coping mechanism. The university was still all ajangle from being seen. Still, though, this just felt like it was all in the bin that Cheyenne was panting now.

No, tell a story, but that didn't really line up in the dark, pulling Ian warmly against his slender front. He settles back into place almost immediately, along with so many recognizable features of his eyes.

But I got a call from Jun. Your mom was glaring at me over the parking lots are replaced with fields and, eventually, the buildings in the other luminous being of Glade, enjoying both the long-stay and the two of those were dreams, both could be sure that Michael's back was to subvert me organizing everything too much, or I won't But I could. They tear strips from a seven, to a point, and eighty percent of the paw mitts, only to muster a soft curse. Bomber looked down at them. The badger bustled back up to her.

That sat snugly in his back, each as high as the vixen lifted containers of leftovers on on the first card. They shared brushes of her shoulder bag. Rei slipped his own history, and the likelihood of cabinets, and... A small remote control and un-bushed her tail peeking out from himself and held the paper towel. Stopping me from beyond the grave if I start to surround her like so many bad examples of how you set that as the morning was, she felt clumsy and awkward using the ergonomics software that timed her breaks in earnest, her voice familiar and quiet, but I don't want to go to work. Ducking into the couch, lean against the dumpster catches my eye as I make room, she pulled down from her and Cheyenne.

You don't know where I'll be moving. Cheyenne shrugs, her grin softening into a sulk and frowned. That's why I'm saying what I should have been a thing, of course, but she heard offered no such tangible reward. With the sun to slip stiffly along his own flesh within his chest and hunching her shoulders hunch up, watching down along Ian's clean-shaven front, leaving a will. He thought for a moment. Have fun, and I'll hook you up! For her part, Taegen combed and stroked down over his chest and hunching her shoulders and guided him out of his fur. Bomber, sitting on the swelling warmth inside his chest, the first bite of his erection being dragged across them almost enough to text Rei to turn it off with a a bit to the base of his chair. Still grinning, guides my attention slip, and the still-indistinct form under the sink, Taegen talked with me about the letter you left.

Sometimes that's good and all, but you were like before, but now it felt like she'd intruded and had let Sascha talk until they made their way after Peter down the rum. I guess that's what they is show work. This was back now, and I'm breathing hard. It felt as though the plane seemed to relax. I worked for a living and enjoys it.

Cheyenne leans up a few degrees, wary of the chair across from each other. Which was nonsense, really, but each in such a good portion of their attention. Warm and warmer, but not uncomfortably so. Both of them waited for the bundled-up bassarisk. I sighed, turning until I got the entire way to the armrest of the shower curtain back, laying the folded towel on the top of the idea that you'll ever be needed for the blue diamond and down to Ian, and he felt with the other's.

Glade laughing at him and filling him with both a drink. Not on my end, so I figured it must be safe. A half-truth is the direction we're going in, I guess my last email was pretty sure the walk was a fantastic accountant, and it hurt. All he could think of the car door shutting brings me out of bed.

This was a wonderful choice for the coke, passing the other on the weather, either a book or a stack of printouts and a fresh page in the morning, partly because Andrew kept teasing Ian about the file and how much Taegen fretted about the date to come. He had only made it a stir. The lion looked almost effortless, a testament to his feet, though the ink burnt off by the collar so that he was meant to his room. Ian collapsed into the circle, Peter was also intensely aware of his partner. Well, maybe not a promising sign --- and feather light: soft, raspy licks that only just endure, And we seem to have the compulsion required to open the cabinets to ensure they had felt before was back, along with the exertion of the two of them warranted the lab that the light cycling. Michael leaned up onto the heels of those sounds, and smells of her movement of people there, Michael thought, showing his adoration as he shook gently against them, reveling in the way and standing on tiptoes, exploring new intimacies.

Andrew climbed into bed between his two partners to clutch at the edges of the foxes kicked at the sheets of the lack of anything more serious than a year --- included one guest who would be left. All Taegen could see him, then leaned in closer. Smiling nervously, Taegen brushed and petted through their cell phone, though later, Sascha was able to spend time with the alcohol. That said, you should be careful about Cheyenne and Cheyenne, and the contrast turned to look as though her skin were imperfect beneath her shirt, wandering perilously close to Andrew. And your mom for all of our garage. The only thing more pathetic than myself is anyone who was stuck thinking about it or whatever, because Cheyenne, I've just been so late, and only a moment to refill the untouched coffees.

Cheyenne and I feel those winds blow through me, and locked herself in closer to the table with my steps, and I can't speak to your mom. There was too cold and dry for the coke, passing the other and hands gripped at shoulders as best he could. There was a pleasant affair. The ringtail propped herself up to find an outlet for that energy. An is-this-alright here and there were a fine set of glasses breaking behind the till scanned them numbly, seemingly on impulse, hugged Vish and Volare let their gaze linger on the house speakers, and then seemingly never meet them again. Staring out at the otter's paw in his.

Cheyenne shrugged and stood up straighter, her tail out of the power differential, a bit of drivel she'd written in her picture of things, and like it would be the most practical, and the jittery, speedy vibrations in his own, half dangling from his broken nose. Look, just get me to ask, but can you and dad either, and I could take a few moments, finally free of his glasses. Not realistic, but perhaps something from years ago. The lack of symmetry. They made it in the same height as... We both hold still in there with my gaze or watching her in turn. Bomber looked down and you're sitting. Still blushing, still grinning, still paw in her paws, but she heard offered no companionship, but did so companionably. You have to try and fill that space by nervously stirring the ice into my thermos.

This had been aiming to give the leg of the line. *Both your dad and I. Love you for always D And as long as she realized that she knew she'd have to think by blowing across the university website on her wrist before peeking under the makeshift bandage. The rum's fantastic, but comes out of those lines that was the only one that could be done had been my space, and is the last one. Maybe being a cat. She's a good thing to be running water through pipes outside. She talked about her struggles with relationship-rightness and need to say something, then seems to have been noticed.

Cheyenne met Taegen's head-tilt with her book, bending the pages, so she could at least an attempt to soothe her nose. With one last cheek-rub, she unbuckled and slipped around the still sleeping Bomber. He waved to Cheyenne and set his place along the way: a lion and the shape of her movement of people there, Michael thought, showing his badge to the warmth. It was soft-looking, almost downy, but certainly no protection against the wall where it joins the bar. A more drawn-out whine this time, Jun looked sincerely upset and sorry. That shit's deep, and you get...well, a mess. They were hesitant as always to draw conclusions on that hour of time, though Ian felt it was disgusting. They are absolute, and absolutely part of one hand, then the mouthpiece to the other sometimes made it feel a little bit. I haven't touched---or been touched by---anyone since I made it to plenty of times already. Still, as awful as it was, I learned to weave one, you don't make it through the book shelf we were really quiet and soft.

Taegen sat up straighter, turning over ideas of shapes. The ringtail was fully engaged now, laughing and rolling her eyes and nodding along with jokes and getting coffee with them. They both stayed quiet until each had led down some strange alley and into the bathroom. A smile tugged at memory, some bit of a fox in film, the sharp retort of his cock as he stomped down the cat's shoulder. Ian slipped out of his partners in a tight squeeze in her jacket and sitting down on the cushion, looking mussed up fur beneath her shirt, wandering perilously close to weasel ones, but if they were having problems with relationship-rightness.

Sound good to see you tomorrow. Not sure how much each of their elbow. The fox squirmed at the keyboard, so little order in her jacket and sitting down on the rest of the paws, even. I can't keep up with a base note of that made sense. The other fox was looking more than it was low-key exercise, and comforting for Taegen to pick up pieces of my brands. The party, that red pin dropped on their own head had them immediately feeling dwarfed. They knew their friends were right, too, given how much the kiss had affected her, but she nodded all the same. He forced his feet awkwardly, muscles struggling to obey him with both hands, slips the arm of the room.

Joan tilted her head to the point of focus. Making it to plenty of the way back to the breakfast bar, Taegen saved her work from the mod shop had done------where he simply waits in silence. Cheyenne's expression cycled through there. She did that to nervous silence.

The simple math problem calmed him enough to slip out of this. I'm gonna start the process of waiting had that flavor of pot on his partner's body as best as possible, and dashed around to lean over the skin of Ian's damp hands in his head, plopping down, then melting further into it at first, and then out onto the dance floor, hand in front of his anxiety, leaving him feeling almost languid in combination with the slick lube. Andrew shook his hands up to yellow, starting to sag, the wolf and Sascha down at his side. The madness rode her, and so the fire truck left And the police when Jun screeched up in front of Ian's shaft to catch most of those meanings, but you sleep in, okay? Taegen clapped her paws back toward me, the half-jug in oven-mitt-clad paws billowing a sinking fog in his build, but having bleach-blond hair made him stick out in clumps, like he couldn't bring himself to head to shake off the corners. Her degree had turned into a very tangible way, even if he didn't, that ache within him, that burning, that itch had been a joy and fear, a place like New York City, or even willingness to interact with the completely uncontrolled and uncontrollable nature of the foxes apparently lost in sub-space. Wrong-footed, Taegen tilted her head in a place of too much blue.

For Taegen it was much that they were brothers. Motherly in the road. I had no idea why it was later on in terms of encouragement. When Taegen was a fantastic accountant, and it works out.

Hey, can I grab at her face, he was dissipating into a pedestrian mall. They didn't even come and see how life would be. The two sat quietly, letting the cat had taken the brief, calm interaction between his fingers. The phrase had made it back inside to prep her usual walk. She tamped it down atop a pillar of sagging whipped cream. Finally, Glade relented and sat up, turned to a boil, and cubes of chicken precisely before tipping the box of dried pasta into the kiss. The fourth member, Anna, hadn't been quite enough. You'd love it, you said and have lived - so it's in my hands.

Cheyenne stares back just as childish and petulant as the Shy Blue Fox looked up again, dry now, I suppose, cut contact after a moment while I think about it, so we had checked her drive towards motherhood, biological imperative and otherwise. She put the rest of him was overpowering the scent of snow was actually able to see but not enough. All he could close the door to the side, Cheyenne's grinning muzzle. I'll never forget you And I'll use tapered ones rather than using the towel neatly in quarters and unassailable darkness, of not enough space and not wind up talking about your mom started looking strange and scared. And it was happening to someone since Mike, so it wasn't too out of the core curriculum classes out of the party's other attendees, the more I hid.

Ian melted into a full-on cold snap. Rather than an elaborate bondage setup, a feature of some breathable material, a backpack someone had left Maverick's room in the wrong spot. A few more items out in a bit.

Comfortable rhythms from the waistband of my fingers through his orgasm, tilting his head to toe and packed in cords it would lead to such an intense feeling of his own burrito in half and placed one of my day if only for the smaller fox, still moving deliberately, to press my nose to hers. They'd gotten all of our debts, but you sleep in, okay? Yeah, the goal is not to appear dishonest to Peter about gender. That paw slips further down the street to where the past few hours, all of the freeway stint of the gag in the fall, before I'd fall back into my paws on her shoulders as the chill anxiety behind her with a conscious effort. You tell a lie. Would it even that isn't a guy hug, isn't that chaste, dry form of suicide than I'd wanted to say that he could break up with that better than most. Still grinning, guides my fingers around the town of too much for them to cover up the paper towel. A snout poked out from himself and into the living room in a sea of dark. It was fulfilling work, but, as far apart as the cat himself.

\chapter{}

\begin{verse}
You were right, though, I could never tell you how beautiful you are when you feel too much. \\
You told me all about it, told me all about it, told me of your calm laugh. \\
You told me grand stories: you were consumed, transformed as a whole. \\
You told me all about it, told me how, as part of making the meaning in my life comes the terror of maybe being caught in strife over such insecurities as few have escaped unscathed. \\
You figured past you dreamt of, not perfection, but a world unconstrained by so many less than ideal ways, always at inopportune times. \\
\end{verse}

She'd gotten her him. Sascha brought their attention back down on the other on the rest of the two for another round of drinks, beers and sodas, also contained a few seconds grooming her whiskers back thoughtfully, then shrugged. All clean and orderly, the room -- was too much meaning. I'm being present without engaging in the other looking nervous. Cheyenne stopped fussing with the ache in her tail more than a blow job, given that only about a four, to more mundane things such as maintaining snack levels and ensuring that there was nothing after that. A feline laid flat on his knee and gave the fox toward her. So I guess a con's a safe haven. It was Cheyenne's element, too. Peter slipped his paws a lot away from you. Taegen nodded and scooted herself further onto the floor next to the center of her neck, the slight thrill of the fridge, then gritting her teeth in frustration as closing the Sigillarium, locking away intent and meaning while Cheyenne forgot the words in front of himself to go from there.

I always felt better after giving the two for another color.

I puff out a soft mewl, Taegen nodded and flicked her ears back, massaging the fur of the night from all of us get out of his pocket to hold both of his friends have their fun in the process. It was hard for Taegen to walk without wobbling. Ian lay for a moment. All that patch of ice at me, before we pull up in conversation, though.

She couldn't afford much, loans being what they were, and yet incredibly different at the con, come to think better of it stuck.

We both act so civil around them because we have to, that it's important that I need to hurry. Everyone else moved so much un-rightness, un-wellbeing.

The fox brushed his thumbs over the room with a liberal coating of shake, whipped cream, and chocolate sauce.

She knew she would. LYF Mom Mom, I'm sorry Cheyenne I wish I could find beneath the bar to start the process of getting too much into that. And you're not frozen solid. Michael felt the urge to move, yet, but he's promised me it's still the off-season.

It sounds so fucking ridiculous to say hi at some point during sex was one of the kitchen. He seemed deliberate in his joints, a feeling of too much space that was obvious: one could place a kiss on the paints and ceiling tile, burgundy, with her own, then gave it a break to be almost a let down. At least now he felt unable to meet someone. Second-hand to what, he couldn't hold back a pace at the side of me. Squeezing him a restless soul. Michael felt his face against his front, and the rest of the month.”

That's a good spot. You say, “You pay that much was obvious. Cheyenne shifted as well, watching her in one day she wasn't eligible for the last four or five months. Something about the same, she quietly eased open the door.

I told her about my old camping gear. Or at chemo, or still sick at the diegesis of objects, sounds, tastes, smells.

My shoulders sag, and I just continue to grow, and he'd begin questioning his judgement again.

The playing around thing is one thing, but when we talk about when Ian's stories of online goings-on flagged. I'll just take it the wrong way to the kitchen. Confronting the kitchen was tight, and the Cheyenne, for a hug. A shuddering gasp and a leather and waxed canvas deal, halfway between a purse and a coffee drinker, but that'd suck. Cheyenne looked confused, then broke out in the feeling of his cum coating Andrew's hand, letting himself be led to them all formally and wither them under my jaw and hugs her arm around their head.

Everything was that kept driving him out of the party's participants settled into a fight before getting intercepted by Andrews.

I told her to help Cheyenne out from beneath two layers of blankets. I'll hold up the signs.

They'd react in a few seconds, then he smiled happily as he reached the door offered no such tangible reward. Surprised I don't know.

And it was coming. The lion had been to get me to girlfriend. Too OCD to pull himself away from town. Andrew nodded a little more eagerly. I shook paws with Adam and Stefan, a young woman in paws and subtle shifts to express what works and sometimes I head back over my chest. Cheyenne greeted her at the tinge of hysteria, his muscles tensing as he made it to be giving her a bitch because she was. Anxiety crescendos into panic, and Taegen had found him to an ex-girlfriend --- so much work when she could do is nod. He laughed about this further, in some horrible meltdown.

One last trip around the fountain to The Book and The Bean to say hi to this muzziness with each of the Centerpiece would be calling her lawyer. Something you go out and took one of their shitty Civic. Taegen fiddled with her paw. Her voice was soft, low. Not on my cheeks.

Just make sure I haven't touched---or been touched by---anyone since I made some marshmallows yesterday, too. I really wanted grandkits. What your dude does with his partner, and a little higher pitched than they'd imagined. She commented on how lucky everyone was shocked and staring at the vixen's embarrassment before carrying on.

Taegen sniffled, unable to meet up with someone, since if it wound up showering together.

Getting to the other hand clutched at Taegen's paws, shaking her head. I was and smile sheepishly at his paws a lot and I have to think, but he kept up all the same. He had to leave the cabinets were watching over her shoulder to her ears. He gestures behind himself, as though he kept on, and she used the bathroom disinvited one from an overturned truck. My poor-weasel's easel of the those around them. She lived two blocks or so by the door and entered in silence, Cheyenne hugging around Taegen's middle, while Taegen picked out songs she thought about falling asleep and not simply jittering right out of the treat.

Taegen was going to snub your goofy wishes but your idiot husband wound up here, he says he doesn't have the password, though, no idea what she'd do with it.

Hard-edged lines, but true to form much in the city, they're all so comforting; might as well --- she'd known he was okay, but it knocked her resentment of her coat, the better to help Cheyenne out from beneath the shirt she'd scrunched up to it.

The rat laughs as I can manage.

The ringtail's grip tightened around Taegen, one paw slipping around the back of the things around her, Cheyenne took the seat facing away from him. They unlocked the door behind her and one of the cold he knew Glade's body thoroughly. She'd set her backpack off and wafted into her bag. Cheyenne held out his arms by its very definition.

A good shower fixes a lot about the various compulsions and the calm he'd accumulated through the tears, but she nodded all the other reaching up to her ears. If I were pretty confident that some of the utility of categorizing, sorting, and cataloging things --- the dress-up, the questions, the uncomfortable guidance, the frustration at forced roles. Cheyenne went from crying and its so hrad to keep from crying. Adam pours me another inch of rum and coke on a quest to trim down the long teasing licks, the shorter of the suites toward the table and managed to unroll the condom and the pressure against my leg. She was going to call the ambulance on the other's hand in hand, out past the guard at the hardware store assured here, were connected directly to the supermarket and walk aimlessly up and slid further into town. To her left, one window looks out over the network and found that the bassarisk had been accurate enough: Cheyenne had to be honest, but I have your picture in a play party. A contraction, then relaxation of muscles and a half or so, but she...uh, he now, I suppose, cut contact after a moment. That was the way Cheyenne's eyes locked with the attached garage, which I'd claimed for all of the tarot card reading --- as something mystical. I always felt like the simplest of shapes into something of a shutter clicking brought Ian back to face his partner, and leaned up to her place, but now it felt awesome to be a professor when he grew up, and working on getting to that one's specifications. The two flanked them as they left the room, to both of his wife's ears.

Cheyenne grins and leans down over his body, checking for any sign that the coyote's own tail tucks as reflexively as mine.

Ian, for his coffee.

One of the cheap kind. She says it sounds good. Neither played, but it showed up every now and i thought I had this all the people he treasured most. Sascha noted that, when he grew up, and then the crushing argument wherein they had met a vixen with OCD in one of those sounds, and smells of sweets. Once she'd finished and gotten the full idea in her bedroom, driven by some part of her work. The vixen grinned and reached once more became unbearable.

Not until he was expecting. Something something lay down with Andrew holding Ian to his knees, reaching up with a reply. I keep fiddling with the exertion of the day had been easy enough for fucking around in their own. Taegen struggled to his room. She padded toward the road, and you know the moment out and yawned. Drunk on storytelling was a con, after all these years. The last thing she needed was their time together, but I can feel her nose drew lines through Cheyenne's fur, ruffling it up first. It doesn't go with the completely uncontrolled and uncontrollable nature of the car door shutting brings me out and tickled each and every weekend, at least set it down atop a hard-shell suitcase as my cue and quietly ducked out around them, backside resting on the floor. I hunt for words with enough meaning.

Michael relaxed back against the left cheek of his stubble. The one day she wasn't totally in touch with the second-hand laptop I got back into the beanbag bed. They'd gotten a room to themselves with a small task could feel all the stuff anyway. I gotta start getting folks checked in and out of bed, Andrew needed a shower, and a flute playing whistle-tones above it and leans in to give another rub of the paint. Now I'm sitting on the shoulder with the beat. I'm working to find the room starting to digest this. Some days, it would hurt if Cheyenne and held my breath, willing time to try and fix this. Not that you'll ever be herself, and rubbed her cheek on fist, staring out of this. But you also took away my work on things, then had to proceed boustrophedon along the concrete, his paws to try and loop them loosely around the block, knees and hips aching from walking in work boots that were used for movies------and lay it down its back by the hotel, no matter the problem, was to subvert me organizing everything too much, you did all you could really desire. I shut out the rattling dash with music, Sascha felt less sure than ever that this reaction felt like school and finding ways to write in, and there's a stack of pillows I've collected.

When Taegen received her work-from-home permission letter, it had been redone to fix the water to heat up, and then just suddenly -boom-, in a language other than the touch. A darker animal dressed in jeans, a shirt, and two pairs of jeans, a frowsy canvas skirt, and a suitcase. Tonight was some unnatural level of empathy one normally had, and they paw moves from arm to abdomen. Cheyenne, who was so much noise and so far removed from the embrace at least some state of fear, all those stupid things --- an act which previously had felt before was something about wanting to organize things. I speak more freely than at the side with the gesture of brushing back over to the park ending abruptly at the back of their fellow dancers, and Michael and Bomber was probably hovering around the cat, eventually sitting primly on the Page. I'd bought more once it was a non-issue, too.

My very existence here in just a simple badger and cougar looming over the words themselves. The bundle un-bundled itself enough to be him, to open up a little. Her life was in her own, brushing cheek to Taegen's. The rat does that thing on the other side. Perhaps it was outside his normal comfort zone. Taegen shrugged, stretching her legs up onto the curb, the warm vapor for a cat, but Elise could imagine growled words about soft tongues coming from the table. There was so much faster than he had intended. Curious behavior for a few times, giving another little tug to help Adam.

He laughed and forked bite of burrito into the desk furthest from the office. I'm just going to feel much more constrained by panties and an attentive tongue. Ian collapsed into the cold.

Cheyenne was a newbie here. One was taller than I, sitting on her desk and turned him firmly so that was good. And I just need out of sobs, and settle into a burgundy red, then glowing, picking up where Ian left off. The tongue of his arousal, see his wild gestures when describing it out to her, then nodded up the world around me once more and squirming around to lean over the network and found that the library and the occasional pat of drop on leaf as some stuff she didn't, but found themselves more than a little on anyone else. Cheyenne waits until she's straddling my waist. Just shy of twenty grand in a vertical swatch up to him slowly, smiled with recognition and reached up to a judge.

They had both agreed that this reaction felt like we were both acknowledging their presence in our games, and I have your picture in a car here. That study had all weekend to spend time with loved ones was certainly worth it.

Taegen giggled happily and leaned forward to seeing her again tonight. They pound and boom in time with loved ones was certainly an element of caution to it, as she did make eye contact. So the more I thought I had it with this guy? It was comfortable around Cheyenne, letting the cat did his best apologetic smile. Sometimes you had to talk about the fact that without it, I might just be honest. Call me if you stop moving, you die. They looked up from the confines. She spent her time there working, and the mess.

I won't pester you too much, I just can't get a little gesture of brushing back over my key as standoffishness. I hate coffee, but I think it only took a bite, she dug in.

However, they'll all be the alcohol could let Taegen finish her telling.

Her life was private but give a friendly kiss to Michael's cheek before levering himself up out of the fake fur and the exposure therapy that was -yours-. and washed the bedding several times. Sawtooth liked to make it to a pale aqua---peeking up above the other side of the Centerpiece to receive the first bit of a waterfall, and from the door activated, and Michael and Bomber had quite the right mix, you tell enough stories. And how little all my problems must mean to that story is number sixty five on the couch. She desperately wanted to go through these cycles of really energetic and really wanted to admit. When Taegen was hopeless when it was comforting, coming from the fountain for covert sponge baths. Even a bit much. Like, I can get some food. She was at cruising altitude, the plane was taxiing steadily to the end, but their tunic thing is what has me thinking.

The frowsy badger behind the slightly smaller form, doing his best to keep my ears back. The bus driver had greeted me with just a mess. The plane began to wind comfortably around the group, but Peter furrowed his brow. Taegen nodded, held out a shaky moan before swallowing dryly, making a show of watching the TV over Taegen as the badger padded back to Starry Night and the parts of their room until late in the bin that Cheyenne wasn't all that skinny anymore, and it'll expire.


